\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[pdftex]{hyperref}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=1in]{geometry}
\newcommand{\MinNumber}{0}\begin{document}

\textbf {\huge In this file:}\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{Table 2}: Summary of the results per sociolinguistic variable;}\newline\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.40\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic Variables}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}Global world population. 65  Asian(growing). 17  Black(growing rapidly).10  White(in decline). 8  other.  & \cellcolor{green!27}Black & \cellcolor{green!27}Black & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}Sounds like white people should stop being the only race trying to start a war among races  & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}If you say it's okay to be a racist, I say it's okay to jail you for domestic terrorism.  & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}Trump supporters suck, they are the Lowest people in the nation.  & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.25\mylength}|C{.40\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Variavel Sociolinguistica} & \textbf{KeyWords} & \textbf{N de ocorrencias} & \textbf{Frequencia}  & \textbf{Frequencia(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Black}  & \cellcolor{red!27}Black & \cellcolor{red!27}1 & \cellcolor{red!27}1/271& \cellcolor{red!27}0.37 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Ethnicity}  & \cellcolor{red!5}Race, Racist & \cellcolor{red!5}2 & \cellcolor{red!5}2/271& \cellcolor{red!5}0.74 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality}  & \cellcolor{red!27}Nation & \cellcolor{red!27}1 & \cellcolor{red!27}1/271& \cellcolor{red!27}0.37 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Black;
 Ethnicity;
 Nationality;%.

\item The percentage of hate speech related words is 1.476.

\item Considering that the variable \textbf{Ethnicity} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 4/16 occurences of hate speech related comments.\end{itemize}\end{document}