\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[pdftex]{hyperref}
\usepackage{colortbl}
\usepackage{longtable, array}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newlength\mylength
\usepackage[legalpaper, landscape, margin=1in]{geometry}
\newcommand{\MinNumber}{0}\begin{document}

\textbf {\huge In this file:}\newline {\par\large --- Table  1: Summary of the results per comment; }

 {\par\large --- \hyperlink{Table 2}{Table 2}: Summary of the results per sociolinguistic variable;}\newline\newline

\centering\textbf{\large Table  1: Summary of the results per comment 
}
\newcommand{\MaxNumber}{0}%
\newcommand{\ApplyGradient}[1]{%
\pgfmathsetmacro{\PercentColor}{100.0*(#1-\MinNumber)/(\MaxNumber-\MinNumber)}
\xdef\PercentColor{\PercentColor}%
\cellcolor{LightSpringGreen!\PercentColor!LightRed}{#1}
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 50\tabcolsep}
\begin{longtable}{|C{.40\mylength}|C{.30\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Comment} & \textbf{KeyWords} & \textbf{Sociolinguistic Variables}  & \textbf{Hate Speech Frequency} & \textbf{Hate Speech Frequency(\%)} \\
\hline\cellcolor{green!27}You guys are really misinformed. There has been scientific proof of transgender brains and that trans guys (FtM) brains align more with a biological mans brains than a woman's, vice versa with trans women. Benton literally has a brain that aligns more with a males.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}Will always be stuck with a pussy though  & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}It s so freaky when you think of all these trannies out there tricking people. Trainees able to go into restrooms and locker rooms of the opposite sex, leering at people.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}I recently found I m attracted to transgender female to male. Just watched this to see what ppl go through when they transition. I wonder if he got bottom surgery  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}HAHA    They can turn there female clit  outside but it is a micro dick a female well not  even notice it a minor stab like a Rat dick  !     But that is ok they have strap on sex toys !!!   As far as a kid they have the sperm bank !    However there side effects from using frozen sperm   the child has no soul !  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}I kNoW I CaN rUn fAsTeR.. What an idiot.  Your gender doesn't define have high can you jump or have fast can you run.  What a sexist pig even though he was a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}He is so handsome, but now I know I watched some videos regarding woman convert their gender to Male I noticed that one of the effect of  T   is having a lot of hairs, sooooo.. if going to date with men I will ask them to take off their shirt and see their chest downward, if I'm not convinced oh my gosh! I will  check the penis! LoL            & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/69 & \cellcolor{green!27}1.449 \\  \hline
  \cellcolor{green!5}I love how 99  of the comment section is obsessed with his gender and is dogmatically telling him what he is or isn't. Why do you fucking people give a shit? Get a life.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}So let me get this right. If a man dates this woman, is he gay or straight? This shit has me confused  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}Have you thought about where your spiritual body goes after Death? Why would you choose to end up burning in Hell? Think about it because believe me 100  there is a strict Judgment of God after death. (Hebrews 9:27) I urge you to choose the fear of God and repent. Please, go to a deliverance ministry in your area so they can pray for you, and go back to your original gender before it is too late...  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}The transition sometimes doesn't look so good, and I'm not exactly personally for it myself, but damn you're cute.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}There are only two genders - you have a mental heath issue.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}this is discusting ur still a girl no matter what u do to ur self that's not an Adams apple ur an abomination  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}How old are people in the comment section. Just curious  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}These negative people in the comments really don't understand how it feels to be in the wrong body. They don't know what it's like to wake up everyday feeling awful, and uncomfortable in your own body. For those people I want to say congrats. You don't feel this way and I want to feel what you are feeling, it feels like you're wearing an embarrassing costume everyday and it fucking sucks. Yes, biology you are born with the gender you are born with, but new flash this change. If other people in the world can be happy with who they are, then why can't we transgender people be happy with ourselves. Think before you hurt someone's feelings. And if you disagree, well do you boo and have a great life.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/130 & \cellcolor{green!27}0.769 \\  \hline
  \cellcolor{green!5}Just Why?....just accept your fucking gender wtf  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Science has proven that transgender males have brains that align more with a biological mans brain, vice versa with trans women. He's a guy.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}Alot of people are saying that you will always be a female. Here is my opinion on this subject. Throughout the past 10,000 years it has been determined that sex is not an interchangeable feature. In the absence of modern science people who believed this were absolutely right, but now we have the science to make a person's sex interchangeable. If a person is able to replace their reproductive and endocrine systems (or whatever other systems are associated with sex) with those of the opposite sex then it's factually correct to state that they have successfully changed sexes. You are a male and anyone who tries to deny that is wrong. I'm a guy btw and I feel like it is a ton better than being a woman. I don't have to deal with so many dirty and painful experiences and I fully support your decision to become a man. Congrats bro  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/152 & \cellcolor{green!5}0.658 \\  \hline
  \cellcolor{green!27}You are quite great for a transgender male :-)  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}born a woman stay a woman learn to love yourself instead of using hormones to change your appearance  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}people, let him be who he wants to be. I see a lot of hate in the comments and it hurts me. You're really beautiful :) and you deserve much. But there's only one thing that interests me. If you've taken testosterone for 2 years do you think like a woman or like a man? I don't know if you have noticed any change like that or is it even possible to start thinging the opossite sex way  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}I m happy for you but question for the comments do you believe that gender and sex are the same?  Keep it civilized please. I just want debate.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}Well I think people can be whoever the fuck they can be.  Bc that's them but biologically they are the gender they were born with . If a she became a he tho I'd address them as a he  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}you can fucking change your gender, but they cant resolve the hair loss problem.. :) fml  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}are you woman or you are gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}So wait how are u gonna have sex  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}Ur still a woman lol  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}I don t think this have to be legalized like wtf bro imagine if you are a man and you spend years with someone having sex and stuff and then he tells you im a transgender i would fucking kill him and live all my life uncomfortable.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}Very interesting video. Thank you for sharing, it's really crazy to see the progress that's been made!  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}she still a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Seem like a nice person but feel sorry for any straight women that try hit on you. You are and always will be a woman. People like this are messing with nature, it's just not right.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}Gender is a fucking joke now  Born a girl...oh no I wanna be a boy...inject your self and get an operation  Yay I'm a boy  Born a boy...oh no I wanna be a girl Fucking bullshit  If someone is not comfortable in what they've been born  They will never be comfortable with themselves their entire lives Probably for a while they'll be happy but it'll come back and bite you  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27}what a train wreck, now you can finally be a gay man lol  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}Since all of you are so insistent on saying he's a woman, i guess that means you'd fuck him, am i right?  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Imagine a transgender guy comes up to me looking like a woman and presenting himself like a proper woman. Had hormonal treatment and all. Comes up to me and starts flirting. I have no fucking clue what a real woman is anymore. And not to be rude or anything. But I like my women fertile. And not men with inverted penises and testicles. As not being able to have children is a real deal stopper to many men. I have a huge fucking problem with trannies because they think they can go to the dating market as if they were the opposite gender, when in reality they are being dishonest from the get go. When dating, a transexual needs to say what they were born like to avoid problems when things get intimate. If we can bypass this big issue for me, then we can agree, they can be called whatever the fuck they want. (as long as it's she or he, I won't be using made up words for made up  genders )  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/173 & \cellcolor{green!27}0.578 \\  \hline
  \cellcolor{green!5} Man O' War I see what you're saying, its actually SJWs that have made up these fake genders and not the actual transgender male to female or female to male as they just want to live as the binary gender male or female. Actual trans are not SJW, its pretty sad that these SJW have made the trans community toxic. It has brainwashed how you view it.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}the amount of negative comments is fucking insane, and you all wonder why so many trans people kill themselves. he, nor any other trans person, is bothering you by being themselves. ive had friends in the past who are trans and every single one of them says that theyre just like us, they were just born in the wrong body. try and put yourself in their shoes, you know? you know that you or a boy or a girl. you know that. you are sure of that. now imagine being so sure that youre a boy, but you were born with a vagina instead of a penis. do you know how incredibly frustrating that must be? give the guy a fucking break, hes been through more shit (and made it out alive and well) than your pussy asses could ever EVER handle.  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/142 & \cellcolor{green!27}0.704 \\  \hline
  \cellcolor{green!5}if i saw you on street walking, i should not think that you are transgender omg  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}lol u still got a lot of work to do. u sound like ur gay rn  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}fucking gay if your a girl stay as a girl  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Born a Man always a Man born a Woman always a Woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}These people are mentally ill and should be given the proper help as opposed to mutilating themselves and pretending to be the other gender. Trans people are gross, nuff said. also  she  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}The problem is that they need mental help and if you truly believe otherwise then you're fucking deluded. also  She.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}Bud, the WHA doesn t even classify it as a metal illness, but let s pretend for a second that it does, would you comment in this hateful manner on a video about someone with, let s say, OCD giving you information on their treatment and how it helps them? Maybe this is their mental help? I don t see you giving them support and help. You re part of the problem, so maybe that makes you deluded.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}wait so he was a women how he looks like a whole nigga  & \cellcolor{green!27}Nigga & \cellcolor{green!27}Black & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}Fucking weird times. Now i can't even recognize a real man or woman  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}I hate this its taking away everything special about being male and female whats special about either of them now if you can just take some hormones for a while and basically become the other sex its completely stupid  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}You will always be a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}gay fuck  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}Shes not a man. U were born has a woman  and ur blood is a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}How not to treat gender dysphoria 101.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}Hey! I just wanted to take a moment, after reading all these comments and tell you that the decisions you made, were in my opinion, are very brave. I am sure you have been told a million times or heard a million negative things in regards to the changes you have made in your life. After reading some of the comments, I felt sick.  I have a friend who went through this same process and it was an amazing experience watching him become himself, and find happiness, who is now married to a wonderful women! Although, I do not exactly understand what it is to feel like I am in the wrong body, or born the wrong gender - I can only imagine - I have great respect for you taking these steps to become the person you intended to be. I hope your journey in life brings you all that you hope for! - Congrats  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/156 & \cellcolor{green!5}0.641 \\  \hline
  \cellcolor{green!27}I think I just found a loophole  I m gay. And I think you re cute. But you re a woman. So am I gay or straight?  If I m straight, then why do I find you attractive if you look like a guy? That basically means I m gay. Repeat cycle.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}Normie Trash HE is a GUY NOT a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Your chromosomes are XY and they will always be. You disgusting freak.  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}so would it be gay? asking for a friend  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}If you're assuming that i'm middle eastern then you are wrong and second of all my opinion is that I don't support what I see as freaks and I don't think anyone should, and a majority of the middle east thinks so too. Tell me why the hell a woman want's to be a man? You're sick in the head if you think this will ever become a norm. Don't worry, proper people like me will see to it that these freaks and their supporters are shut down.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/88 & \cellcolor{green!27}1.136 \\  \hline
  \cellcolor{green!5}The lines are starting to blur Its getting really hard to tell who s a transgender now a days, not that its a bad thing but damn  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}You aren t a male you have no balls and where not born a male, your just a weird lookin girl.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}pussy boy  & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Screw it, if we changin gender I m changing my age, species, and race. I wanna be 21 so I can drink and party, I want to be African American so I can pretend like my ancestors struggled because of people s selfishness, and I m not human so I don t have to abide by America s rules since I m not created equal, I m higher than everyone.  & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}What are you heckin gay?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}Why the fuck are here so many people that put you down?? What the fuck? It's not a mental illness, she felt bad in her body so she changed it, it's not a mental issue. You sick fucks know nothing about it, tho you hate people who do this. Disgusting  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}It's funny to see all this people commenting dumb stuff, don't pay attention to them, awesome changes! I wish I had started T at a young age.  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}hope one day your son will change his gender  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Dude in church they say it's a sin stop be gay or transgender or bisexual in fact I'm working on a diss track to all people that believe in science and are LGBTQ but I'll name someone specific  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}you are a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Classytagz I know right? The youtube algorithm keeps showing LGBT and sjw stuff  & \cellcolor{green!27}LGBT & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}FAGGOT  & \cellcolor{green!5}Faggot & \cellcolor{green!5}Male homosexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}Nothing will change the fact that you were born a girl. Stop trying to change that fact and trying to be someone that you aren't. This truly is a mental illness and should be illegal.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}Why is there so much negativity on this video? Yes, being trans is a mental illness, but this GUY has taken the step to cure his illness. Why are people hating on someone trying to help themselves and make their life happier? This handsome man is doing great.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}She's not curing her illness though. Transgender people have one the highest rates of suicide in modern society and it's not because of the discrimination. It's because there is something inherintly wrong with their brain function.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}Gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}I will still call you a woman. I'm not going to pretend and call you a man just because it would make you feel better.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}The opposite gender and a different species cannot be compared. Just, fyi.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}You can't go from man to woman. Or from woman to man.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}Born with a vagina  woman.    Born with penis  man.  Can't tell me I'm Rong it's proved with Dna it's just how it works.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}Gender dysphoria is a mental illness and shouldn't be treated as normal human behavior. Schizophrenic people aren't told to give in to the voices in their head rather than get help. Children who see/told that certain thoughts make you a male/female it will cause this mental issue. Call me an transphobic( Why would I fear them?) or whatever but doing this won't help especially people who can't afford all those hormones/surgeries.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/71 & \cellcolor{green!27}1.408 \\  \hline
  \cellcolor{green!5}smh transgenderism is a mental illness and we're mainstreaming it  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}You was a girl? crazy. i can't believe it  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}wow u totally look like 2 years old XD 0:08  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}This is Just Wrong, ur a woman no matter what you say/do to yourself  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}atleast u  cant get gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}And why do you think gay guys all consume soy on a regular basis? The estrogen is fucking them up.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}so this guy/girl has a vagina? so if you fuck him does that make you gay?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}ew what a gross woman, she looks like shes trying to be a man!  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}trans people transition to help ease their dysphoria. literally just do some research if you actually wanted to know why  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}one more freak without future. how ill is society nowadays.  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}turns out the man calling out freak was a freak himself  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}all the triggered 13 year old boys in the comment section give me life  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}So I see a lot of hate comments that he/she shouldn't have done this. I mean yeah, it's not 100  a good thing but let them be who they want to be. They do this because they were born with a gender they didn't feel comfortable with.   It's 2018, Jeez  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}Eggy Boi wanna have sex with my dad?  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Stop promoting and supporting a mental illness. Making a life decision while your brain is not even developed yet is stupid. Countless of studies have shown that it is a phase, just look at the suicide rates of trans people: 78  thought about killing themselves and 40  have attempted suicide.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27} god left Fck psychically damaged transgender monsters  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}I'd fuck you... Not sure if that makes me streight or keeps me gay...  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}This is weird, if i look at a video about trans people i almost only see nice comments. But this video has a lot of mean comments, i don't get it  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}I don't really get what the goal is anyway.  I mean, what's done is done.  Calling out  freak  or  mentally ill  won't do any one any good.  waste of time in my opinion, but honestly, it feels as if these people have reserved some time of their day to do just that.  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}gay lol  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}female can't change to woman lul  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}If a woman is feeling like man, its generally prudent to reduce testosterone and increase estrogen to rebalance the female system.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}Lol, it says female to male but he s got an Adam s apple. It s so fake  & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}You know everyone has an adams apple right..?  Testosterone just defines it, check facts before saying something  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}Gray The Procrastinator okay mate. Okay   maybe everyone has it, but bitch a female doesn t get an Adam s apple like that.  & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Gray The Procrastinator yeah u probably right. I mean yeah when female the Adam s apple wont show like that but the testosterone probably made it like that, want me to delete the comment?  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}Freak  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}Its a mental disease called Gender Dysphoria, it is who you truly are.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}Transgenderism is a mental disorder.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}If only you could change your gender...  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}this transgender dude already looked like a dude when he was a girl.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}This shit is gay as fuck.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}mental illness  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}you're still a woman nomatter what science experiments you have on yourself.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}Biologically set sex changed to opposite sex with injections, how fucked up is that ?  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}I hope they find a cure for someone thinking they are a different gender...  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}Big Nips well I'm 18 got laid when I was 15 and means a lot coming from a guy who's name is fucking  big nips . There are two genders one cannot change and call them selves the opposite sex you fucken dumbass this person has a disease and we will find a cure...  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}Big Nips dang you really live up to your fucked up name  big nips  I don't think there is a cure for you. If you really think that saying your a different gender for no reason is not a disease then your lost. They are teenagers they go through a lot of emotions during this time. Some are just to ignorant to realize and go in a path that doesn't make sense like switching genders...  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}Kaneda then your lost. A guy making incompetent arguments about disgusting things and one who believes a man or women and nothing else can call themselves the opposite sex... your fucken retarded. Seeing you like anime proves it. Yes I am a gamer but at least I know this is a disease and that there are only 2 genders no more no less...  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/63 & \cellcolor{green!5}1.587 \\  \hline
  \cellcolor{green!27}You're normalizing a mental disorder, it's repulsive.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}Too bad you're still a chick  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Wtf u're a woman !!!!! That's sooooo wrong  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Fucking weirdo kid.  & \cellcolor{green!5}Weirdo & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}It's really hard to believe you were ever a woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}So people with the need to chop off their arm or any other limb are scientifically proven as mentally ill, but if people do it with their genitals theyre transgender and just born in a different body??? Dont wanna discriminate someone but its just ridiculous that there are people who support this...  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}What about the side effects? Even when you are a male doctors tell you about the million of side effects. I'm a man, but i don't have too much testosterone.  & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}While you may believe you will eventually be able to  fit in  as a man, you will realize that this dream is futile. Men and women are not blank slates learned by society to act the way we do, we are two very dimorphic genders that have patterns and brainwaves that makes us unique. I can tell you're emotional, I can smell your female way of being as a groundwork for who you are, and this will never go away. This is especially obvious in male -  female surgery. It's easy to spot a male to female transperson, you can sense him from far away. This begs the question, is it better to be a rejected man than a real woman who deep down inside wants to be a boy.   Why do you think transpeople suicide rates are so high, when they change they will never fit in, and once they have they can never change back. Transpeople are chasing a dream it's impossible to achieve.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/166 & \cellcolor{green!5}0.602 \\  \hline
  \cellcolor{green!27}Congratulations, now you're just a hideous woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}Faggot  & \cellcolor{green!5}Faggot & \cellcolor{green!5}Male homosexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}hope they find what they are looking for but i doubt it the problem is mental you can go so far fixing it physically  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}All these sus boys have nothing else to say but insult you  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}Gender dysphoria, it is an illness  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Being trans isn t a mental illness. The fact so many trans people kill themselves is only because so many people are bigoted and unaccepting.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}being transgender means you have a mental ilness  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Yes, its called Gender identity disorder or now more known as Gender dysphoria, it is in fact a mental illness so.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Retro Frog 186 likes btw... this person is extremely depressed and confused, not happy. GOOD try tho  & \cellcolor{green!27}Frog & \cellcolor{green!27}French & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}I'm trans and i agree it's a mental illness cuz what else would it be. The treatment is to go on hormones. So basically people who make fun of trans people are making fun of mentally ill people and that's messed up. Would you make fun of someone who was retarded or someone with down syndrome? If the answer is yes you need to reassess the way you think.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}you look wonderful and happy, and nobody would ever know you transitioned! best of luck xx  & \cellcolor{green!27}Nobody & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}rpg videogames gender choosing is getting real  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Hairline recedes -just gotta live with it Born a woman -gotta inject that testosterone..   I'm not hating on anything, I just find it ironic. Wish you best of luck.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}This is fucking sick. Men are men! Women are women! THERE IS NO FUCKING SUCH THING AS TRANSGENDER!! Can you imagine that?  Fuck you good at suckin dick   yeh thats cause i used to have one!  FUCKKKK THATTTTTT  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}Why did you censor your man boobs, its not woman boobs anymore  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}You still have pussy    & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}I am transgender!! Is watching more of this videos makes me more happy. I m so proud that you have done what you wanted to do  hope your a happy person    & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}I m gay! Also your username is I n t e r e s t i n g  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}Gray The Procrastinator not about you being gay, I wouldn t know that Aish Lololol  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}No dick no man! You cannot give pleasure to a woman you mutilated hybrid.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Wait ARE you a gay trans  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}wait so?? if im a boy and shes a boy and i would say lets bang so i would bang  HER  but  him  so does that make me gay?? HMMMMMMMMMMMMMMMMMMMM??????!!!??!???!!!???  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Normie Trash retard  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5} ZebraSnot how old are u cuz ur actual stupid  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}You re still a woman though.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}I'm fine with transgender people if they actually commit to being the gender they believe to but when they say for example a girl but then look and dress like a boy and get mad at you for calling them  he  i kinda have a problem with  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}That transformation is impressive. I would never guess you were a woman before.   I need to start taking testosterone. Hopefully I'll grow taller a bit  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}I'm sorry you felt like you had to glorify your mental disorder for views.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}yea you definitely look like a guy, seeing a trans person looking like the opposite gender makes me cringe  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}an 18 year old that transitioned from female to male has more facial hair than me, and i'm 21. i'm gonna kill myself rn  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}One of the prominent mental illnesses in the 1st world society.  Nu em a gey ev en doh i bern a gerl.  Disgusting, you fools parading and cheering on these mentally challenged and pain inflicted individuals should be ashamed of yourselves. We need to help these people understand the reality of things, taking testosterone to look like a man, even when you are a girl should not be the celebrated phenomenon it is the media and western countries.  Homosexuals probably wouldn't care, but people like this will start attracting heterosexuals, and in the case of men, things can become pretty violent. A man finding out his girlfriend is a estrogen induced biological male could become a very dangerous situation.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/119 & \cellcolor{green!27}0.84 \\  \hline
  \cellcolor{green!5}ArthaxtaDaVince777 I m sorry, but do you not think the person that needs the mental health check is you? Why in the world would any situation like that (in where a man dating a woman that they later found out to be transgender) end up violently? Violence is not the answer  and there should be absolutely nothing dangerous about a situation like that. I absolutely can t believe how shockingly horrific your comment is. Even if a situation ends up in something that may frustrate or anger you, violence absolutely should never be involved. You are the last person who should have any right calling others disgusting and mentally challenged. The disappointment in humanity is you.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/114 & \cellcolor{green!5}0.877 \\  \hline
  \cellcolor{green!27}Blank Blank You shouldn't be sorry, so that's your first major problem, handing out sorry's when there is no need for one. I need a mental health check because I consider the fact that a fake woman sleeping with a biological male can turn violent? Did I suggest it should turn violent, or simply that it will, naturally? It turns out to be the latter, now what the hell does that have to do with my mental health, you cretin? You libtard progressives fully present your illogical thoughts and opinions in all their infamous tyranny. A man dating or even sleeping with a fake woman could easily turn violent, this man was taken advantage of by another man who tricked him into buying his female appearance. This can be considered rape, do you understand that? And in the right circumstances, even a decent man can go ape shit and harm or kill this fake woman that tricked him. The same goes for fake men that trick biological women, there are many transgender deaths that occur due to these problems, but of course not all the time. When did I say violence is the answer? And that is bullshit, toddler  logic. If violence wasn't the answer, we wouldn't have established militaries  across the world to defend our countries, and police in the streets to uphold the law and protect the civilians. I call them for what they are, a man is a man, a woman is a woman,  if one changes their appearance artificially to sate their mental state and their paranoia, then yes, that is disgusting. A man that is now a woman, is disgusting. A woman that is now a man, is disgusting. You don't think so? You think its great? Fine, that's your opinion, just don't pretend like you are the  golden standard of acceptance and moral understanding when you decide to cheer on these mentally deranged individuals. These people need serious help, not in the form of holding their hand to make  their fantasy appear like reality. This disappointment in humanity is me? How? I am trying to uphold the evolutionary and scientific concept of men being men and women being women,   not women turning to men and man to women. This is real life, not a circus act, people like you that are cheering on these folk, instead of helping them understand that they could potentially ruin their life permanently, are doing no service to humanity, you are devolving humanity.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/414 & \cellcolor{green!27}0.242 \\  \hline
  \cellcolor{green!5}Not here to hate but you can t just become a male... your a biological female and so just because you  take  testosterone doesn t make you a male sorry it just doesn t work that way you still have cells of a female in your body they don t go to far Some transgender people make me sick because what they do is try to change who they are both physically and mentally because they don t feel right the way they were born but they put themselves farther away from fitting in because they break away from who they really are...  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/98 & \cellcolor{green!5}1.02 \\  \hline
  \cellcolor{green!27} Who they really are  is what gender they feel the most comfortable in - They're more themselves in the gender they want to be. Also, what do you think makes somebody a certain gender? If it's genitals, then gender reassignment makes them the gender they're reassigned to. If it's hormones, this person's already a male. (Idk if they've had surgery.)  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5}so how is this woman gonna get a penis.. magically grow one?  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}just wait untill shim regrets it lol btw u have a thing called gender dysphoria  it is a mental illness   & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}i hope she said no and gave you to a mental hospital,for your good kiddo  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}Fucking weirdo!  & \cellcolor{green!27}Weirdo & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}Freak of Nature  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}Freak of ignorance  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}Retard....this is pretty unhealthy...You was, are and will FOREVER  be a women.....  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}reverse gay?  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}You're still a woman belive it or not.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}I should just pretend to be a transgender and say I was a girl ,so I get a fuck ton of basic hoes telling me I m strong  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}When you have a mental condition  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}You're still a woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}ur still a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Fucking freak  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}16 when you started? Maybe i'm old school and ignorant... It just seems too young. Although... maybe it's better to adjust earlier... I dunno how I feel about it!!! but i wish you all the best.  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}You'll still be a woman in my eyes  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Bryan U  because changing sexual organs on a teenager in a way that can never be undone is harmless right? Because tax payers paying for said surgery's when they should be classified as cosmetic is fine right? Because giving parents permission to change their childrens body's before they have even gone half way through puberty is harmless right? Fuck off. If a grown man wants to change fine. But that's not what's happening here.  & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}https://williamsinstitute.law.ucla.edu/wp-content/uploads/AFSP-Williams-Suicide-Report-Final.pdf Five seconds to find a decent source. You missed my point however, The rates in witch trans people kill themselves does not change Pre or after hormones and surgery, Meaning its not effective at anything in the vast majority of cases. As well as costing tax payers a large amount of money for cosmetic/Non necessary surgery. Giving someone who is mentally Ill the ability to change their body is not a good idea. And i refuse to believe something that comes with a minimum of 50  mortality rate is not an illness. that 50  comes from the best cases btw. They need help, not a knife. and sure as fucking hell not a knife under 21.  & \cellcolor{green!27}Witch & \cellcolor{green!27}Female age and physical appearance & \cellcolor{green!27}1/117 & \cellcolor{green!27}0.855 \\  \hline
  \cellcolor{green!5}FeedMeSalt  because changing sexual organs on a teenager in a way that can never be undone is harmless right?  This can be said for any cosmetic surgery really. It's their decision after all. It's not as black and white as you think.    Because tax payers paying for said surgery's when they should be classified as cosmetic is fine right?   In almost all countries, it's not free at all. You still need to pay it yourself. This is generally the case with cosmetic surgeries.    Because giving parents permission to change their childrens body's before they have even gone half way through puberty is harmless right?   I don't think there has been any evidence that someone has suddenly gotten attracted to the different gender after puberty. However there are kids who pretend to be straight until they are teens, then come out of the closet. Plus these children are carefully monitored and given counseling. It's not as easy as you think.  If you are fine with the surgery but not the age, then you should edit your original comment to reflect that.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/181 & \cellcolor{green!5}0.552 \\  \hline
  \cellcolor{green!27}OH damn so you have gender dysphoria. Well you sure look like a male, but if I knew you are biologically a female I would still call you a she.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}Why the  fuck would you wanna be a different gender.. it means you're fucked in the head. You're gonna kill yourself probably in future. It's a big change man. I mean girl  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}You have a mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}That s gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}This is becoming a new fashion. I am so bored, what I will do? I will turn myself into opposite sex.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}I've got no hair at all. I'm your same age  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Keep up the good work !!! And stay happy my friend ! You have came along way in your transition !! Congrats !!!  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}Lol i bet if u punch him, he would cry like a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}i dont know how trans thingy works why do they wanna chnage thier gender i mean why whats wrong with the existing one  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}This shit weird  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}Being transgender is a mental illness. And I doubt anyone can change my mind.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}What You Egg V.2 being a weeb is a mental illness  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}And you also grew an Adam's apple? Yeah friggin right  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}see a mental health doctor before the surgeon  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}once woman, always woman. sick times  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Pepe SEX is different to GENDER, informe your self a little bit  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}yeah sick times when people like you spread ignorant, hateful speech. on things you don't even fully understand. gender dysphoria is real and causes physiological changes in the brain. if you did research you'd know that. he's a man.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}disgusting tranny  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}She basically promoting mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}she probably got a pussy under those jeans  & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27} ZebraSnot you don't get it don't you, don't worry like 10 year old you'll get it sooner or later.     & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}ZebraSnot you sound dumb as fuck. you clearly know nothing about trans people, so you shouldn't be talking at all. no one is changing their body with pills because there are no pills involved. do research before you try to speak on something you don't know shit about.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}Those who shit on you are pathetic, denying reality and probably jealous. They want to manipulate others to do what their sick mind wants, so every LGBTQ  person, come out of the closet if you havent already. Please please please dont be afraid of it, because it's completely normal. We should be treated just like cis and/or heterosexual people, we're no diffrent than them, we are just like nature wanted us to be. All that mental illness shit should've stayed where it was, and if your argument is exactly that, sorry, your info is outdated and you didn't even live in those times! Dear LGBTQ  people who decided to be true to themselvs and others, you can be proud you decided to live your life as it was meant. And you Benton, you are doing great, boy!  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/137 & \cellcolor{green!27}0.73 \\  \hline
  \cellcolor{green!5}Youll never look anything past a 15yro boy with female to male transition  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}You can say,  You  when talking to a woman what difference does it make? for example with your logic  She cab is here  make sense? that's what i thought  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}Like I said, it's an example. When saying  You look hot af  you don't have to take into consideration the gender of that person.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}you got the big gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}He's a guy, a transgender guy but a guy nonetheless. What's with all these stupid ass comments saying he's a girl? Ya'll need to take a class or something on how to be respectful.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}you look better as a manly, but I wonder how dating works, what woman would go without the pinapple apple pen? or are you not into women? maybe bisexual men might be really into you, OBVIOUSLY not gay men.  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}Why are you taking steroids ? Does that not apply to transgender people?  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}Can't change your gender.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}Retro Frog not an opinion.  & \cellcolor{green!5}Frog & \cellcolor{green!5}French & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}so you are gay? or...  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}alright everyone in the comments are being cunts so ill put this lightly but scientifically so dont expect pussyfooting 1) chromosomes determine sex not muscle mass and T 2)no matter what i dont believe this mental illness should be etertained and i am sorry for you that you feel this way 3)i know you think that t is the only way to make your gender m but its not gender is just the male characateurs so going to the gym and weightlifting makes you m eventually  4)unless you were xxy you are and will be a woman  5)suciide rates stay the same after and no its not down to bullying  6)it's not you i want to fight it's the doctors who know better despite what i think of this i do wish you a good day mate (and i will call you mate but thats as far as i'll stretch bud)  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/151 & \cellcolor{green!5}0.662 \\  \hline
  \cellcolor{green!27}Wow!! you look amazing, I could never tell that you 've ever been a woman!  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}The sheer fact that someone allowed a 16 year old to do this is child abuse what 16 year old isnt confused and fucked up in some way. This is a cop out a permanent solution to a temporary problem  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}This is disgusting! Now I'm very skeptical if my girlfriend is a guy or not! This sex change shit should be strictly illegal.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}hell nah bro. this shit is fucking crazy. i cant even tell u were a girl. this is why i have trust issues  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}What's the point of going trans if s... he's gonna act like he... his 'original' gender though.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}Siren cis means they re the same gender that they were born with. They feel that way and act that way, and are comfortable in the gender that they were born with.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}Siren why is transgender allowed in US you are born that gender for a reason.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}How does being transgender in any way shape or form justify rape..? You're disgusting.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Michael Taylor actually, it has been proven that a transgenders persons brain correlates with the sex that they act and feel like, hence why they dislike their original puberty, I don t have a specific website but it was found on multiple sources when I looked it up. Please revise your opinions by using a more open minded view and ideology.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/60 & \cellcolor{green!27}1.667 \\  \hline
  \cellcolor{green!5} SRI HARI  Even though he is technically a female, I would consider any man who finds him sexually attractive as gay.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}toothless toe I would consider anyone who is sexually attracted to her weird.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}thicc question what does this achieve? Do you think a girl will see your comments and wanna fuck you? You ll make him want to stop taking testosterone? You ll suddenly rid the world of transgender people? Because surprise surprise, he knows that his chromosomes are the same, that s not something he can change and if he could he would. Scientifically gender dysphoria is eased or even cured by body transition, which what this is.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}shes still a woman. just a mental disorder thinking she's male and therefor trying to become one but it's biologically not possible  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}Kalle Kallenkallela wtf is wrong with you?! You need mental help  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}Z!NDa god has anal sex with african kids DAILY  & \cellcolor{green!27}African & \cellcolor{green!27}Black & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}gay xd  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}thot trying to sneak in the homie club wont work at all  & \cellcolor{green!27}THOT & \cellcolor{green!27}Female sexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}Hormones aren t the correct way to treat gender dysphoria.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Aiden TheGayTrans oh right. So suicide is the correct way to treat depression? This just keeps taking it to another level, just continuing the mental illness.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}Paws Yes, gender dysphoria is an illness. But there's a way to treat it. Hormones and surgery are the way. Just like anti-depressants treat depression.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}Aiden TheGayTrans I m not saying it s just a phase, moron. And you really don t understand. Hormones aren t stopping the problem, it s just going WITH the problem. You can t change your gender, simple.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}Paws Okay first, the insult is not needed. Second, I understand completely. And third, you can change gender. That's how transgender works.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Aiden TheGayTrans if our can t handle an insult, that s sad, and if you don t want to be insulted, don t make assumptions about people who disagree with you. And no, you can t change your gender. Your chromosomes will still be XY or XX. Male is male, female is female.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}Aiden TheGayTrans Oh you bet. You can take off some body parts, put some new ones in and take in hormones, but your chromosomes will still indicate you re your first gender. You cannot biologically change your gender. And just as you think an insult is rude, I find rude assumptions about people who disagree with you to be rude. And you aren t doing it politely, because you wouldn t have made the assumption that different opinionated people that say  it s just a phase  is part of the problem. They re wrong, but it doesn t make the problem worse, and I really don t know very many people who say that. They used to for sure, but nobody really says that nowadays.  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/118 & \cellcolor{green!5}0.847 \\  \hline
  \cellcolor{green!27}Paws Um, my mother said it to my face. And I'm in a trans support group who have had it said to them. I know what I'm talking about. I know a lot of people who are helped by the transition. And biology can change. What about all the people with X chromosomes, are they still a woman? Or the ones with XXY, are they still a man? Or the ones born with both body parts? Biology can't explain everything. Science is always being proven wrong by new experiments. You can't count on only that. And it's been proven that trans people are literally not the right gender. It's been researched. And I think it's ignorant and insulting of you to come here and put down people because you don't agree.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/131 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}Saying you can take away gender dysphoria is like saying you can take away homosexuality. It's fucking dumb. Comparing it to depression is also dumb, since depression can actually harm the person who suffers from it physically, either by self inflicted wounds or even suicide. Gender dysphoria is harmless to the person  suffering  from it and the people around that person.  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}Kaneda gender dysphoria causes suicide and self harm too  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}Kaneda and no one said you can take away gender dysphoryia. Like anti depressants they just keep it down  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}Unknown Comics that would mostly be attributed to depression, which they probably have from people like this telling them to kill themselves and that they are freaks. There's articles that have been written by people who have gender dysphoria themselves, and they say that they do in fact have depression, saying things like they feel like freaks and that they don't fit in, again, most likely attributed to comments just like these. Obviously not necessarily online, but irl too.  Other articles written by psychologists themselves who say that people with gender dysphoria have more mental illnesses mostly due to the way they are treated.  Fuck, even I would be depressed if my parents thought I was a freak.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/117 & \cellcolor{green!27}0.855 \\  \hline
  \cellcolor{green!5}Asher TheGayTrans No you can't change your gender! GENDER IS A BIOLOGICAL THING AND FOR YOU TO CHANGE IT WOUKD MEAN YOU WOULD HAVE TO CHANGE EVERY FUCKING CELL IN YOUR BODY  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}oh and who are you now mr psychologist? what are people to do? live their life depressed and unhappy because miserable assholes like you can't comprehend or accept them? since when did living for other people's satisfaction become the norm? you can't electrocute gay out of someone, you can't do that for being transgender either. the only Reason people even have gender dysphoria is because their brains are PHYSICALLY structured differently. look up the psychology behind it. just like with intersex kids, trans kid are born with brains reflecting one sex and their genitalia another or a mix of the two, and because the brain develops first it only makes sense that you'd accept that to be the correct gender.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/120 & \cellcolor{green!27}0.833 \\  \hline
  \cellcolor{green!5}transgender is not         R E A L  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Lol gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}You have as much facial hair as me in this video and I am 19 years old and was born male lol  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Impressive. Adam s apple too.  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}NotSpooky no thats wrong pls link the source to your opinion then   Furthermore it is selfdestructive behavior bady dismorrphia called it comes in all diffrent shapes in every shape its getting treated except with the gender one thats normalized  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}Cave Beast the WHO and CDC now don t consider it as a mental illness anymore but a sexual health condition.  Look at the suicide rates for gay people back then, they were much higher then, when more people were homophobic, than they are now.  It s the same with trans people right now, once other people see transgenderism as normal suicide rates will drop.  This is because of discrimination.    And if you guys wanna pull that  I had 2 trans friends kill themselves becuz for some reason AFTER transitioning I feel depressed as fuck because I feel as if I am a man or woman which is totally related to suicide rates,  I ll give you an actual example of someone who I know in real life.  They were born female and transitioned to male.  When they told their parents, their parents agreed to help them transition.  When the parents broke the news to the grandparents, the grandparents were in fucking tears and unhappy as fuck.  They transitioned, but they loved knowing that their grandparents as well as society would look down on them.  This made him stay stuck in his room for a while until years later he finally got the confidence and self-assurance to go out and be himself.    This is what transphobia does.  Had his parents and brother looked down on him he probably would have killed himself.  This is why we need to be more accepting, so that trans people don t fucking go through depression and commit suicide.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/250 & \cellcolor{green!27}0.4 \\  \hline
  \cellcolor{green!5}Cave Beast one in six highschool students have thought about suicide.  Here are statistics of LGB suicide rates from 2015, 3 years ago.  http://www.suicidology.org/Portals/14/Re-Formatted 20LGB 20Youth 202016 20Fact 20Sheet.pdf?ver 2016-11-16-105952-633  Over 60  of LGB people have thought about suicide.  Imagine if this was 2000, these percentages would be way higher.  Trans people having a 40  suicide attempt rate at this time is not unrealistic as they are only just now becoming more accepted within society.  This source states that the main reasons for these suicide statistics in just LGB people is homophobia/discrimination.  The fact that trans people are more oppressed than LGB people nowadays would make sense that trans suicide rates are this high, right?  Also gay suicide statistics back then are extremely similar to trans suicide rates now.  So what s your point?  No where near as high?  Horseshit.   There s a problem with you if everyone you know hates you and you kill yourself.   Okay, tell that to the kids who get bullied and kill themselves.  Or parents who verbally abuse their kids.  Is there something wrong with these kids?  Do they have mental illnesses too? http://www.bullyingstatistics.org/content/bullying-and-suicide.html  If everyone fucking hates you I bet you would be sad about it.  Not everyone is emotionally identical to you.  Some may kill themselves if they were bullied, just because you wouldn t doesn t mean those who does have something wrong with their brains.  Before you spout transphobic shit to demonize transgenderism learn your shit.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/235 & \cellcolor{green!5}0.426 \\  \hline
  \cellcolor{green!27}NotSpooky Not true at all. You are a postmodernist with no data on your opinion at all. There is no data that tell is discrimination or bullying leads to people killing their self. If that were true  and we live in a racist society where blacks and poor people are bullied then why don t they kill them selves at a higher rate than white men? The only time that a group of people have killed themselves at 40  rate was Jews during the holocaust who were being gassed to death... Trans people have it much easier and they have a mental illness that is being over looked.  & \cellcolor{green!27}Racist & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/107 & \cellcolor{green!27}0.935 \\  \hline
  \cellcolor{green!5}It actually is.  The study you're referring to is a Swedish study that is often misquoted. Newer data shows that plenty of those who transition get improved quality of life.  https://www.liebertpub.com/doi/full/10.1089/trgh.2015.0008  A lot of people also take said study out of context, this is a very important part   For the purpose of evaluating the safety of sex reassignment in terms of morbidity and mortality, however, it is reasonable to compare sex reassigned persons with matched population controls. The caveat with this design is that transsexual persons before sex reassignment might differ from healthy controls (although this bias can be statistically corrected for by adjusting for baseline differences). It is therefore important to note that the current study is only informative with respect to transsexuals persons health after sex reassignment  no inferences can be drawn as to the effectiveness of sex reassignment as a treatment for transsexualism. In other words, the results should not be interpreted such as sex reassignment per se increases morbidity and mortality. Things might have been even worse without sex reassignment. As an analogy, similar studies have found increased somatic morbidity, suicide rate, and overall mortality for patients treated for bipolar disorder and schizophrenia. 39 ,  40  This is important information, but it does not follow that mood stabilizing treatment or antipsychotic treatment is the culprit.  http://www.medscape.com/viewarticle/827713  Largest study to date.  At entry into the study (baseline), the most common comorbidity in both groups was depression, with a 24.9  incidence in MTF subjects and 13.6  in FTM, according to Dr. Asscheman. He noted, however, that the frequency of depression varied greatly among the study centers. Even after treatment, 26 (2.4 ) of the MTF subjects and 7 (1.4 ) of the FTM subjects still reported depression, leading Dr. Asscheman to tell the large audience,  Sex-reassignment treatment does not cure depression.   That'd be about 90  decrease of depression, even if the clinical illness in itself can obviously never be fully cured.  We also know that people who are treated for dysphoria early and who are allowed to grow up in the gender of affirmation have suicide rates no higher than the control group (again, suicide seems to be more related to prejudice and discrimination against trans people, not their transition situation).  http://pediatrics.aappublications.org/content/early/2014/09/02/peds.2013-2958  Transition isn t magical, isn t easy, and doesn t solve every problem transgender people face. Unemployment rates in the transgender population are significantly higher than what the general population faces, along with elevated rates of discrimination, harassment and violence. The data tells us that the best ways we can reduce the transgender suicide rate are by affirming the identities of transgender people and providing safe and supportive environments. A supporting family has again and again been shown to correlate highly with reduced transgender suicidality.  But, TL DR, while transitioning will not always completely fix a person for life, it CLEARLY does help in many, MANY cases and in the end it's a decision trans people themselves make for the sake of easing their dysphoria.  Now, gender dysphoria shouldn't be normalized as something that is  cool  or  special , because it's a genuine mental condition, and it's shitty as all hell. It's the source of anxieties and depression because one cannot stand seeing themselves in a body where they feel they do not belong. And hormones are also NOT easy to deal with, but in the end, it could also save your life depending on how much dysphoria you're struggling with.  However the fact that trans people exist and are just trying to live their lives like any other person SHOULD be normalized.   If a transgender person wants to go ahead and take the risk in hopes of a better life, then let them be. Discrimination doesn't help their case.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/615 & \cellcolor{green!5}0.163 \\  \hline
  \cellcolor{green!27}FeedMeSalt  Homophobia doesn t exist anymore because gay marriage is legal.  Racism doesn t exist anymore because slavery is abolished.  Sexism isn t real because they have equal rights.   This is your logic.  All of these exist, including transphobia, and if you deny that you are delusional.  & \cellcolor{green!27}Racism & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}Parking Lott Gay and bisexuals don't have fucking suicide rates Dubble the national average. Black people don't kill themselves 50  of the time when people are racist. You know why? It's not an illness. You shot your own argument down. Nothing will ever be fully accepted, the thing is, a healthy human won't fucking drown themselves because they don't feel like they are accepted or fit in. Obese people don't even have have mortality rates as high as the suicide rates. You think they feel comfortable in their body's? Probably fucking not. Jesus Christ you defending something so harmful is disgusting to me. For something to drive a person to end them selves, an act so selfish and fundamentally wrong. That's an illness.  & \cellcolor{green!5}Racist & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}1/123 & \cellcolor{green!5}0.813 \\  \hline
  \cellcolor{green!27}FeedMeSalt last time I checked it s way more socially accepted to be fat, gay or black than it is to be transgender.  I mean, look at you, you re a great example of this.    I was not making the argument, if you are oppressed, your group of people will have significantly high suicide rates.   I was making the argument  the more oppressed/discriminated against you are, the higher your suicide rates are.   And the fact is, people like you are the reason discrimination is very well alive against the trans community.    Anyways, LGB suicide rates are still much higher than straight suicide rates, so that completely defeats your point on how oppressed people don t have higher suicide rates.    You know, there are statistics that show post transition trans people have an improved quality of life than pre transition.  Look at the sources in this comment thread, pre transitioned trans people are more likely to kill themselves than post transition.  So what you re against is actually the most effective way of reducing suicide rates because this has been repeatedly shown to reduce suicide rates in individuals with gender dysphoria.    Please, tell me what you think would be a better method of reducing suicide rates among those with gender dysphoria.  I d really like to know.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/210 & \cellcolor{green!27}0.476 \\  \hline
  \cellcolor{green!5}it is caused by a mental disorder, that causes them to feel disgusted in their own body. It will never change.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Lucas Nicoara pretty sure psychological treatment wouldn t work since it doesn t fucking work for gay people  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}Lucas Nicoara and anyways, most trans people would not consensually go under psychological treatment for good reason.  They don t WANT TO.  Just like gay people didn t.  You claim you know what would be a better solution but similar cases in the past show it s not.  If a trans person really wants to go through psychological treatment, I m pretty sure they would have.  Unless you re advocating for them to be forcefully put through this?  Now that s actual evil.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/77 & \cellcolor{green!5}1.299 \\  \hline
  \cellcolor{green!27}Parking Lott Being sexually attracted to the same sex or both is found in countless places in nature. It has fucking nothing to do with feeling as though you are the wrong sex. Get out of here. Gender sex and sexual orientation are not the same fucking thing you monkey.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}FeedMeSalt you re repeating the same shit and I m refuting it.  This is the basis of transphobia, you re too blinded by prejudice to fucking think.   Yeah, but would their suicide rates be as high as 50 ?!  Therefore, say it s a mental illness!     I ve literally explained why that is, and given you evidence and sited sources.  Yes, oppression leads to depression, which leads to fucking suicide.  Society will change for the better of trans people as it has for black and gay people (though of course not completely).  Suicide rates will drop once people become tolerant.  It s disgusting how you act like you know what s best for trans people but you don t fucking know shit about how trans people feel.  Trans people unanimously agree that transitioning is the best option.  We ve shown you evidence of improved quality of life for post transitioned trans people, which means performing sex changes literally reduces suicide attempts instead of not performing surgery.  And that isn t debatable, that s objective and fact.  You can disprove this.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/168 & \cellcolor{green!5}0.595 \\  \hline
  \cellcolor{green!27}Matthew Clifford trans people and the WHO classify it as a sexual health condition.  Just like erectile dysfunction is a sexual health condition.  Just because someone feels sexually unmotivated would not mean they re mentally ill.    A mental illness is something that directly causes impairment to the brain.  Gender dysphoria may cause mental disorders like depression but that would not make it a mental disorder.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}I believe this is a mental illness. These people are only hurting themselves, and then want to play the victim card. It's not right  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}FeedMeSalt  you are the one making the claim you have to provide me proof    Google the proof   Fuck off with your hypocrisy.  And no I m not making the claim, you are.  You are saying it is a mental illness, and I m debunking your shit.    It s just like the religion argument.  Christians and other religious people make the claim god is real.  Atheists aren t required to disprove god.  You need to provide evidence that I haven t fucking refuted to prove to me that it isn t a mental illness.  Stay inside your bubble of cognitive dissonance, because you bring nothing to the table and expect me to provide more sources when you haven t even provided me one.  You re transphobic.  You don t know what s best for others, so don t try to decide for them.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/131 & \cellcolor{green!27}0.763 \\  \hline
  \cellcolor{green!5}they should stay the gender u are fuck your looks if your trans i will call u what u were born as fuckin hell they can kill themselves cause idgaf  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Cave Beast so we have to stigmatise mental health conditions? There's already a lot of stigma.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}NotSpooky true I nearly killed myself the other day and it was cause of discrimination due to me being transgender  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}David Pinkerton it's not hard you fucking moron. I gotta go through life knowing I won't be able to save all the children who are being slaughtered right now in parts of the world. You are just dealing with some bullshit mental illness that you refuse to acknowledge. Imagine thinking not having a dick is hard to deal with. Get fucking over yourself you whiny bitch.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}Advenco it is a crippling mental disorder yes so I also feel bad about not getting to save all the children? It is diagnostic real symptoms and 41  of trans people attempt suicide, I ve been discriminated against, not so much rejected thankfully, but the symptoms of being uncomfortable are hard to deal with, shut up you whiny little bitch tits fight me  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}David Pinkerton yes it is a mental disorder it doesn't mean you accept it you idiot. Fighting is not going to help you.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}Advenco you cannot live with crippling gender dysphoria caused by a misalignment between brain and body so you have to transition to help yourself, everyone is entitled to live a happy life that is not filled with pain and distress do ya understand?  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}David Pinkerton No, that's not how you cure it you fucking moron. There are also conditions where people have believed they are babies or cats. That doesn't mean you transition them into that you idiot. It's a MENTAL ILLNESS and this is a scientific fact. You don't enable illnesses. It's extremely dangerous.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}Advenco you are one stupid morherfucker ask any doctor they will tell you this is the cure. A brain scan shows that the brain is the opposite gender. They re literally in the wrong fucking bodies!!!!!! There s medical fucking proof and any licenced professional will tell you that  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}Advenco the mental illness that often accompanies gender dysphoria is depression anxiety etc due to direct discomfort with their gender and body it is extremely difficult to deal with, extremely extremely uncomfortable feeling. Just fuck off and leave them alone.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}David Pinkerton lol that isn't proof for shit. If that's the  cure  why do trans still commit suicide? Trans people in the west never get discriminated against yet they still kill themselves even AFTER their bullshit treatment. It's because IT'S NOT THE CURE. And besides, no matter what you do, you are still the gender you were born with at birth. So nothing you do will change that. Fix your illness instead. By the way answer my question. There are people who believe they are a baby or a cat. Why do you ignore them? Why do you only care about gender?  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}Advenco otherkin and etc isn t lgbt they really are mentally ill. Transitioning can t always cure everything as for eg you will still have smaller muscle mass, or deeper voice etc but it massively alleviates gender dysphoria. I m in Ireland and I experience a lot of discrimination, couldn t join the army, couldn t be a drummer in the marching bands, gay marriage ain t even legal here.  & \cellcolor{green!27}LGBT & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}Advenco gender dysphoria is most likely caused by cross sex hormones in the brain, it s rare but intersex is also rare, is prenatal  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}I can't believe this society supports this trans garbage. She was born a girl and nothing can change that fact.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}Suicide rate before and after gender reassignment surgery is the same. It won't fix anything.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27} 10,000 subscribers with no vids? That's their problem. They're the offended one's. Frankly, I don't give a shit about yours or anyone else's feelings. I think our world today places too much value in political correctness. We need to think more practically, and not so much with our feelings.   This whole transgender movement is a load of people with a disease that needs to be treated, but with cognitive behavioral therapy instead of chopping off our genitals. End of story.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/80 & \cellcolor{green!27}1.25 \\  \hline
  \cellcolor{green!5}I'm not asking anyone to care about my feelings? We're talking about major depressive disorder in the context of individuals with gender dysphoria. I don't have either of these disorders so I'm just making an observation from an objective point of view.   All I said was that I do not feel that enabling people to mutilate their genitals is the right answer to the problem. Cognitive behavior therapy and other proper forms of treatment are.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27} Hey. Omw? please tell me what is so wrong about somebody being happy and changing their gender  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}Nobody said its wrong to be happy, but people are allowed to have opinnions and beliefs which both make transgender people unhappy, so we should all abandone our opinnions and beliefs just because some poeple who cant decide what gender they are got offended? And before you tell me that our beliefs are to exterminate LGBT poeple Id want to assure you most people do not think they should be killed or hurt, people simply think that they are sick and certain people have a problem when LGBT community are treating their conditions as  normal  and forcing it into public. Straight people dont care about LGBT people and they dont have a problem with them, they have a problem when they start to normalize their conditions. Whats next? Autism is normal? Pedophilia? After all pedophiles are not mentally sick, they think like normal people and are capable of independence, but they have certain sexuall drives towards kids, they were born that way and had no choice in the matter, so should we normalize pedophilia? I think not.  LGBT people are not pedophilles, i know, but they have similar disorders none of which are normal and none of them chose to be born that way. Its just that pedophilles disorder makes them a predator. So its seen as not normal and LGBT is suddenly becoming normal just because its not predatory...they are both abnormalities.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/233 & \cellcolor{green!5}0.429 \\  \hline
  \cellcolor{green!27} World of Stupid don't you ever dare compare the LGBT community to pedophiles, we want acceptance and love, not to rape kids. PEDOPHILES ARE NOT PART OF OUR COMMUNITY. There is a drastic difference between loving the same sex as you, and wanting to have sex with children. And by the way you are putting it sounds you have a huge problem with the LGBT community.       I can see why your name is World of Stupid  & \cellcolor{green!27}LGBT & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5} Sour System if I chop off my arm they would call me crazy .  Chop off my dick and I'm a sane hero  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}This video pisses me off because this person clearly doesn't accept who they are as a person. Like I thought it was just a person that had no choice around this, but no you clearly just wanted to do this because you have gender dysphoria.... just childish. Maybe grow some balls and accept who your really are LITTERLY!  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}Fucking gay. Burn in hell  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}this is literally mutilating your body...... crazy shit, u feel like a dude why would you have to inject yourself with all that shit???  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}Oh now you went from a chick all the way to a soy boy.  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Darth Vader so you don't like what someone does, so you want to make it illegal? Next you'll say pineapple on pizza is illegal or something dumb like that  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}Darth Vader google gender dysphoria. It's a real condition and transitioning is a way to deal with it. That's why it's legal. It's definitely not a choice, because if it were, then I'd bet you most people wouldn't want to transition because of all the work you have to go through.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27}Darth Vader every single person has testosterone in them, as well as estrogen, you fucking retard.  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}U still have a pussy or? xd  & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}how the adam's apple can grow ?  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}If gender is just cultural, why even take hormones? Doesn't that kind of demonstrate how non-cultural gender is?  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}SHE has XX chromosomes all over HER body, not XY, and SHE cannot produce testosterone without external influence (aka going on juice), and SHE cannot produce sperm, and SHE does not have a prostate, and SHE does not have testicles, and SHE has a vaginal cannal from which SHE pees from.  Seems to me the primary aspects are of a woman, regardless of the secondary aspects that come with testosterone consumption, SHE cannot change the primary characteristics that come from birth, chromosomes, thinner skin, weaker bone structure, VAGINA, etc  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/89 & \cellcolor{green!27}1.124 \\  \hline
  \cellcolor{green!5}Man O' War okay but...women don t pee from their fucking vaginas, dumbass. Both men and women have this thing called a urethra. It s a small hole located a few centimetres up from the vagina and is used explicitly for urinating as a female, while males ejaculate and pee from the same hole. Also, nobody s arguing that he isn t still, scientifically, a female. There s a difference between sex and gender, sex being your physical attributes (genitals, xy or xx chromosomes, etc) and gender being the way you identify. Just because they re basically still female doesn t mean they can t identify as male. There s a lot to take into consideration here. We re humans, not animals, nothing is black and white and in the end, basic human decency is to let people be who they want to be. (So long as they re not hurting anyone.)  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}She can identify as whatever the fuck she wants, but I will identify her as the gender she was born in, no further questions, she cannot force me to address her as a him when it's clearly not the case, it goes against biology, and I like exact terms, not made up stuff that can vary from day to day, one day she can identify as male and another she wants to be identified as a female. I will not buy into this bullcrap. She is a she, her family can address her as a he, I do not mind, but not me.  Same thing with the CIS gender bullshit, there is no such thing as cis gender or binary or whatever the fuck, there is male, female, and then there are mental illnessess (hermaphrodites and some chromosome syndromes are some exceptions when the person is born with both genders, only then can the person be allowed to choose one or the other)  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/163 & \cellcolor{green!27}0.613 \\  \hline
  \cellcolor{green!5}Man O'War it's literally just called being a decent fucking human being.  it goes against biology  who the fuck cares??? If someone wants to be called he, or she, do it?? You don't have to agree with it or anything, but for someone to go through so much effort to transition and then still be called the thing they specifically don't want to be called after all of it? That has to fucking suck. People like you are why trans people kill themselves in the first place lol  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}Man O' War Why are you so obsessed with trans people, you creepy fucking retard?  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5} Man O' War Have you learned biology past basic sixth grade stuff? It sounds like your grasp on sex is very rudimentary and absolutely steeped in social context.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27} PrinceGalaxy Because imagine a transgender guy comes up to me looking like a woman and presenting himself like a proper woman. Had hormonal treatment and all. Comes up to me and starts flirting. I have no fucking clue what a real woman is anymore. And not to be rude or anything. But I like my women fertile. And not men with inverted penises and testicles. As not being able to have children is a real deal stopper to many men.  I have a huge fucking problem with trannies because they think they can go to the dating market as if they were the opposite gender, when in reality they are being dishonest from the get go.  When dating, a transexual needs to say what they were born like to avoid problems when things get intimate.   If we can bypass this big issue for me, then we can agree, they can be called whatever the fuck they want. (as long as it's she or he, I won't be using made up words for made up  genders )  Because let's be honest, if a man finds out he's been making out with a tranny when before he thought he was a woman, there is a big chance that tranny is getting his shit beat the fuck out of him. Because in the end. A tranny is not a lady, but a gay man/woman on steroids basically  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/233 & \cellcolor{green!27}0.429 \\  \hline
  \cellcolor{green!5} Man O' War I think you're a little confused. Transgender guy that looks like a woman??? Transgender men look   identify as men. Transgender women look   identify as women.   And, inverted penises and testicles??? i don't think it's qualified to be called that, as the surgery for trans women looks really fucking good. And it's possible for a woman who was born as a woman, to be infertile, I don't think someone would dump the love of their life just because their infertile, you know what i mean?   Not to mention a lot of trans people already mention they're trans, WAY before they get to the stage of having children. Or at least it's best for them to go to a dating site that's welcome to lgbtq .  If some man beats the shit out of a trans woman just because they made out, that's on him for being transphobic. Trans women are women, and trans men are men. Maybe not 100  biologically, but who cares?? All trans people are different, some have the entire full surgery, and some don't. there's always adoption, and if you dont want to date someone because their trans for the sake of not being able to have biological children, then that's fine too, but it's best to be nice about it.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/217 & \cellcolor{green!5}0.461 \\  \hline
  \cellcolor{green!27}Man O' War Newsflash: Not every woman is fertile anyway. If you don't want to date a trans woman, that's fine. But don't act like it's because you only want a fertile woman. Because A. infertile women exist, and B. Just because a woman is fertile, doesn't mean she wants to have kids. To be honest, I hope no one ever has your kids until you learn how to mind your own business and grow up.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/76 & \cellcolor{green!27}1.316 \\  \hline
  \cellcolor{green!5} Jamil Listen mate, where I live, this shit doesn't happen. And it never will, because it's not retarded USA.  Go be a tranny whenever you want, but not in Portugal. Stay the fuck away  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27} Man O' War Hey, it's you who's transphobic okay? We all know it's your opinion, and I can blatantly get behind defending one's opinion, this is a little different than you think. Study the topic.  Trans men and women both can have severe mental illnesses because of their born gender. I have a friend who told me their story, in which before they realized how they identified they hated absolutely everything about their body. Their voice, their natural curves, their eyes, their jaw, their hair, the way they walked, the stereotypes of their gender, you fucking name it, they had a literal anxiety attack over it. It was devasting to their mental health.  Only when they realized they were trans did things change.  They did what they could to be more like who they wanted to be physically, and they're still waiting it out before they can finally get testosterone.  They're fighting a literal mental health issue because they identify as male and not female. They're dealing with it and taking the criticism. Most of them won't fuck with Transphobic people because they know it's useless, but I'm proud to back them up. I'm also proud to say that ever since I've accepted the fact that I'm genderfluid my life has gotten so much easier. For me it's call me whatever the fuck you want.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/225 & \cellcolor{green!27}0.444 \\  \hline
  \cellcolor{green!5} Depresso 101 I haven't a single clue on how being  genderfluid  (whatever the fuck that means) can improve one's life. As a man, I could not imagine a healthy happy life if I characterized myself as  genderfluid , but I am also not living in the land of the fools, aka, US.  In my country in Europe, people aren't obsessed with gender or race... Because we have better shit to do than cutting up our genitals and injecting hormones in our bodies.  I'll say it again, I don't give a fuck if you or whoever the fuck cut your genitals and stat injecting anabolic steroids.  But if children are influenced by theses transgender depressive lowlives. And are encouraged to cut up their own genitals. Then we have a fucking problem.  & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}1/129 & \cellcolor{green!5}0.775 \\  \hline
  \cellcolor{green!27} Depresso 101 It's because of people like you that Europe and America are shifting their politics to the right wing, the proper wing, that worries more about the economy  than the feelings of a retard that decides it's a good idea to cut his dick off for attention.  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}You dont even look trans an you dont act gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Good job dude!! Honestly like I m scrolling through all these comments and man, I wouldn t have had the courage to post this video if it were me. People seriously feel it s necessary to impose their beliefs on strangers and honestly? People that think gender is an absolute concept really, really confuse me. You keep going on, dude. You give me hope.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}Still have the chromosomes of a woman so I mean you re only changing your appearence  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}guy with a pussy  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}alien maybe  & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}He still looks gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}your granny tranny wait no u  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}You are an Idiot, nothing will change, thats fact too.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}I'm gay, and I clicked on this literally because you're a good looking guy. That testo's doing you good! Congrats!  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}Maybe rather than being gay you should have just found her before she went down this destructive path (and same for you). Could have saved yourselves and the world a whole shitty mess. Just proves there's a girl for every guy and vice versa.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}What the actual fuck, you are stupid. Let people be who they want to be, its also not like its a choice if they feel like they are gay or the opposite gender.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}Thank you for your absolutely inaccurate, medieval, misinformed, heteronormative and downright dumb advice. Unfortunately for you, you're living in 2018, and this is not your world alone anymore. Please take several seats. Much love.  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}Poker Face has none, how ironic! I am not the one promoting somebody being something they are not, that would be you lot.   I love how you came up with all these non-applicable words to discount my opinion as if they could, by their cumulative weight somehow refute the obvious. I also just adore the idea that you lot have somehow taken over and are running things now and that somehow reciting the date makes your opinion more meritorious.  You lot are literally clinically insane and dragging the susceptible bits down into the abyss with you. I don't really mind as it trims the fat off the carcass and makes it more fit in the end, but that doesn't mean that I have any empathy (let alone sympathy) for militant mental illness nor the negative impact it has on so many individuals and families.  On the plus side my lot are actually having children and teaching them the truth about this mortal sphere in time... so there's that. My kids crush rainbows for breakfast.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/174 & \cellcolor{green!5}0.575 \\  \hline
  \cellcolor{green!27}See here's the real root of the issue. Waste is wrong on all levels. Doesn't matter whether that waste is of talents  (intelligence, wisdom, strength, knowledge, kindness, beauty, happiness, etc...) or material goods and services. Humanity is not a new thing and human happiness is not something that hasn't been explored in great depth and breadth. I know that you think that your pervertions are cute and new, novel and innovative, but there truly is nothing new under the sun. It has all been tried before. What you are advocating herein has a long and miserable track record that you think you can change with rainbows and unicorns and singing whatever the new version of Kumbaya is.  To any sane person the waste in human potential, beauty, happiness, productivity, increase, and so many more things of value, is stark and overwhelming. You think that everybody that opposes what you advocate is mean and unfeeling when in reality we feel more and deeper than those who have become past feeling. We mourn daily and agonize over the great misery being forced upon the world by an extremely militant and rabid minority that have managed to deceive many good people into buying their lies by attaching their fallacious arguments to things everybody is for. It is no different than those who are pro-murdering-babies re-badging as being for choice and a woman's body and her rights to it being respected when in reality the entirety of the issue is whether a woman has a right to murder a baby before it is born in a certain and specific way. You do not support diversity, human rights, nor individual identity you advocate the destruction of these things if not solely a Stalinesque partisan brand of such that pretends not to know it rabidly seeks to deprive others of choice, diversity, rights, identity etc...  But I'll leave it at this. It won't work. You will never find true and lasting happiness down this road (the real hard truth as to why deviants have such a hankering for suicide). You will only find sorrow and the endless pursuit of some new strange and winding path that you can prove to those of us clinging to the straight and narrow is a shortcut and have your long sought for vindication. You will forever remain lost and wandering while hacking brush away from the obvious traditional source your own conscience once told you about (you remember, back before you shouted it down into submission and became past feeling).  God is loving and so am I but that does not presuppose acceptance of, nor the promotion of misery. Never has, never will. Any and every good father will ceaselessly promote the true path to happiness to his posterity in whatever manner best suits its acceptance without causing additional waste and misery. Sometimes the carrot, sometimes the stick. At this point however when you are trying to take over the commons and indoctrinate youth into your miserable hoard the stick is absolutely the order of the day, the stakes are too high.  So yeah she should have waited and found the right guy to pursue all of her human potential with. That's not mean it is the nicest thing anybody could say given the ramifications (which is why that's what I led with and left it to before engaging you lot).  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/561 & \cellcolor{green!27}0.178 \\  \hline
  \cellcolor{green!5}L Parker grow up kid. Some people are simply born this way. You don't tell people with autism to simply become normal do you? Same way you can't make him physically be attracted to the opposite gender.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}L Parker No one's celebrating autism dumbass. However, we shouldn't judge autistic people because they simply were born that way. It's not something they can help with. So society tries their best to make their lives little bit less harder. Same thing with transgender people.  Not sure why you are so against that.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}Gods come and go, cultures come and go, people come and go, but what's natural is here to stay. Homosexuality is natural, and so is gender fluidity. These things have been around a whole lot longer than even the man made idea of such a thing as god. So ramble on all you want, oppress people all you want, this is here to stay. It always has, even in the animal kingdom. You can either make peace with it or ruin your whole life fighting a losing battle. Autism and any form of LGBT identification are not the same. One debilitates you from functioning as a healthy human being, the other is no way or form is debilitating except for the fact that extremists like you make society hostile for us, which has to stop, and this fact is being recognised everywhere. Slowly but certainly. I don't blame you for your narrow mindset, you grew up in that world, but the world is changing, as it always does, and you'd be a fool to want to stop that. You are welcome to try.  & \cellcolor{green!5}LGBT & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/183 & \cellcolor{green!5}0.546 \\  \hline
  \cellcolor{green!27}If you are gay at least you are not insane with regards to hating yourself so much that you play dress up, take drugs, and have surgeries to try and live a lie. A gay guy, for example, remains a male. He just likes other guys. He does NOT have his penis removed believing somehow he is a female.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}L. Parker U are right man....And after all who cares about someone sexual preferences....Let the ppl do in their bedrooms whatever they want...But promoting sexual degenracy and anomalies and promoting it as something normal is just idiotic..... But Usa is so gay and so corrupted it is sad....Thanks God i dont live there....  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/53 & \cellcolor{green!5}1.887 \\  \hline
  \cellcolor{green!27}isaac ong Why they need too accept?? I hope those kids stay away from toxic LGBT sect and community...Everbody have right on their opinion...Like they have right to do what they do, i have right to not like it ,what they do to themselves and what they are talking....but is their right and my right is to stay far away from them as possible     Have a nice day all  & \cellcolor{green!27}LGBT & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5}Faggot.  & \cellcolor{green!5}Faggot & \cellcolor{green!5}Male homosexuality & \cellcolor{green!5}1/1 & \cellcolor{green!5}100.0 \\  \hline
  \cellcolor{green!27}L Parker bruhhhhh im fuckin sure that u ve had a crush on someone at least on time in yo fuckin life nd u couldn t do anything bout it, right?? U just had to live with it till it was over Its the exact same for ppl who r gay they cant do anything bout it they just fall in love with someone they find attractive, just like u  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}don't listen to these idiots. I know that you are attracted to him because of the masculine qualities not the feminine ones. I am in the same boat as you, gay and this guy is decently good looking.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}Poker Face this society is just wow. Now being gay and trans is  normal  and  natural  open your eyes and realise you're abnormal and unatural.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}Wow this conservative nature is very scary. I cannot believe that people nowadays are still not embracing it. Love is love! I am very sorry that you are this ignorant to this matter. Being gay/transgender is not a choice or preference, it is just somebody being themselves. I really do not think this is a healthy mindset and the amount of people in the LGBT community falling into depression and suicide due to mindsets like this is scary. I do not want to have an argument or make anybody feel bad, just find it scary that we live in a world of the future and are still being dragged back by things like this. Poker Face was simply leaving a kind comment trying to be kind to somebody and instead they are granted by and onslaught of harassment. Please, do some research - and respect people for who they are! Mindsets like these are dangerous. Once again I don't want to offend anybody!  & \cellcolor{green!5}LGBT & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/163 & \cellcolor{green!5}0.613 \\  \hline
  \cellcolor{green!27}Ok so both have valid points in this argument. This situation of being gay or transgender was not a problem years ago, yet for some reason it is gaining a lot of popularity. Fine, be who you want to be, gay or bi or whatever, but some people still won't support you. Just remember that  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}Poker Face of course your gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Poker Face More and more people are becoming  gay ,  bi  or trans and whatever the fuck also exists I'm actually sick of it. Soon our kids won't know what the fuck they are. The weird thing about me is that I respect the LGBTQ community, but at the same time I just can't stand it anymore. It's like we are starting to promote being gay??? What the actual fuck? I'm sorry but that's just not normal. I won't say anything rude to you whether it were in person or here but this is getting out of hand nowadays.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}That means your Bisexual, not gay, good sir.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27} Dank Matters fish Never had a crush on somebody that I couldn't do something about. Gay is a mental illness. If every animal turned gay there would be none left. What is scientifically good is what perpetuates the species and what is bad is what destroys the species. Scientifically gay is bad. Religiously gay is bad. Common sense and oh looky still bad.   The cure to mental illness is not acceptance, it is getting rid of it.   Had I been so cursed to be attracted to men I would have just married a masculine female and moved on with life in a way that makes sense instead of self-destructing like you lot always manage to do. Part of me is glad then, that the blight is removed from humanity and part of me is sad because I really do want people to all find, posses, and maintain true happiness that lasts. But I realize there are way too many that refuse to be happy and that's just sad.  But keep trying to sail your anchor all you like...  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/178 & \cellcolor{green!27}0.562 \\  \hline
  \cellcolor{green!5}You will always be a woman.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}You seem more concerned about his gender than he is himself.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}To be fair, my friend, this video isn t to please or help you in life, so you really shouldn t be concerned about HIS gender. You should keep your opinion to yourself because I guarantee no one cares but you and the very few that agree with it because most of the comments are to support  HIM . Not you. :/  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}Nope,  his  he  himself.  The heuristic almost everyone uses when determining with which pronouns somebody should be addressed is based on the appearance of the person, because you can't do a genetic test on the street. And it is more than obvious that he looks like a dude now and that you would use  he  if you didn't know him and would have met him as a stranger. So I don't understand this  but muh biological gender  bullshit. It doesn't even make sense to call him  she  and you wouldn't do it in person, so why not help him find comfort in his life and call him  he , when you would do it anyways? It has nothing to do with  political correctness  or forcing some made-up pronouns upon you, it is literally common sense, and something you do probably every day when meeting a stranger.  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/145 & \cellcolor{green!27}0.69 \\  \hline
  \cellcolor{green!5}but it is a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}But it is a woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}facts are facts she can act like a man, piss like a man, take chemicals to  change  into a man, but she was and still is naturally and biologically a woman...  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}if i dress like a muslim does that mean that i am muslim? nope, she can look like a man to us ofc she does, but that doesent change the fact that she is and always was a woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}Well HE was woman now HES a MALE  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}I don't get it, testosterone changed his jaw? So does that mean if I, as an 18 year old dude, increased my testosterone (naturally through like lifting weights and gaining muscle) will my jaw start changing? I don't get it  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}You were a female? What that s absolutely crazy  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}Ironically Childish shut you dumb fuck liberal and the left are the dumbest fucking people they preach tolerance but cant stand it when someone has a different opinion  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}Ironically Childish go suck some bbc, soyboy beta cuck  & \cellcolor{green!5}Cuck & \cellcolor{green!5} Ideological and Political Identity & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Ironically Childish it's a mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}It does not matter, she is a woman, she cannot rid herself of the xx chromosomes that compose her entire body. She can try, but she is a woman, no matter how much testosterone she puts up her ass. I've no problem with women injecting testosterone in their bodies, but I have a problem when people try to force me to identify those people as men, when they are clearly not, they are an infertile abomination worthy of being studied in a lab.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}Man O' War So if you randomly encountered him on the street, without knowing, who he is, then you would call him  she ? You are full of shit. Nobody here is forcing you to identify anyone as anything, and you know damn well that you couldn't tell from the looks that he was a female before, if you hadn't watched this video, so you would instinctively call him  he . People like you are the reason why these fucking third wave ultra-leftist feminists even exist, because they are called into existence as a reaction to your hate. Why does it matter to you if he's a woman or a man, as long as I am not forced to call someone by a made-up pronoun nobody uses, why bother? He looks and sounds like a dude, and that's the only information I need to determine how I call someone.  If you would just start to let people, that haven't forced you to do shit, live their own fucking lives, without calling them  infertile abominations worthy of being studied in a lab , then there would be one radical feminist, and one person that can be rightly called  transphobe  and used as fuel for feminist agenda, less.  & \cellcolor{green!27}Nobody & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/203 & \cellcolor{green!27}0.493 \\  \hline
  \cellcolor{green!5}Curious what types of anabolics the doctor had you on? As someone who has had taken test and other anabolics to first improve performance and now to simply feel better and fight off the effects of aging I have never heard of increased bone size. Are you taking GH or IG-F? I am hoping with the increase of hormone therapy for the transgender community we will see a increase in the ability to get them without having to deal with the black market.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}Wait, this person was a woman?  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Stfu and be who u were born u gay boy  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}im not a tranny, but im considering on taking roids  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}wtf i dont want to change my gender but i want to have deep voice like you omg L:  (  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}you blink like a woman and your hands look female you are stupid hahahaha  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}Asking what gender a person is in the dating industry is going to a serious question. This stuff is a prime example of critical theory and societal degeneracy  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}Imagine dating someone you thought was one gender, getting married and then saying,  hey let's have a baby!   & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}hun demojumper yeah, honestly it s disgusting  & \cellcolor{green!5}Hun & \cellcolor{green!5}German & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Advenco your muslim countries suffer from a mental disease of radical violence, mental insanity that leads to suicide bombings, and various other terrorist attacks .  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}Advenco it really isn t fake buddy. Have you been oblivious to the terrorist attacks that happen almost everyday because of your dumbass religion?  & \cellcolor{green!5}Terrorist & \cellcolor{green!5}Muslim & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}Gender is technically mental. But even when referring to sex, it should be illegal to hide your transition.  I won't date a girl who doesn't want kids, but I think it shouldn't be legal to hide infertility from someone. (Transition-ers can't have kids obviously)  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}gender is only mental for autists  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}you're always going to be a woman just be yourself and get a psychologist to help you  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}Gender dysphoria is a disease.    hardy har har  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}So I guess transphobic is the new homophobic?  & \cellcolor{green!27}homophobic & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}now you just look like a gay male  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}Fucking tranny  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}Transgenders are born with opposite sex brain. Like mtf would be biological male in appearance but female in the brain. This creates them to have the behavioural and characteristics of the opposite sex and having gender dysphoria. This can show that they are actually female or male mentally.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}That doesn't happen. You are either born normally or born with gender dysphoria and have the brain of the opposite sex: evidence is here: https://youtu.be/W 655Vt6LKA  Either way people who say they become a man or women for a day or non-binary is a loud of crap because there is no scientific evidence for that and your brain can't change itself over and over to think you're male or female.  There is no diagnosis for them. People like that literally diagnose themselves or just want attention. And no it's not schizophrenic. That's seeing things in your mind  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/96 & \cellcolor{green!27}1.042 \\  \hline
  \cellcolor{green!5}GUYS WHAT'S UP WITH YOU?! WHY WOULD YOU JUDGE HIM BY HIS BIOLOGICAL GENDER? HE IS OBVIOUSLY NOT A GIRL AND A LOT HAPPIER. FUCK OFF WITH ALL OF YOUR SIN BULLSHIT AND YOUR CRAP ABOUT CHROMOSOMES. DO YOU WANT A HAPPY PERSON? YES. THAT'S ALL THAT FUCKING MATTERS. GOD WOULD NEVER WANT ONE TO KILL THEMSELVES AND IF HE EXISTED THEN HE'D KICK YOUR IGNORANT ASSES FOR BEING SUCH JERKS. GET A LIFE PEOPLE. HE IS HAPPY NOW THAT IS ALL THAT MATTERS.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}why the fu k did your censor your nipple... common dwg... your a man  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}Ur granny tranny  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}still a woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}this is crazy. good job i guess haha. its so crazy u were once a chick!?!?  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}I can't believe there's parents out there pushing for transgenderism? children don't understand that when they mutilate their sexual organs there's no coming back from that not just a choice you can make to flip flop back and forth as you desire once you mutilate yourself that's it. Not to mention the lifelong pain associated with anyone who's ever had surgery will tell you. I mean this is truly a mental illness what kind of person wakes up and decides, say I think I'll mutilate my sexual organs? WTF these parents should be in jail for child abuse.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}big gay xd  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}To whoever  wonders this: yes (s)he does have a pussy  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}transgender is a mental disorder  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}Gender Dysphoria is the mental disorder that comes with being transgender, nothing wrong with that though.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}fukin gay bro  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}You look like a guy homie. If you got fucked by a guy it s not gay??  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}Homie did you just ask if its gay if a guy fucks a guy?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Biological Woman always a woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}Joshua Flack wow you're dumb you do realize that cells regenerate, right? Every 7 years all of your cells are new. And cells don't have a gender. Next you'll say that atoms do, idiot.  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}Joshua Flack Yes, but cells don't have gender. You have the same cells as a female. They might be in different places, but blood cells all function and look the same, skin cells, hair cells, etc.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5} Water Symbol cells dont have a gender but cells are differebt in male then they are female  do your research and stop with the shitty arguments  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27} Water Symbol lol, cells ARE gender itself... each cell contains chromosomes (coiled up DNA) X and Y sex chromosomes are the blueprint of the cell. If you have XX chromosomes, the cell will become female and produce female hormones. If you have XY chromosomes, the cell will become male and produce male hormones.   Do your fucking research before you say stupid shit. thank you.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}The fuck are you even talking about? Cells make up organs, they don't do special things like change your gender. Last time I checked, men and women both have livers, skin, and hearts.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27} Water Symbol Cells. Do. Have. Gender. XX chromosomes   Female cells, XY chromosomes   Male cells. Those chromosomes are in every single cell in your body. Also men and women have different reproductive organs ie. testicles or ovaries. You obviously didn't check well.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5} Water Symbol haahhahah how old are you? 10? if you have finished education, or payed attention to school... OR EVEN GOOGLED IT XD. you would have known, that cells define your gender. yes they make up the same organs, but they also make up different organs. ovaries? don't be silly, females don't have a penis.  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27} hun demojumper yes thank you for that. like you said, not a man, but he/she is not a woman either. he/she is transgender(in between). even if 50 years pass, even if everyone thinks he/she a man, that person is still transgender. Neither man nor woman.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5} yes thank you for that. like you said, not a man, but he/she is not a woman either    ----- not a women either???? every sane person knows there are 2 genders... no in between bullshit, you are probably a buzzfeed fan who belives there are 400  genders or something, don't want to hurt your feelings and i don't call you an idiot, but if you say she is in between, you speak against nature. 2 gender is a FACT and you can't do much about that  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/86 & \cellcolor{green!5}1.163 \\  \hline
  \cellcolor{green!27} hun demojumper no lol, i am not a believer of 400  genders. I know for a fact that there are 2. but this person decided to go against nature. naturally there are 2. but since this against natural, he/she is in between.  & \cellcolor{green!27}Hun & \cellcolor{green!27}German & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}stupid fuck she is a biologically a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}how about we just not give a shit what others choose to do with their bodies and be on your merry way. I am christian, conservative, agender, and bisexual. I am completely against pride but thats just a personal preference cuz i know 90  of ppl with common sense realize that what others do with their lives should have no effect on them. Is respect for other humans that damn hard to find??????  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}Nobody you dumb fuck  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Hearts are Muscle's dumb shit  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}look   that dude and call him a woman. just look  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}still, a female but identifies as a boy, not a male mind you, a boy, gender is different than sex.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}Caio chill the fuck out moron, he is right. ''He'' will always be a female.. she won't replace her female cells with male cells... And as long as she has a pussy she will be a female no matter what. :)  & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}hes a still a woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}Ur kinda stupid, cells have chromosomes in them, 2 of them are Sex chromosomes, if you are born with XX, it'll stay XX for the rest of your life.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}Shut the fuck up honestly. If he was to identify as a man then that is him. Its people like you who say this type of shit that make transgender people a target and there are laws in the world that bann trangender people. You honestly DONT DESERVE INTERNET CONNECTION.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}WhiteEurope, being transgender is a mental disorder, it s when u feel that u are trapped in the wrong body and to change that feeling and be satisfied you would transition. Yes he will biogically always be a woman but that doesn t affect anyone else s life except his... he should feel happy in his own skin  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}Water Symbol cells replicate, they don't have sexual contact but they perfectly replicate  & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}but she was a nice woman, with beautiful hear and skin, and now he is a hairy dude... just WHY??  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}Water Symbol  Sex cannot be changed by surgical operations. The term  sex change operation  is misleading.  Cosmetic surgery can alter the appearance of the genitalia, hormones can enlarge the male breasts and change hair distribution. Make-up artists can alter a male face into a pouting female one. These have changed your sex, haven't they? Actually, no they haven't. The only things that have changed are your name, title, appearance and dress. Even without surgery it may be difficult at times to differentiate male from female, with both sexes wearing their hair long and dressed in similar attire. Looking up their genes is one way of distinguishing their sex.  In the first place it is genes which determine our sex. We humans have 23 pairs of chromosomes   one from the mother's ovum and one from the father's sperm in all our body cells. Genes (made of DNA) lie strung along our 23 pairs of chromosomes.  Chromosome-pairs numbers 1 to 22 are microscopically identical, but chromosome pair number 23 the so called sex chromosomes are different. In the female number 23 has two paired large X chromosomes (so called because they resemble the letter X). In the male number 23 has one X chromosome paired with one small Y chromosome. It is this variation that determines sex differentiation. The ovum produces X chromosomes only, while the sperm produces both X and Y varieties.  Other factors are involved   for example the steroid hormones and other hormones and enzymes, which play an important role in the later maturation of sex.  Clearly, no amount of surgery can change the 100 million million body cells to alter the chromosome combinations that determine our sex. So a sex change is impossible.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/286 & \cellcolor{green!27}0.35 \\  \hline
  \cellcolor{green!5}Agreed, nothing will change the fact that she was born a girl.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}WhiteEurope  If what your born as is your gender forever then what about people who are intersex/etc  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}but it is a  woman. It has a Vagina, aka female organ therefore, a female.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}Caio Jorge he didn t ask for yours ether dumb fuck  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}Now she's just ugly woman.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}lol nobody asked for your's or mine.  & \cellcolor{green!27}Nobody & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}shut up nigga he still a bitch  & \cellcolor{green!5}Nigga & \cellcolor{green!5}Black & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Biological Female  always female. But he is not a woman. He is a man but not male  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}I'm totally on your side but you must understand that nowadays children and early adults are being taut gender and sex are two different thing, being that sex is Female and Male and gender is whatever you identify as. Although that is literally retarded it's how the world sees it today  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27} Misty Wolf10 Just a quick question, I have heard of gay christians and such but do you understand it is a sin in the christian religion to be gay at all, also applying to 'bi' people because they are technically still gay they just also still like the other opposite gender.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/51 & \cellcolor{green!27}1.961 \\  \hline
  \cellcolor{green!5}Sex isn t gender, young one. Are you being productive?  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Joshua Flack Do you see his Adam s apple? That s proof enough. Girls don t have them.  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}DeadlyKitten Transgender is the process of changing your gender into the opposite one. For example, I was born a girl but I identify as a boy. Non binary is when people either identify with both (or more) woman and man or none at all  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}hun demojumper I believe that you are talking about  sex  not gender. They are totally different things. Gender is something you identify as. For example, I am a boy (Sex) vs. I am a cisgendered boy (gender). See the difference?  & \cellcolor{green!27}Hun & \cellcolor{green!27}German & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}Water Symbol Hey, how old are you because I would like to be friends and talk more, I agree with all of your beliefs. Also, whoever posted this comment is a dumbass, enough said.  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}It no longer looks like a woman, so I fail to see your point, Mr Seljak.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5} Thomas is Gay I'm just wondering did you copy and paste all that cause that would take along time to write  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}cereal it s a pussy so it s a female  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Sex and gender are different things. Gender originates from the BRAIN, meaning certain chemicals are there that make you a male or female. Sex is the chromosomes and genitals. His gender is MALE, and it s also frankly none of your business. Maybe you should be more educated about this topic before you decide to harass him.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}DeadlyKitten - Your brain defines your gender, idiot. Lmao.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}DeadlyKitten - He TRANSITIONED from female to male, meaning he is a man. Genitals don t define your gender.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}hun demojumper man   & \cellcolor{green!27}Hun & \cellcolor{green!27}German & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}Teekee bo burnham as a joke said kill yourself to his viewer and maybe kids that are my age are doing it cause of school and personal life. Cuberbulling is decreasing  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}Teekee dudee that kind of people should not ever be here on youtube! why anyone in the world have to know about their mental issues? come on  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}Law of the jungle man...weak can't survive. It's not my fault that you or anyone else have weak mind. Only your mind will make you kill yourself. The choice is yours/theirs. He posted video, i express my opinion. For me its disgusting. We are talking here about gender change god damn..This is not the place for ppl like him.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/59 & \cellcolor{green!5}1.695 \\  \hline
  \cellcolor{green!27}Remember how in the 20th century and before that when being homosexual etc was bad? It s kinda like this now. I personally support you my dude :)  & \cellcolor{green!27}homosexual & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}you have a mental illness that you should get checked out.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}Degeneracy and mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}why didn't you take pheromones injections to cure yourself from the instable mental state you were in? Most of transgenders have hormones issues and I still can't beleive doctors go on with that nonsense  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}You have a sickness a mental one,  you need to be cured sweetie  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}And you will never impregnate a woman, you will never know how it is to truly be a man sorry sweetheart  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Mael Boy why would trans ppl make a fake vag and a fake dick? Never will be the real thing. They can do whatever they want but it's a mental illness and forcing ppl to believe their delusions is fucked.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}Why change your gender??  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Fuck you, you freak of science  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Spoiler, youre still a female, fucking mental illness too think otherwise.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}still a woman , now your just a women taking testosterone and not shaving doesn't make you a dude , you will never be a dude you will always be a woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}You know you succeeded in transitioning when I as a gay guy wanna have sex with you.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}Could of just been given councilling to help you feel comfortable in the body you were born in like every other similar mental illness is treated.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}I would like to change my age, what do I have to do?  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}I wouldn't think you were a woman, you are quite and handsome guy.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}Can't change your dna you'll always be xx never xy. Mental illness at its finest this is the PC world we live in today smh  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}If someone doing what they want without hurting anyone annoys you then you have the mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}SamIsOG it gender dysphoria is actually a mental illness i think, but you don't have to talk down on these people. If this is what makes them happy who or you to tell them they should live differently.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}how hard is it to act your fucking gender lmao  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}Fuck this gay nibba  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Wow this is gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}Gay men have nothing to do with transgender people.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Duff Clem wow let me guess, you are from the trangender liberal west. Little boy, you cannot go against simple biology. Being gay and trans is wrong and thats it.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}Duff Clem ohh and I am an open minded person, so pls, if you and willing, dont hasitate to say a few valid arguments on how being transgender is  normal . Change my mind. I wont fight with you.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}I'm neither gay nor trans. I'm just informed about those topics. You aren't. I'm a master student in biomedical research. You certainly don't have any knowledge about biology at all. Get over the fact that you're nothing but shit, fuck boy.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}Duff Clem okay since you are a master biology student please do say how being transgender is normal looking through a scientific point of view. Change my mind  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}Duff Clem you see, I agree with most of this, but strongly dissagree with gender being a social construct, I suspect you are american? Correct me if im wrong  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}'Normal' isn't a word that applies to nature. Nothing is 'normal' in nature. 'Normal' refers to things conforming to certain norms, and norms are human-made rules. It comes from the Latin 'norma' which was an instrument of measurement. Things in nature are typical or atypical. Homosexuality and transgenderism are atypical, but so are left-handedness or situs inversus. You can read  On the Normal and the Pathological  , a book written by French physician Georges Canguilhem. It's a very important book for philosophers and medicine practitioners. I'm not a biology student, I'm a student in biomedical research. It's a bit like medicine if you prefer, but it's aimed at doing research in a laboratory to make medicine go forward instead of directly providing care to people. I'm not American. I'm Belgian. Please read the links I posted if you want to understand transgenderism better.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/143 & \cellcolor{green!5}0.699 \\  \hline
  \cellcolor{green!27}On gender being a social construct, I will admit that I have too little knowledge about the subject to be able to form a well-substantiated opinion. I still have to brush up on social sciences. What I can say is that  male  and  female  are biological realities, independent of human social representations, while  man  and  woman  are categories to which humans culturally attach certain qualities. But those qualities aren't always based on biological realities. Therefore, you can observe certain people indentifying more with certain aspects of the category they weren't assigned to at birth in virtue of their genitalia. The link I sent you talks about the causes of that fluidity and tends to explain it through an incomplete masculinization or feminization of the brain.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/125 & \cellcolor{green!27}0.8 \\  \hline
  \cellcolor{green!5}hun demojumper I am trans now  & \cellcolor{green!5}Hun & \cellcolor{green!5}German & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}I know it's late but gay people have nothing to do with transgender people at all. It should just be LGB not LGBT  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}i heard a man call his dog a ''good boy'' the other day, i nearly needed to go to my safespace after hearing that ignorant assumption of gender.  it'll definitely  be something i bring up with my psychotherapist tomorrow. i hope i can sleep tonight.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}Glad you choosed to be male ..Other way its freak ...You are a men now    & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}You can't Change gender. So why try?  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}this is crazy you are not normal , you need help . this world is not okay I feel bad for you girl  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}How is it possible that your body shape changed? Do your bones suffer a modification? If so, how old you need to be before testosterone is not effective any more?  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Bones don't change, it's just the fat moving around. It's called fat redistribution. Because he's on testosterone it no longer stays in the places typical for females (hips, etc.)  & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Features & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}i would have never ever guessed that you were transgender. happy for u bruh  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Today at 2:00am , I had a breakdown,, I almost went crazy , I ve been trying to figure out how to make people accept me being FTM since I was 17 ,,  Before couple of days I became 21 ,, and I still didn t achieve anything ,, i swear I can t even describe my feelings , I spent the whole night crying hysterically watching pictures of 21 years old boys and realizing that I m dead inside..  I m still now , and I ll take my own life soon.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}fucking transgender  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Please visit a Psychologist,you clearly have a mental illnes  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}Fucking weird man.  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}why do trans ppl whine about hate they are getting? I have been to several trans videos and I can barely see anything, like meanwhile in the gay community ... tf is up with humanity  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}gay nigga  & \cellcolor{green!5}Nigga & \cellcolor{green!5}Black & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}OMG I'm a gay boy and I'm having a crush on a trans man. Be minee! XD  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}you should be fucked before,  during and after transition  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Does testosterone make you grow taller?...bc I want to be taller than 5'7 if I'm gonna transition  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}Nope still just a female.... but now a female with a far worse mental disorder... by the way girl, you have to cycle on and off testosterone and shouldn't take more than one cycle in five years. Enjoy the heart attacks that are coming.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}Transgender female to male Transgender female   Havee  fake p   right?do they have sperm? Or not? If she have sex with girls do girls will be pregnant?  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}Is this a mental disorder?  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}Why has no one pointed out that this person has a Adams apple , it's obviously a hoax  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}Why tf would having  female  genitalia make someone a girl at birth ? I mean, you're not defined by your body, you're defined by you, your spirit. Once and for all, people, VAGINA DOESN'T MEAN PINK AND PRETTY, PENIS DOESN'T MEAN BLUE AND STRONG. You are who you are, a boy or a girl, straight or gay, no matter what's in your pants. You do you, boo.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}I'm in South Africa and my girlfriend wants to do transgender thing but don't have money and does not even know how much it will cause. Any advice  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}Is  transgender process expensive?  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}A lot of people will think wrong of me on this. But I will say it anyway, we have no authority to change our   body gender by any means possible. We were all designed by God (Yahweh). Therefore changing our gender etc is a form of rebellion. We should take the matter to him in prayer. There were cases where people changed their gender identity and lived to regret it. If you feel that you are in the wrong body (feelings that do exist due to chemical imbalance etc) take it to the LORD in prayer, he can do wonders.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5}Still a female. Lckily you can't reproduce and your mental health issue will not carry on to any children. I hope this mental health issue is removed from society via natural selection.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}Taking T gives you sort of an Adam s apple yeah?  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}stay  a woman  I'm a man and I  hate it  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}ThePbrook1967 fucking gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}Get me to 1400 subscribers  But he s originally a woman so it s not gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}If the person change 2 boy.....is tht they can have sex like normally n get baby  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}Is tht a transgender can have sex....female 2 male???  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}im actually transgender female, turning male. I am 14 years old right now, and want some advice?  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}PinkHairedGamer I GOTCHU! I'm FTM as well. What you should do before you come to a full decision is search up as much information as you can. Try things with the sex you desire later on. Be selfish about this. And if your family doesn't know yet, see if you're comfortable with them knowing this before you come out to them. This is the best I can give you  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}Here's some advice. don't do it until you're a fully formed adult and after careful consultation with a mental health practitioner.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}way do  woman  want to be a man  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27} IdolMike that is a very dangerous sentence. A person's brain isn't even close to full development at age 14, let alone 18. Synnerization wasn't hating, he was advising. The reason i mention age is because you can't fully understand the consequences of an action at such an age. i don't know how old you are but if you are an adult think back to when you were a child/teen. think of all the impulse moves you made. whether it was buying something on a whim or maybe even a sexual act that you thought was a good idea but really wasn't, there's no denying that we have things like legal drinking/smoking age and age of consent.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/116 & \cellcolor{green!27}0.862 \\  \hline
  \cellcolor{green!5}Go to mental hospital  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}PinkHairedGamer  1. wait it out until you re an adult (many of us have waited). It sucks, but try your best to cope with your body while you change and grow.  2. Medically transitioning is a very serious step. Also understand that medically transitioning is not necessary to be trans. 3. Don t let the hate get to you. These comments prove it s all over the place. Namely, hate in this area is coming from ignorance.  Gender is absolutely not a social construct. Gender and sex are both biological.  Gender can be seen in the body through the brain (MRI, white/grey matter and region differences).  And last but not least: Worry about transitioning when you have full control over your environment. For now, keep up with studying. Hang out with your friends and make good memories. Express yourself how you seem fit (even if that means coming out).    Peace, brother.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/148 & \cellcolor{green!27}0.676 \\  \hline
  \cellcolor{green!5}Fake Namelol if gender is a social construct why do transgenders need to change themselves physically I'm confused  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}Sarcastic Squash that s leftist propaganda. Gender is not a social construct. I actually hate that belief because it does so much harm for the trans community. We ve been fighting for appropriate medical treatment, and to have so many people spouting  oh it s a social construct!  has taken us a million steps back. Gender resides in the brain and can be examined. Sex resides between the legs and can be examined. They go hand in hand, and if something doesn t align, dysphoria is the result.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}hun demojumper excuse me but the age 14 isn't a 'kid' anymore. Teenagers have their own rights to do what they want.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}PinkHairedGamer Female?Transgender Female?Listen up Girl you are a kid.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}transgender is just another cry for attention. next please  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}She s still a girl she s  biologically a girl, she will never be a boy, just because you ware saggy pants doesn t make you black, same thing with this  & \cellcolor{green!27}Black & \cellcolor{green!27}Black & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}Im not surprised... she was a fat sjw lesbian that wanted to  become  male  & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Female homosexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Transgender is a mental illness you re still a women kys you dumb bitch  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}Palacsinta Csatornaja born a baby with no knowledge of anything now a libtard brainwashed by society  & \cellcolor{green!5}Libtard & \cellcolor{green!5} Ideological and Political Identity & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Palacsinta Csatorn ja dumb liberal  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}So he has an adam apple Has a penis Doesn't have breasts But he is still she fuck this logic  & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27} BTS                  . its not logic. its science lmao. it has been proved you are what gender you were born with.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}They are facts, a biologically born woman is always gonna be a woman. no matter how much testosterone you inject, your DNA is not gonna change, only your look.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}Hey hey does anyone here realize that the point of taking t is not to change your DNA, it's to change the way the body looks and feels so that those who feel more masculine mentally and feel trapped in their body can finally feel more comfortable in it? It's not about changing their biological sex, it's about being in a body that feels right to them, and it's making them happy, if they do it right it doesn't harm them, and it's not hurting you either.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}Yeah he's not a male, he is a transgender male. This are facts, but there is also a little thing called respect.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Neck Assboi you don't know what chromosomes he has because there are more chromosomes than XX and XY. there are also people with XY chromosomes who are born with a vagina, and people with XX chromosomes born with a penis. you know zero about biology. Stop trying to seem smart.  & \cellcolor{green!27}Zero & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/50 & \cellcolor{green!27}2.0 \\  \hline
  \cellcolor{green!5}What the fuck is with this time in age. Faggots like you think you can just change because you want to. I can't believe how fucking retarded these gays are. It just blows my mind that your parents are fine with this. Just fucking die.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}You look so much like a dude that if I were to kiss you I would call myself gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}This creature is a freak. It has a mental illness that needs to be fixed not encouraged. And it s genetics still classify it as female.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}So she s a guy that s weird  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Male , female that's it , manipulating your body to  change gender  is a sin   Genetals   Gender  Your a woman with short hair and body hair because of testosterone  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}I believe that what you're trying to imply is sex. Gender is the preference and personality of person.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}OnionBro  YT Why must you be close minded rather than have a proper discussion of sex and gender?  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}OnionBro  YT but there IS a difference between sex and gender. I just wanna discuss that gender is different from sex. Sex is the physiological body of a person, however, gender is the emotional aspect. Sex body Gender emotional or mental  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5} gerard bernos No...gender is not disconnected from sex. You cannot magically change your gender just because you believe you are what you aren't. Dumbass, you clearly don't understand basic biology  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Klovod i do understand biology. That there is a female and a male body. If they are the same why there be two words? And yes, you can be any gender you want because it is emotional and mental. How can you say that it is not disconnected? Firstly define what gender is so that we can understand. A dictionary definition  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5} gerard burnos Gender is determined by your XY chromosomes, you cannot change it based on your own convenience. You can't change your DNA, you can't become a male when you are genetically a female. If I say and  believe  that I am a cat when I am genetically a human, does that mean I'm a cat? DNA cannot be changed. Claiming that you are the gender to which you are not, is a mental illness known as gender dysphoria. Which is also why the suicide rates are so high, because it's a mental illness that needs to be treated accordingly, not encouraged.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/102 & \cellcolor{green!5}0.98 \\  \hline
  \cellcolor{green!27}You are not a man if you're a female, just because you believe so in the mind. The notion that gender is malleable and can be changed based on your own convenience, is not philosophically consistent. Because you (the moron) believe that gender which is determined by DNA, can be changed based on your own opinions of the English language, then can I change my race as well and become a Filipino woman despite me being an Ethiopian Male? If not, then why can't I identify as such?   The transgender (mental illness) ideology is only constructed to appeal to emotion rather than logic and science. Which is why in every professional debate, the left always loses on this topic (and many more), because they have no facts to reinforce their argument. This whole argument that gender can be changed based on your own opinions, is not sustained at all by solid facts, just emotion. Which is why members of the LGBT (degeneracy) group suggest that transgender pronouns should be respected despite the fact that transgenderism lacks philosophical consistency regarding the disregard for DNA over feelings.  & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/185 & \cellcolor{green!27}0.541 \\  \hline
  \cellcolor{green!5}And just to respond to your argument which was based on your believe that gender to you, is a social construct. Almost every single word is a social construct, what is your point? The reason why there are two genders, is because throughout history, boy meant boy and girl meant girl, it was never the other way around. Of course some primitive cultures believed in third or fourth, etc genders, but that doesn't make it correct. These cultured believed in many spiritual things which contradict science and biology. My point is, the reason why there are two genders is because 99.99  of the human race either has an XX or XY chromosome, with acceptance for those with very rare genetic disorders which greatly affect their body and health (height, weight, body hair, bone structure, etc), these are genetic disorders because they are not normal and come with a multitude of cons, nature does not intend for there to be a third gender for the human race, whenever this phenomenon happens (XXY, YY), it results in non-normal distribution of testosterone and estrogen along with many other disastrous variations.   The healthy human, has an XX or XY chromosome is my other point, which is why most healthy human beings have one of the two, I made this argument just to disassemble your upcoming argument on the fact that third genders genetically exist. Of course they do, but they are genetic mutations which are very rare and affect the person's body greatly.   Another thing, males and females are intended by nature to look and behave differently. Which is why binary gender exists for the two genitalia. Just to disassemble your  genderfluid  bullshit.  & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}1/279 & \cellcolor{green!5}0.358 \\  \hline
  \cellcolor{green!27}Klovod why is it philosophically iconsistent? Reference? Race is out of the picture. As it is defined as the biological body. You are the only one that is incosistent. I already told you that it is sex. Well, yeah a woman can feel like a man but it will not change their sex, i conceed to that. But it is still gender.  & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5} gerard burnos First of all, you clearly didn't bother READING all three of my comments which thoroughly explained the philosophical inconsistencies in the leftist transgender ideology where a man can become a woman whenever he wants, vice versa. This ideology is philosophically consistent because it is based upon being able to modify and disregard DNA based on how you feel in the mind. You would know what I meant if you read my comments you fucking dumb degenerate. Just like race, sex is genetic. If you have XY chromosomes you are a male, if you have XX chromosomes, you are a female. No amount of surgery or hormones can change this, dumbass. Now dumbass, you still haven't answered my question. If gender/sex, which is GENETIC/PERMANENT, can be changed based on the individual's convenience, then why cannot race which is GENETIC/PERMANENT as well be changed? Gender is genetic, if you even bother to argue against this, you're full of shit.  & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}1/159 & \cellcolor{green!5}0.629 \\  \hline
  \cellcolor{green!27}what the dude is talking about when you have the genitals, chromosomes, all of that nature, that s sex. what you want to be known as is gender  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}Firstly, as gerard said gender is in your mind, whilst sex is your body. Secondly I doubt he is going to hell. Probably just going to get buried and rot, like everyone else.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}OnionBro  YT he has gender disphoria so he can t help it  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}Jesus. You christians need to chill the fuck out. I think it's weird and wrong, and I too believe that  he  is still a she. It can't be changed. But calm the fuck down with all this sin and damnation talk. You christians sounds like fanatic lunatics when you do that. You are equally as stupid if you believe in god. But if you find you consolation in a big sky daddy, good on you. But that immediately removes all of your rights to judge other people.  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/87 & \cellcolor{green!5}1.149 \\  \hline
  \cellcolor{green!27}Fuck you, you're a piece of fucking shit. I'm transgender and proud. If you disagree and say it's a sin, fuck off and let people live their lives.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}Sex is biological, gender is mental. Doesn't change the fact that trans people usually have mental issues leading to the decision to change their sex.   And yes, you can be any gender you want because it is emotional and mental   That's why the whole gender thing is complete bullshit, you can say that you're a woman but it just isn't right. You can't just decide that you want to be a women out of nowhere, that's not how it works and operation won't make you a woman either.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/88 & \cellcolor{green!5}1.136 \\  \hline
  \cellcolor{green!27}OnionBro  YT imagine this,  you are in a horrible car accident and the doctors saved you, but they had to amputate your penis. So what do you do now,  you no longer have a penis, so what are you? Do you begin life as a female because you no longer have male genitalia?  See? Your genetails do not determine your gender.  & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}How do you know this isn't just a gay guy?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}Adolf Hitler Retarded. Have you ever seen females on Testosterone? Lmao... you're such a retard.  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}Tyler then why don't female bodybuilders win in heavy lifting vs males lifting  Even if they use steroids they cannot beat what nature intended Males are stronger gender and will have more muscles mass no matter what  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}Tyler it's also common sense something you lack  & \cellcolor{green!5}Common & \cellcolor{green!5}Working class & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}First of all, males react very differently to steroids, which everyone in professional heavy lifting uses. And females that use test get huge if they train and eat enough, you're right a male can get bigger even without using test or steroids, I was saying if she was lifting she would start looking like a male that lifts. So shut the fuck up talking about shit you know nothing about, considering you're arguing a point I never even contradicted. Fucking idiot  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}Tyler you think she will look huge? She has x-small shirt size  She will look like a fucking wimp standing next to a average guy  She would even look smaller then scrawny guy  & \cellcolor{green!5}Scrawny & \cellcolor{green!5}Physical Features & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}Tyler I know for a fact man have shoulders of 20 inches broad and woman have 15 inches Man have bigger bones structure And bigger muscles fiber  Thats why I know she  wont surpass a average guy  So shut the fuck up I know allot about this more then you  I'm personal trainer  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}You sound like a autistic 12 year old with your English, and no where did I say a woman can surpass a man, I said women can look like men if they take test. You're literally arguing with yourself.  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}Tyler It s fine. :)  It s just funny how you say he  sounds like a autistic 12 year old with your English ..  and in the same sentence you had bad grammar :p  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}Cis guy? retard  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}Lol.. god forbid someone has shoulders that are broader then 20ins or smaller than 15ins.  We can't categorize them as any gender :0  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}Holy shit, this is so fucking gay. please hang yourself  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}You're still a girl. This is what's messing up society. Transgender is not a thing. Born male, or born female. No crossing.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}this chick is confusing  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}I wonder if  he  has a gender neutral name  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}Ehhhhhh its a alien  & \cellcolor{green!5}Alien & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}You were meant to be a male! You honestly look so good! I'm not gay but going from female to this? Science has done so well!  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}West Coast Elements shut up woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Gender bender  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}This is bullshit. These people would start dating someone without telling them that they are transgender and their other wouldn't know in any way, i think it is fucking disgusting that people think that they can change simple fucking biology. You are taking the human anatomy and changing it how you see fit. I wouldn't consider this a humane act, i think it should be alienated. Just imagine if you found someone you loved so much and they made you so happy and you have never felt this way about someone and then it turns out they have the same genitalia as you and they are transgender. That would be so fucked up and you would basically be forced into a homosexual relationship without even knowing. That stays with you for life, you cannot change it.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/136 & \cellcolor{green!5}0.735 \\  \hline
  \cellcolor{green!27}So weird that this somen has a vagina  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}fkn retards who dont know vagena meme :D all those indian guys asking vagena pics :D  & \cellcolor{green!5}Indian & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}sex bob pls  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}late my Indian ass feels offended by 0.1      & \cellcolor{green!5}Indian & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}now since you have been a women and a man which gender is above  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}what a freak...  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}does he have a vagina or dick? i always wonder that when people change gender  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}How old is she?  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}sadly yes, since gonads constantly create the hormones of the gender you were born as  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}traps are gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}Kaden Crow yes  & \cellcolor{green!27}Crow & \cellcolor{green!27}Black & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}So he s transgender? If he is wow i cant tell u were ever female.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}You have to be kidding. Your 7 in mens at age 18? Wow. Im 13 and i wear 12's      & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}There is no such thing as more then one gender it s only male or female seriously what is wrong with the world you people obviously see it if you guys want a change it has to come from you and apparently you can see it because now there is  more then one gender  when it s visibly and clearly male and female  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}What the fuck is wrong with transgender people they seem so mental  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}oh hun, they're still female nipples.  & \cellcolor{green!5}Hun & \cellcolor{green!5}German & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}st va  They are still big and brown and soggy, and she is woman...  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}because they re still woman nipples  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}What does your nipple color have to do with anything? Weirdo.  & \cellcolor{green!27}Weirdo & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}it s crazy how much a mental illness can change someone  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}lol.... millennials... you cant or ever wont be able to change your gender.. You are what your born.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}not an opinion, its a fact. if your born a woman you will always be a woman. no matter how much testosterone you inject into yourself you will always be a woman. Testosterone only affects the outside of your body.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27}Traps are GAY  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}ur mom GAY lol xdxdxdxd  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}Traps are gay loser.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}If traps are gay, I'm glad I'm not straight  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}huh you thick brain forgot the testosterone dont grow you adams apple. stupid llad  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}Fucking transgender die in hell you piece of shit  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Wait you ware A woman A cant see back  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}a woman has that rib that was taken from Adam.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}I love my gender.      & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}EW nigga tf  & \cellcolor{green!5}Nigga & \cellcolor{green!5}Black & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}It absolutely pisses me off how when a guy who wants to build muscle and wants testosterone  The doctor will immediately blacklist him and no one will support him  But if a person with a mental illness who think they should have been born a male needs testosterone, without hesitation the doctor will give them testosterone and society will deem them a hero.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}Maybe this should make you realise that transgenderism is a real medical condition that is understood and explained by science, no ? Doctors have studied medicine for years, they know better than you.  & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}Homosexuality was designated as a mental illness for decades. The DSM is a highly politicized guide that is written by committee. It has as much to do with political perspectives as it does with science.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}Homosexuality has nothing to do with transgenderism. This just proves that you know nothing about those topics. Lactose intolerance was also listed as an allergy by the WHO while the majority of people are lactose intolerant... It was removed because scientists understand more and more what homosexuality is and where it comes from. You won't find any neuroscientist or psychologist saying it's a mental illness. It's just science. But you just refuse to acknowledge it. You just deny reality. That's pathetic.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}Actually transgenderism is still classified as a mental illness but you completely missed the point of what I was saying anyway.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}Yeah, kind of disappointing, it encourages lying, like a refugee claiming to be gay and persecuted, but they're not, or like how amphetamines are prescribed to children, but they're an illegal drug otherwise, but our world is filled with those cases where lying benefits those who do it without consequences, so better deal with it...  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}Duff Clem i identify my gender as a gym rat...can i have my test now?  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}African Kid no, he isn't.  & \cellcolor{green!5}African & \cellcolor{green!5}Black & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}Igloo Dreggin  I have nothing against homosexual people or LGBT community but when it comes down to facts then it's different thing.  It's not my life but i dislike when they'll complain all the time  Please, explain  Close mindedness   & \cellcolor{green!27}LGBT & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}Igloo, you are clueless ... This mentally ill female is parading her dysfunction on the internet hoping her dysfunction which leads to suicide 31  of the time makes her some sort of YouTube star. Taking drugs and having surgeries is not a game. This behavior should NOT be encouraged or celebrated. It is dangerous.  Conditioning children to believe the absurdity that they or anyone could be  born into the wrong body,  and that a lifetime of chemical and surgical impersonation of the opposite sex is normal and healthful is child abuse. Affirming gender dysphoria via public education and legal policies will confuse children and parents, leading more children to present to  gender clinics  where they will be given puberty-blocking drugs. This, in turn, virtually ensures that they will  choose  a lifetime of sterility, toxic cross-sex hormones, and likely consider unnecessary surgical mutilation of their healthy body parts as young adults. Puberty is not a disorder and therefore should not be arrested as though it is a disease.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/167 & \cellcolor{green!5}0.599 \\  \hline
  \cellcolor{green!27}African Kid she still got a coochie not a pepe  & \cellcolor{green!27}African & \cellcolor{green!27}Black & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}African Kid , and you re still a virgin, thats never gonna change.  & \cellcolor{green!5}African & \cellcolor{green!5}Black & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}This is a woman!  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}Is it counted gay if I think he s hot even though he used to be a girl  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}Wait, he s wasn t born with a mans body! It s crazy what the testosterone does  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}I always respected to gay people, or lesbian people, but i can't be respect for transgender people, cuz they are not be grateful for herself or himself, Women cant be a whole men or real boy, Or vice versa  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}Actually insane he is ftm, like he looks so natural it's crazy!!  3  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}flolo crafted Lp it only hurts people with rainbow coloured hair. You re right, this shite crazy. Hard to believe the guy in the vid was ever a girl though...  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}Children make the decision to kill themselves at this age. I myself am transgender and pre transition I attempted suicide I am now living as a boy and am so much happier  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}No, you would've only made that decision if you were actually transgender. People don't do it for fun. Try living as a transgender person for just one day and then ask yourself if that is the life you would choose. Society is cruel as fuck. Your reasoning is ridiculously weak.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}Not So Neurotypical No, certainly not you. You are transgender, you get it better than anyone else. My reply was to the original comment by Jane.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}people can grow up and be men!(if you are a man) girls should not be trying to be men and boys should not be looking like woman NO!!!!!!!!!!  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}The Majestic Hawk im not rainbow colored , and its hurst my mind to see stupid people like you , with no whatsoever intelect  & \cellcolor{green!27}Colored & \cellcolor{green!27}Black & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}Litle Ken i mean that i hate this transgender shit, its unatural and ieven though im athiest, if there is a god, i dont think this would be his idea... but it is pretty incredible how she looks like a man now  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}I agree with you, i think there should be an age restriction in order to go through with this process like if its a 30 year old man wanting to change his gender than fine he is just mentally retarded but if a 16 year old wants to do this than the parents should be thrown in prison for allowing it  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}Apparently it's legal to change your   gender  from the age of 6. Any parent who allows their child to do that is practically abusing them  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}Dang I would date you if you were gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}So ur not gay if u like her  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}SHE is not gay.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}Ew gay people.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}oAxid damn man ! Stop ! Being gay isn t disgusting everyone is different !  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}There s literally no way that anyone can tell that you re transgender. You did a great job man. :)  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}How old do you have to be to take testosterone?  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5} AR Fifteens I'm the dumbass? Look who's talking. He was never a girl, he was born biologically female but he's a guy because gender and sex are 2 different things. Do some fucking research, you clearly don't even know what transgender means.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27} AR Fifteens  He. He's a human being, calling him 'It' is just stupid and disrespectful (like the rest of your comments). He's a man because he has a male brain, not because he 'thinks he's one'. He still has a vagina and breasts, but he's a man. Look up the definition of gender. It isn't based on your body, because it isn't biological.  He was never a girl. You should seriously get educated, I doubt you're over the age of 9 but you are seriously fucking ignorant, hateful, transphobic and stupid. Get help, asshole.  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/94 & \cellcolor{green!27}1.064 \\  \hline
  \cellcolor{green!5}AR Fifteens sex, is different than gender. It s possible to change your sex, but only with surgery. Do some research, dipshit  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27} Andy BVB no it isn t dude... gender has always been associated with sex but only until recently trans people have been altering its meaning to suggest that means what you identify as being personality based. But it really isn t lol.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5} Annamation   what did you say? Did you just say it s possible to change sex with surgery! Are you braindead?  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}But im a man if i wanna add a bit of muscle with test. I am a freak and told to go home by my doctor    & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}FUKIN GAY  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Snaze Gaming what. Sexuality and gender are two VERY different things  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}if she is a trans gender and is a  guy  now and wants to date girls its still lesbian shit  & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Female homosexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}well... if you are a felamle than yes, but even they it sounds lesbian xd  & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Female homosexuality & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}  Spidertrash   she doesn't she looks like a scrawny white 'boy' while Chris Evans is a normal man  & \cellcolor{green!5}Scrawny & \cellcolor{green!5}Physical Features & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}Can someone answer this for me please, because I cant get my head round it. If gender is a social construct, how can gender dysphoria be biological?   You see, if gender is a social construct, then gender dysphoria MUST be a mental illness, right? On the other hand, if gender dysphoria is biological, if people can actually be born 'wrong-brained' ...then there can only be two genders, right?   It seems to me that the trans community are trying to argue that gender is both biologically determined and a social construct that can be whatever you want it to be. It cant logically be both. You see the problem?  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/108 & \cellcolor{green!27}0.926 \\  \hline
  \cellcolor{green!5}Martyntd5 I think of gender and sex as two things you re born as. My sex is female because I have higher estrogen levels, breasts and a vagina, but my gender is genderfluid. Gender has always been physiological thing because  it s not a physical feature. Sex has always been a biological thing because it is what parts you have. Gender dysphoria is also physiological because it s mostly caused by people using the wrong pronouns or bringing up things that are for the wrong gender.  Whoever told you that gender dysphoria is biological is incorrect  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/93 & \cellcolor{green!5}1.075 \\  \hline
  \cellcolor{green!27} Anna Mation ///Gender dysphoria is also physiological because it s mostly caused by people using the wrong pronouns or bringing up things that are for the wrong gender. Whoever told you that gender dysphoria is biological is incorrect///  Can I ask you to clarify this, because physiology is a subset of biology, if something is physiological, then it must also be biological.   Did you mean psychological?  Are you saying that gender dysphoria is exclusively a mental illness? You see, if gender dysphoria is a mental health problem and nothing else, then that begs the question  how can surgery be justified? The surgical treatment of mental health problems went out of fashion with the lobotomy. If gender dysphoria is exclusively a mental health issue, how can you possibly justify giving puberty blockers to pre-pubescent children? If gender dysphoria is not a physical, biological thing, then reassignment surgery is just a huge sticking plaster that does nothing more than prop up someone's illusions.  You see the problem? For reassignment surgery to be a rational, logical option, then you have to accept that gender dysphoria is biological. That you can be born the 'wrong' gender. If you accept that gender dysphoria is biological, then there can only be two genders. If you dont accept that gender dysphoria is biological, then it can only be psychological. That makes gender dysphoria a mental illness and reassignment surgery becomes irrational and immoral in many cases. You cant have it both ways. Whichever side you come down on, your choice alienates half of the trans community.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/258 & \cellcolor{green!27}0.388 \\  \hline
  \cellcolor{green!5}its a mental illness. Ben Shapiro. Look him up.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}jasonudliketoknow it s not a mental illness dip shut  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}He's actually smart. Trans and gays are mental illnesses.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}gender dysphoria is a mental disease that is clearly stated in the DSM-5. everyone who says anything otherwise has their head in the sand and is purposefully being ignorant. period, end.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}Koctail Games gays arent mental illness. evidence? you're just a bigot. transgenderism itself isnt a mental disorder but trans people have gender dysphoria which is considered a mental illness. but trans prople itself isnt. will you call depressed people a mental illness? lol.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}chadee   Actually some people call depression mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Depressed people have a mental illness. I can't argue with someone who thinks depression isn't a mental illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}depressed people have a mental disease, transgender people have a mental disease and schizophrenics have a mental disease. guys, this is not hard!  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}Koctail Games Um, no. Being a homosexual isn't a mental illness. It is just a sexual orientation.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}jasonudliketoknow who is Ben Sharpiro. As far as this being mental illness...this guy is pretty clear and solid. I don't pick that up from him. I just think this is weird for you to breath in and accepting that people really do this disrupts your peace of mind.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}Even if it is a mental illness why it concerns you what other people do, in order  to feel happy? I am suffering from severe depression and other psychosis and yes I am mentally ill and not gay or trans, would you want to take off my meds because you don't like them?  what's up to you what depressed people do to feel happy? that's plain fascism! or religious lunacy! By the way, christians who are against trans  n gays, are way more mentally ill than them! At least most trans people don't have imaginary friends, and don't believe in paranoic, fearmongering and hateful misanthropic fairytales!  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/106 & \cellcolor{green!5}0.943 \\  \hline
  \cellcolor{green!27}HASHEAVEN I m an atheist and being transgender is a mental disease. Sorry about your depression, keep taking your placebos.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}Let's accept it's a disease...  Then all people who don't accept the gender they are born with having this so-called ''mental disease'' even if they try to act straight and oppress their feelings and they way they naturally faction since they are born. So being trans isn't the disease we talk about, but the solution many of these people find to ''cure'' this disease! Since there are no meds that can make them accept their gender! (different to gays who accept their gender and the body they are born with)! So even if it is a disease, we should let them be whatever makes them happy.  and not point the finger at them telling them they are mentally ill! Fighting their inner self because of taboos, and being oppressed and ridiculed by society, is way worse for them than letting them be and dress as they wish! (and can lead to unhappy lifes,  depression, marginalism, and even to suicides.)  And if all people who don't like their body they are born with are mentally ill, then 90  of the planet have mental diseases.  So if you are streight and aren't affected by this it's unethical and sort of evil attacking people with ''mental illnesses'' just because you don't like them. It's like going to psychiatric hospitals telling the patients -Hey dude you have a mental disease!!  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/226 & \cellcolor{green!5}0.442 \\  \hline
  \cellcolor{green!27}jasonudliketoknow why do you assume that it s a mental illness? Why not a physical illness. The person in the video is a male. The consciousness is male. If the consciousness says it s male and feels like it s male. It s fucking male. The body is the part which is the illness. The consciousness is you. You aren t your body. You say  that is MY dick  not  that is me  because you are separate to your body (sorta). Now on the logic that we have here. The person in this video is a male. The body is a female. So what are they? I say male. If your consciousness is male then I think  you re male. But it is of course a mater of perspective. And this guy isn t hurting anyone, not even himself. So what s the problem?  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/136 & \cellcolor{green!27}0.735 \\  \hline
  \cellcolor{green!5}Samuel Williams A dolphin is mammal no matter if it wanted to be a fish. This girl embodies the real problem of everything and that is delusion. I m an atheist and I believe that human purpose is to enhance the present so that there is a more advanced tomorrow. Gays, Trans, Queer whatever you call it only deprecates human existence. Non existent terms such as zoophilia currently are on the rise simply because of moronic liberals caring about people s  feelings . I m pretty sure within a few years when you find Femenazis ranting on about  She just wants to have sex with her dog, it s physically what she requires  you ll be much happier.  & \cellcolor{green!5}Queer & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/112 & \cellcolor{green!5}0.893 \\  \hline
  \cellcolor{green!27}jasonudliketoknow gender dysphoria is a mental illness not transgenderism its self.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}Koctail Games you need to reread what i said but okay doki my friend. but in case you can't here's baby words for you  transgenderism itself is not a mental illness. gender dysphoria is a mental illness, not transgenderism. the same way depressed PEOPLE itself is not a mental illness but DEPRESSION is a mental illness..  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}Tennessee Redneck even if you say that, you said something that you knew would cause a comotion here, so you kinda start the argument, it's not them making their life harder, is you who is doing it    & \cellcolor{green!27}Redneck & \cellcolor{green!27}Working class & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}I want to be a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}So she looks like a male, good for her. But she's still a female. Analyze her DNA to prove me wrong. Well, as far as sexuality goes she's a  she , but since  gender  has lately been misused and has started to become more of a self-proclaimed thing, I guess it's alright to refer to her as  he . Grammatically It's justified by the intention, but it's still correct to use  she  since you could mean that you're using the biological pronoun and not the  intentional  one. Aaah, grammar....  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}Tennessee Redneck Yee Yee. I with ya  & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}And he even got an adam's apple  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}Smonster TIME don t u understand he s transgender so he went from female to male  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}lol thats a fucking female, its got a pussy  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}Jaclynkay would say he look gay tho  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Tennessee Redneck there is allot of things wrong with that sentence  & \cellcolor{green!27}Redneck & \cellcolor{green!27}Working class & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}Tennessee Redneck I'm liberal and I agree with you to a certain extent. I agree she's/he's not male in my opinion, but she/he is still a human being with emotions and feelings. You should still treat transgender/gay people with respect even if you don't agree with their views  & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}He is nothing less than human, I will call him a  he  out of respect but he was born as a  she  and still is we can't pretend he isn't. Honestly this type of shit scares me. If some guy comes up to me pretending he's a girl and a few months later reveals that to me, I don't give a fuck. I would run for the mountains. I would hope that a trans guy would go for a trans women but that is very unlikely so who will they go for next?  A trans person should tell us their trans before we start chatting, and don't start saying why don't straight people tell us their straight before they communicate because truth is they are the norm. Fact. Don't take offence, everyone is human and should be treated no less. Testosterone won't grow you a dick and you cannot produce sperm. He IS a female but out of respect I'll refer to him as he. He has a female brain (yes that exists) and if I thought I was a horse it does not make me a horse. He's transgender.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/190 & \cellcolor{green!27}0.526 \\  \hline
  \cellcolor{green!5} oh he still is a woman  he identifies as a man, why are you guys so bothered with people being themselves and happy?  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}Tennessee Redneck- Has your dumb mind forgotten simple gender pronouns taught in kindergarten, or have you not passed that stage of life yet?  Dictionary: IT Referring to an animal or child of unspecified sex. In this situation the sex is specified, he would preferred to be referred to as a 'he'. But you being the transphobic person you are, would ignore his humane choice. And don't bring God into this, God would most likely support him in his choices because as said in the bible  God loves every man  (not the exact quote). Your geeky-but-wrong 9-year-old self will probably next say  but 'it' isn't human . Well he obviously is human, he has been to the doctors at least once and if they would've seen any traces of alien life, it would be all over the news!  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/135 & \cellcolor{green!27}0.741 \\  \hline
  \cellcolor{green!5}Tennessee Redneck it damn mate that'd cancerous  & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Tennessee Redneck In the same sense youtube shouldn't consider nudity a shemales boobs since in your logic he is still a man, but it does... so youtube is wrong! Besides what str8 man would get turned on by her/his nipples as they are on this video? All I can see is a dude's chest, If you didn't know her,  you would also think he is a dude as that's what he looks like!  So it's not   ''just a screwed up fantasy of  hers '' as you say but a reality, and yes youtube is wrong and so are you!  & \cellcolor{green!27}Redneck & \cellcolor{green!27}Working class & \cellcolor{green!27}1/98 & \cellcolor{green!27}1.02 \\  \hline
  \cellcolor{green!5}Then ur dumb  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}lol u such a obvious troll now Tennessee Redneck  & \cellcolor{green!27}Redneck & \cellcolor{green!27}Working class & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}lmao it is a woman that's why  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}TheSuperSaturos he is a male tho.. maybe not biological but for the society he's a male  gender and sex is not the same! he will always be a biological female but that does not mean that he can't live his life as a man in society he has genderdysphoria and this is a serious problem.. not a serious problem for you or society in general but for him.. it's really hard to live with a genderdisphoria and he tries everything to make himself feel as comfortable as possible because he's not a biological male.. btw it's he/him and not she/her because pronouns have nothing to do with x or y chromosomes  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/111 & \cellcolor{green!27}0.901 \\  \hline
  \cellcolor{green!5}Karkat Vantas Well, picking up my example, I can live socially as Batman and have people calling me Mr. Wayne, would that make me Batman? No, It makes me insane. Gender dysphoria is a cute euphemism for  thinking you're something you're not . If I think I'm Batman, I need medical treatment, not people saying  It's okay, you can be whatever you want, Mr. Wayne . How is Gender dysphoria different from other psychological problems like messiah complex? And considering 40  of transgenders have attempted suicide at some point, I don't believe that saying it's okay to think you're a (wo)man is the correct approach to this issue.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/106 & \cellcolor{green!5}0.943 \\  \hline
  \cellcolor{green!27}TheSuperSaturos the trans people who did commit suicide (or have suicidal thoughts) did not do it because they're trans but because of people like you who say they're  insane  or  freaks  if they're trans.. or that they should just accept their biological gender (which is impossible if you have genderdysphoria) by they way they do not think that they're the opposite gender they do know very well what biological gender they are.. but they don't want to live like that (which is also not a personal decision.. they just cant live like that if they really want to enjoy their life)  anyway I see that it's pointless because you just can't understand the pain of a transgender person also there are no pills or medicine who can actually heal genderdysphoria (believe me some transpeople really don't wanna be trans and would prefer to just be happy with their biological gender and  fit in ) so the only way you can be happy with this disorder is through transitions/hormones otherwise they might commit suicide because who would want to live in pain for their whole life?  actually you can compare genderdysphoria with an autoimmune disease with the only difference that it's mental and not physical  and please don't compare it to a stupid costume.. it really is a disorder you know? you can compare it to other disorders for example but come on.. it's not in a single way like a costume.. transpeople don't want to be a fictional character who can do impossible things.. they only want to live a life as the opposite gender and again they do know that they're not an 100  actual biological male.. it's really silly to compare it to a person who believes they're batman because of a costume  I'm gonna repeat myself just to make sure: It's pointless to talk to you about stuff like that because you will never change your opinion no matter what would happen.. even if a loved person of yours would be trans you would probably call them insane and what not until they commit suicide  have a nice day mr. wayne  and excuse my english it's not my native language but I'm sure you were able to understand me anyway  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/372 & \cellcolor{green!27}0.269 \\  \hline
  \cellcolor{green!5}Karkat Vantas Hey, hey, hey, hold on! I don't see trans people as freaks, that actually offends me because you're accusing me of something I'm clearly not, I respect everyone EQUALLY. What I'm saying is that transgenders are people who need help to blend in our society, but  feeding  their gender dysphoria by saying  you can be whatever you want  is no help at all.  Well, guess what people with messiah complex say:  I KNOW I'm destined to something big. I'm SURE I'll save my country/the world.  People with disorders of this kind usually deny they have a problem until it's evident for them that something's not right. Even if it's not the same as that, as the name says, it's, like depression or anxiety. People with any kind of dysphoria seek psychology to overcome that mental state, not pills to  feed  the problem even more.   Let's say I have depression because I'm physically handicapped (which I actually am, it's a disease with unknown cure or treatment, but I have no depression because of that). If I go to a psychologist, he won't tell me  oh, poor thing. I'll give you artificial legs so you can walk , he will try to make me accept what I am and live my life the best I can. My parents suffered from serious depression after my brother died (I didn't because I was a baby), they went to a psychologist and he helped them accept and overcome his death, he didn't say  you can have another kid to replace him , that's absurd (and cruel, too).  Besides, can you back that up? Can you prove that trans people commit suicide only because they're not accepted? How do you know there aren't other reasons? Most transgender people who try or commit suicide are teens and young adults, a period of life that is very hard and confusing for most heterossexuals, imagine what it's like for transgenders: severe cases of identity crisis which leads to depression, which may lead to suicide. Relationship problems, unhappiness with body modifications, etc, etc... See? There are other possible reasons. As far as I'm aware, transssexuals and transgenders are getting more and more respected and accepted, but the suicide rates are this high. It simply doesn't make sense.  Last, but not least, I used to be homophobic, I despised gays and saw them as abnormals, and I've changed my mind because someone convinced me it wasn't like that. I will change my opinion on this matter when you or someone else use convincing enough arguments.  And regarding your english, no problem. English isn't my first language either.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/436 & \cellcolor{green!5}0.229 \\  \hline
  \cellcolor{green!27}TheSuperSaturos maybe you don't see them exactly as  freaks  but you do definitely not accept them the way they are because you said transitions are the wrong way to help those people which clearly isn't the case because they are much happier after their transition  you want them to suffer their whole life because you say  you can't be who/whatever you want  as if they would want to be unicorns or superheros  everything about gender is a society problem and in my opinion everyone can live their life how they want to and they just want to be accepted as a male/female in our soxiety and want you to use he/him pronouns and that's it so where's the fucking problem? now let's talk about surgery  woman can get a top surgery to make their breasts bigger so they feel more comfortable in their body so why can't other  woman  make their breasts smaller because of the the same reason?  it's everything about/because of our society.. and maybe you also don't like that some women make their breasts bigger or anything like that but I'm sure you say  It's their life so I don't care  and same with tattoos but OOOHHH don't a stranger dare to identify as the opposite gender and make them feel comfortable in their body and life  look if you have genderdysphoria everything you do is using other pronouns.. changing your name and maybe doing some surgeries and taking hormones and after that they are mostly likely happy for the rest of their life.. they do not bring anyone else in danger and harm no one around them  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/271 & \cellcolor{green!27}0.369 \\  \hline
  \cellcolor{green!5}Karkat Vantas You're so wrong about me, dude, but I'll get there.   Are they really happy after the transition? Happy people don't commit suicide. People can do whatever they want, even live in a world of lies and illusions, but don't come complaining and whining if you find out that escapism doesn't solve your problems.  Now that's where you're mistaken about me. If I wanted them to suffer, I wouldn't want to help them accept themselves and seek help if they need. How can they be accepted if they don't do it for themselves first?   I'm not against breast augmentation, but I don't advise it because implants may cause lymphomas and other serious problems which will require the remotion of the breast in worst case scenarios. There are also bad surgeons that, yes, make your boobs bigger, but then they get ugly because the surgeon is a bad professional. Assymetrical breasts, balloon/gravity defying breasts and visible scars are very common  issues  in breast augmentation surgeries. If a woman close to me asked my opinion I'd say  don't do it, because (insert reasons I said before) . As for breast reduction, there's no danger other than visible scars, so I'd say  it's a waste, but go ahead and do it if you want .  As for tattoos, it's the same: not against it, but I don't advise it. Big tattoos are cool when we're young, but when we get old and the skin gets flabby, the tattoo will be ruined and you will regret it. The remotion of tattoos is expensive and painful, there's that, too.  As for gender and society, the word  gender  itself as we're using it is a social construct made by those who say everything's a social construct. In reality, there's no such thing as genders, in this context, of course. What exist are men and women with different personalities: from feminine men to masculine women. Even I, sometimes feel more feminine or more masculine. Sometimes I'm grossed out or apathic to sexual stimuli, sometimes I respond positively to it. Sometimes I like shopping, sometimes I like MMA. Does it mean I'm genderfluid (is that the word?)? No, it just means I have a personality that changes according to my state of mind and it can change in a matter of seconds. Gender is just a word that mostly feminists and LGBT activists use in a deceptive manner, claiming that a feminine man or a masculine woman is a gender amongst 153 others.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/414 & \cellcolor{green!5}0.242 \\  \hline
  \cellcolor{green!27}TheSuperSaturos okay just to make things clear I only believe in Female, male and transgender and nothing else  and now you don't get the point again.. gender has nothing to do with your personality.. transgender people only like to be seen as a male (I'm gonna use female to male as example) meaning they want to use he/him pronouns maybe want a deeper voice and a flat chest.. it's nothing about your personality at all  and you know if you would really want transgender people to be happy you would support them on their way of transitioning and not say  accept your biological gender I don't care if you're getting depressed because of it or hate yourself so much that I can't even imagine it and that only because of your biological gender  (I know those are not your exact words but that's basically what it is.. you want them to accept themselves as their biological gender but you don't want to accept them being transgender even tho they would feel way better this way)  I'm sorry if I got a wrong picture of you but let's be honest.. you're not helping them at all like this..  and again.. it's nothing about your personality  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/204 & \cellcolor{green!27}0.49 \\  \hline
  \cellcolor{green!5}Karkat Vantas We don't know if it helps. Have we tried? No. Because transgender people don't make sense: they claim they need to change sex in order to be happy. They change sex, but still 40  of them commit suicide, which means they're still not happy. We try to accept them more and more and the numbers still  won't go down. When we try a different approach, they call us, explicitly or implicitly, transphobic. So what the fuck are we supposed to do?  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}TheSuperSaturos what you're supposed to do? nothing! that's none of your buisness at all.. maybe people should just accept them as their  wrong  gender.. try to see them as actual males even if they were born a female.. no one cares about the x/y chromosome  you know being trans is a thing.. transitioning is the way how we face the disorder these days.. this is what psychologists decided is the best for transpeople.. and I think they know what they do..    transpeople who commit suicide might have other reasons for this just like other cis people who commit suicide too.. not all of them commit suicide because they are trans (at least not after the transition) yes maybe some of them but not all of them.. and just because you transitioned doesn't mean all your problems are gone.. transpeople have other problems as well just like normal people because that's what they are.. normal people  and again being trans is not easy.. you have to talk to so many psychologists.. have to make a test that goes at least one year and only after that and after more than just one psychologist said it's the only way.. only after that.. you are allowed to take hormones/surgeries and don't forget that they don't run to a psychologist right after they just came up with the thought of maybe being transgender no.. so the way for transpeople is really hard and long..  and why? because they don't want people who aren't actually trans to make the biggest mistake in their life.. and because of all this it is mostly the case that they are happy after transitioning because many psychologists thought about it asked you so many questions and what not just so they can be at least 90  sure that it's the right thing for you  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/305 & \cellcolor{green!27}0.328 \\  \hline
  \cellcolor{green!5}Karkat Vantas So, I'm supposed to forget common sense and pretend that men are women and women are men? I'm supposed to accept that almost half of transgenders commit suicide? I'm supposed to just let them call me names because I want to treat gender dysphoria as what it is: a dysphoria? Sorry, but no. I'm not gonna just sit and do nothing. What psychologists do nowadays isn't a definitive solution, it's clearly a temporary one, looking at the suicide rates.   Yes, cis people also commit suicide, but they're not even near 40 . You can't compare. If even after 1 year of examining transgenders and after the transition, some still commit suicide, then psychologists are obviously doing something wrong. That's the famous definition of insanity: doing the same thing over and over again and expect different results. Assuming most transgenders nowadays seek psychologists, but still their methodology for treating gender dysphoria has a success rate of nearly 60  (pretty low compared to other dysphorias like anxiety and depression), that means that sex transition still isn't the ideal treatment. The logical solution is  let's try other methods and see how it goes . That's how science approaches problems, try different methods until one reaches satisfactory results and 60  success rate is nowhere near satisfactory.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/212 & \cellcolor{green!5}0.472 \\  \hline
  \cellcolor{green!27}Because she's still a woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}TheSuperSaturos Transgender already DO get help and treatment. The treatment is medical too. It entails taking hormonal supplements for the rest of their lives to ensure that their body matches who they are (their gender). Gender dysphoria is not as simplistic as a psychological problem, as you state. It is a physiological anomaly that can only be treated by making the body match up with the gender that the brain IS. It's not a mental illness or a personality disorder. It's way more complex than that. How does it hurt you in any way that the preferred treatment (only treatment that works) is not what you subjectively (and naively) believe what is right and wrong? It doesn't affect you in any way. So it's not your place, at all, to determine what the best option is for those who are transgender.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/141 & \cellcolor{green!5}0.709 \\  \hline
  \cellcolor{green!27}TheSuperSaturos you gotta get your facts straight.  almost half of transgenders commit suicide  because they are shunned by society and are unable to, or prevented from receiving gender reassignment treatments. THAT's why they commit suicide. Try look up the statistics on suicide amongst transgendered people who have successfully transitioned... I challenge you  )  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}Tennessee Redneck you happy with your self. I would rather ve transgender than be as fat as you..  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27} TheSuperSaturos bcoz tht Batman shit is not really real and gender dsyphoria is REAL  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}of course,biogically female,but hes a man now   old fashion shit  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Pronouns aren't used to show respect, they're used to refer to someone's gender, so using pronouns for respect doesn't work in the English language. Additionally, she's still genetically female and always will be. She will never be truly male and that's sort of something she has to deal with.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5} aaron do u even know what pronouns mean?get urslf educated with this thing before u judge people stop looking like a dumb shit  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27} Tennessee Redneck Okay, so first of all, that person that you called  she  is on Testosterone. Why? To feel complete and comfortable in their body. Now even though I don't know their pronouns, but a nice and neutral way would be using they/them pronouns. If they do identify as male, they are FULLY valid- as valid as any cis-male could be.  & \cellcolor{green!27}Redneck & \cellcolor{green!27}Working class & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5} Tennessee Redneck Also, Youtube is censoring their nipples to hide anything that the poster feels uncomfortable about and to follow the rules (No nudity)...  & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}One ugly ass woman. Good luck finding a husband and raising a sane family now.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}Because its El Female and need to be El Executo. Transgender is a mental disability. You are a girl or guy that thing up above in the video is disgusting.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}if the dude is not okay with this then he doesnt have to be like just cause this is  part of this day and age  doesnt mean he has to give in and do what other people say just because they dont identify as what they are. everyone has their own opinions and if you dont agree with that then  this day and age is not for you   & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5}I currently identify as an apache attack helicopter and I want my pronouns to be Apach and Apach's. Next week though I'm thinking about changing to an apple and then I want my pronouns to be it and it's. Also I have it planed for the first week of August to change to a piano. I'm still working on the pronouns for for piano I was thinking something like pianer and pianoes. Let me know what you think.  & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/78 & \cellcolor{green!5}1.282 \\  \hline
  \cellcolor{green!27}If ur trans cuz you have a mental illness or disability that makes you associate with the other gender, then  change  genders by all means, it only makes more sense. If you change because you WANT to be the other gender, then by all means, kill yourself. You don t associate with the other gender, you just want to reap benefits, lose responsibilities or run away from issues you have of your current gender.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5}Tennessee Redneck bitch, he s more of a man than you ll ever be. Sit tf down.  & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}I identify as a promiscuous toddler and you better respek dat and educate yourself.  & \cellcolor{green!27}Promiscuous & \cellcolor{green!27}Female sexuality & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}Ted Barrera what. You can t change genetics, but guess what-this is a big secret- gender isn t determined by your genetics. WOAH IKR  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Andrei sex organs does NOT determine gender. So shut the fuck up, be respectful and accept that HE is a BOY.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}Moni Sings actually sex organs do determine gender  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}Nobody cares get off his channel  & \cellcolor{green!27}Nobody & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}jesus Actually, yes! Women can actually make other women pregnant, but the process does not involve sex.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}rhiannon No, they can't. And only men can impregnate women, involving sex or not. Women can not produce sperm cells which are required to form a zygote, which grows up to be a human being. Transgender is the most stupid thing in the history of the world. What's next? Us impregnating animals?  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/52 & \cellcolor{green!27}1.923 \\  \hline
  \cellcolor{green!5}jesus  transgender is the most stupidest thing in the world.  Honey have you looked in the mirror lately? LOL  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}Hayden Clark HAH. lemme guess  you re a triggered snowflake?  & \cellcolor{green!27}Snowflake & \cellcolor{green!27} Ideological and Political Identity & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}Aww... You look beautiful. Congratulations on your transition.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}Steinal  Congratulations for being mental disability  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Sarrah, gender dysphoria is a mental illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}What You Egg V.2  Some people don't what to believe the facts i bet she didn't believe in history because she is an alien  & \cellcolor{green!27}Alien & \cellcolor{green!27}Nationality & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}Sarrah Siano Doesn't matter  If you're a hater or not it's a mental disorder. Worst of all Society Glorifies this, it's absolutely horrible nice people have to go through this. Next thing you know they'll start glorifying being mentally unstable because  OH they're left out . It's the truth there can't be opinions for this.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/54 & \cellcolor{green!5}1.852 \\  \hline
  \cellcolor{green!27}It may be a mental transition, but all it does is make the person feel wrong in the body they were born with. They didn't choose to be born with it. Just let them be happy.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}hey um....being born a woman typically means that you have XX chromosomes so yeah. Basic highschool science.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}it is impossible to change your genetic chromosomes or change your gender she still is a girl xx chromosomes  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}Annamation it is like unfathomable how dumb that is, females are born with XX chromosomes this is a female, testosterone will not change your chromosomes.  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}Annamation   Basic science: Females have XX, Males have XY. Therefore she is born with the XX chromosomes and will biologically always be a female. Even though you become transgender does not mean you entirely shift to the other gender.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}Yes. Biologically, he is still a woman, but he doesn't feel good as female, so his body is male now. Just let him/her be happy. Happiness is all we want after all.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}i dont feel good being a white man. therefore, i am now a black kid from michigan named requise. and if you don't refer to me as Zim, Zee or Zeys... ill have you fired  & \cellcolor{green!27}Black & \cellcolor{green!27}Black & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}You are mental health for wanting to look like the opposite sex.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}You sound just as dumb as her. You are adding to her nonsense. She is not even being a real woman. There is no way someone would be happy trying to be something that there not.  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}Maurice Williams if you re not happy it s your problem, im not dumb at all it s just my opinion, he look happy to me probably more than before the transition , who are you to tell what people have to do or to be  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}Maurice Williams he is not even being a real woman because he is a male  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}hdhgd gfgfb You know damn well she is a woman taking testosterone. Why are you lying  ?  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}Maurice Williams i know he his a transgender male  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}hdhgd gfgfb she is still a woman. That's how she was born that's how she'll die.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Maurice Williams woah I didn t know a person could become a metaphorical object. That s crazy  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}kylie don't be assuming things and insulting a man for expressing is well deserved opinion. This is a case of mental illness  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Nathan Ochoa how is it a case of mental illness?? yeah, it's not. and I have my opinions too, and I can express them too.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}Yes!! You can express them but there is no need to insulting the man and it's a case of mental Ilness because we have a girl who whishes to claim she is a he when in fact she is a she but yet goes around demanding that people refer to her as Bret and to make it worse takes hormones that her body doesn't even produce ..  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/67 & \cellcolor{green!5}1.493 \\  \hline
  \cellcolor{green!27}kylie She's still a woman tho. You can change how you look but you can't change the genetics. You will always be who you were born  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}Good thing he's not a woman!!!    & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}ew what the fuck this chick is crazy  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}still woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Finska wdym? he's a man, there is nothing else to explain.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}Camera Man what's wrong with him? What he's doing isn't hurting you in any way. You don't have to accept him entirely but please explain what he's doing wrong that affects your life so greatly. How am I 'unintelligent' for helping another human being that's doing nothing wrong  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}What about pussy  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}kylie no he s a woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}kylie woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}Poor Girl has such a bad mental disorder. I hope she can find peace with this illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}Don't know why this is recommended to me, but anyway...   Benton Just wanna say that testosterone has the muscle increase effect on men too. Nothing to do with changing from female to male.  It can also have other effects you may noticed like fat loss, or shape changes.  This is why it's used by most bodybuiders, and also why in most countries or international sport competitions it's illegal.  Also recently I read that it can cause memory issues, nothing major though.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/81 & \cellcolor{green!27}1.235 \\  \hline
  \cellcolor{green!5}considering your profile picture is Mountain Dew I'm guessing youre an inbred redneck 10 year old  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}what gay ? explain....  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}You  little fucker don't say that that's gay and you sad person liking your own comments  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}b da Schurkan, he is female to male or FTM. Males who would like to transition to females are MTF. Hope that made sense :)  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}GENDER DYSPHORIA  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}I hope it stays as a normal pussy, so at least if you're horny you just have to look down with a mirror, but wait you can't get erection.... my bad  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}AJPlayzify no it s not you fucking retard  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}you are still a woman. And still under the anger of God.  Accept Jesus start reading the Bible I dont want you to end up in Hell but I surely dont want you to be gay!  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}fallenSlave, sorry to break it to you but the bible has been written over many times all different from the last. The person in which to write the bible was man, If God made man in his figure man would love all, an hate no one. Because we are all gods children and god coul neer hate his creation.  God made this path for the lgbt because there are the strong to follow their wishes a d there paths to there greatness.  And even besides if god exists or not we should love each other anyway.  If we did there would be no wars, no hate no discrimination and no cruelty. But because of naive people such as yourself we can't cross that line of happiness.  & \cellcolor{green!5}LGBT & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/126 & \cellcolor{green!5}0.794 \\  \hline
  \cellcolor{green!27}fallenSlave he is transgender, and he is a male. not a female. MALE. A BOY. A MAN. God is not angry at this man. God loves him just as much as he loves you.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}Wait. Does homophobia and transphobia STILL exist?!? I could ve sworn that it s the 21st century!  & \cellcolor{green!5}Homophobia & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}You both are  Stupid . Is like two unintelligent cat's fighting with each other. The dumb Soical justice warrior and dumb Christian. I do agree with Christian on this point but not in god, but at the same time! She is still fucking women because it is written in her DNA! That's where biologi class begin! But i Guess soical justice warrior's got F in that class.  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}Igloo Dreggin That's ironic, Coming from someone who doesn't know shit from biology class.  This women is taking drug T is male hormone not female vise versa.  There is only two gender because it is related to sex  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}fallenSlave Jesus can suck his pussy. The anger of god ca suck his pussy. Fuck religion.  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}Oopsie  Well i dislike LGBT community but you need to learn to show  Manners  to everyone.  & \cellcolor{green!5}LGBT & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}After your massive testosterone addiction you just look like a little scrawny faggot with the appearance of a twelve years old boy. That is your only achievement so far and only if you want to die of an overdose you will not get anything else out of it. I would suggest to you giving up with this nonsense and accept yourself like you are  that is as a WOMAN, before you repent yourself and start suffering the miseries and diseases of these misleaded, unnatural and decietful choices.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/87 & \cellcolor{green!27}1.149 \\  \hline
  \cellcolor{green!5}Why the fuck would you change your gender? That's gross.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}thats nasty go back to a woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}HE was never a woman idiot  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Nathan Ryan he, and he will not be a woman ever again.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5} Raiden3 does it have a pussy and females hormones? It s a female fucktard!!!  & \cellcolor{green!5}pussy & \cellcolor{green!5}Chinese & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}Mental issues should be resolved, not encouraged.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}danielul05 it's not a mental issue.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Even if it is a mental illness why it concerns you what other people do, in order  to feel happy? I am suffering from severe depression and other psychosis and yes I am mentally ill and not gay or trans, would you want to take off my meds because you don't like them?  what's up to you what depressed people do to feel happy? that's plain fascism! or religious lunacy! By the way, christians who are against trans  n gays, are way more mentally ill than them! At least most trans people don't have imaginary friends, and don't believe in paranoic, fearmongering and hateful misanthropic fairytales!  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/106 & \cellcolor{green!27}0.943 \\  \hline
  \cellcolor{green!5}The way it is resolved is by changing their gender to the one they wish to be, but some fascist bigots are against things that don't affect them at all and just enjoy others to suffer and  be unhappy just because they don't like them. you can shout at mental illness all you like, but you can affect those people's freedom anyway!  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}And how exactly do you plan to help this  mental illness ? There is nothing wrong with being different. That's like looking at a person of different race or ethnicity and going  You're sick in the head, you could be white if you tried. You should go see a doctor.  That makes absolutely no sense and is ridiculous. It's not an illness to be who you are.  & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/66 & \cellcolor{green!27}1.515 \\  \hline
  \cellcolor{green!5}First of all 'who are you to say' based on ur comment you have never even met a transperson. They are the sex that they know they are. It's nothing like a mental issue. Think of the daily struggles you have to face because they are not comfortable in their body. Who cares about one gene here or there if you don't represent that.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27}There's nothing wrong with humanity. This is the result of us being a highly self-aware and curious species, with a marvellous ability to transform ourselves and our surroundings. We are not bound by anything  life on earth is a big free for all where morals, beliefs etc. are in constant change. Accept the mad house that it is and just go crazy I say!  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}Nobody is encouraging mental issues.....That doesn't even make sense  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}danielul05 Yes, your bigotry is a mental illness, get ir checked. Fucking moron.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}I m agree with you , all this kind of people ,if you get to know them well , you will notice that have very low self esteem , lots of people wants to find an identity, to accept themselves, but never works.  It is so sad the way that they are damaging their bodies, because yes ! It cause damage to the body all this abnormal changes. And all the people that have low self esteems agree with transgender people, and to the people that doesn t support this  , they call us closed mind  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}danielul05 you have a mental illness. can't y'all just let everyone be who they want to be? It's not affecting you in any fucking way but you just have to make their lives harder.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}It depends what you're talking about as a mental issue. For actual scientifically recognized mental disorders like Schizophrenia, Depression, it's best they don't go hidden away. If you're talking about the morons who tell this guy what he should or should not do and why, I agree (if I explain this, i'll come off as offending) but if you're talking about being trans then, my friend, you are the one who needs their problems solved.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/75 & \cellcolor{green!5}1.333 \\  \hline
  \cellcolor{green!27}Gender dysphoria is a mental issue and its resolved with transition. Obviously it doesnt work for everyone but it works for the majority,just as antidepressants dont work for every depressed person. The end  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}i don't even have hair on my chest and belly and i'm a guy. it's genetical though..nobody in my family has  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}is she a tomboy???  & \cellcolor{green!27}Tomboy & \cellcolor{green!27}Female homosexuality & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}Just2Girls are you dumb?  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}i literally cant even tell you are transgender  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Liz Erich He say he is woman in video  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}The title says  Female to Male Transgender.    This boy is, in fact, a male. He looks like a guy because he's been taking testosterone for 2 years.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}Wow it's quite amazing what testosterone can do! I wish you all the best in the future and welcome to the better side of the gender spectrum.. Sorry but its true.. theres zero downsides of being a man. FeelsGoodMan  & \cellcolor{green!5}Zero & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/39 & \cellcolor{green!5}2.564 \\  \hline
  \cellcolor{green!27}tranny  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}this is weird  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}homo sexuale transgender  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/3 & \cellcolor{green!27}33.333 \\  \hline
  \cellcolor{green!5}first of all your sick second of all tell in serbia or russia that you are trans gender and kill you self  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}THIS IS SO CONFUSING ( IM NOT GAY AND IM NOT HOMOPHOBIC) HE IS HOT BUT HE WAS A MALE IN A FEMALE BODY. AM I GAY CAUSE I HAVE A LITTLE CRUSH ON YOU?? AHHH CONFUSION  & \cellcolor{green!27}homophobic & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/37 & \cellcolor{green!27}2.703 \\  \hline
  \cellcolor{green!5}You can't change your Chromosome, you're forever a woman.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Proud Rebel Personally, he's More Than a Woman To Me  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}nah, he's forever a retard :)  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}he has XX chromosome, it doesn't mean he's a woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}Can't blame someone for wanting to be the superior gender  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}The whole transgender thing is fascinating to me, I don t understand it, am intrigued by it and open minded to it. What happens with sexual partners as a result of transitioning, as in, if in a f to m transition you were straight, would that make it harder to find a partner as a straight male would not want to be with another guy? Equally if you were a lesbian would once potential partners be put off because now you are/look male?  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/82 & \cellcolor{green!27}1.22 \\  \hline
  \cellcolor{green!5}Fucking crazy that humankind is able to do this with their bodies.  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}I noticed that too. isn't that a social dilemma LMAO. this crazy world is going to shit.  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}A(N) ELAMEHS   ONLY RED THE FOLLOWING IF YOU DON'T GET IT  (because he/she is a shemale but backwards)  & \cellcolor{green!5}Red & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}still has a pussy though lmfaooo  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}God damn freak  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}Kang Tut  Freak of nature,  is more like it. How awful it must be to be born in the wrong body. What a powerful and strong person he is! I certainly couldn't deal with all the hate I'd get from just trying to be myself, could you?  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/47 & \cellcolor{green!27}2.128 \\  \hline
  \cellcolor{green!5}Are you trying to mimic living with the man's condition? Do you also try to capture the rise and fall of testosterone that naturally occurs in men depending on situations? For example- Falling in love decreases men's testosterone levels while increasing women's testosterone levels. Also, a couple of years into a relationship men who produce less testosterone are more likely to be in that relationship and  men who produce more testosterone are more likely to divorce.  Also, men with raised testosterone are found to be more fair in negotiations but also less generous when there wasn't a clear benefit to be generous.  Men also naturally increase their levels of testosterone if they lift weights, get sun, have a particular diet... excess alcohol or drug use naturally decrease our levels of testosterone.  Do you work with your doctors to try tp mimic this complexity as closely as possible to capture a more authentic male experience?  & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/154 & \cellcolor{green!5}0.649 \\  \hline
  \cellcolor{green!27}I didn't know there were people who are afraid of transgender people. And you say they not only fear them but demand they have a penis and produce cum? The situation in merika is stranger than I thought. Why can't a person just be happy with him/her self? Why is there a need to have breast implants or take hormones? I believe that being beautiful (man or woman) is living healthy. I read that hormone treatments carry unnecessary risk such as an increase rate of cancers...smh  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5}born a female, takes some bullshit, has more chest hair than me, im 27. and born male. fuck you chick  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}You're probably a transvestite with a weak mind. So many transvestites claiming to be transgender. Know the difference.  & \cellcolor{green!27}Transvestite & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}Transvestite- a person who sometimes wears clothes traditionally worn by and associated with the opposite sex  typically a male who cross-dresses occasionally by habit or compulsion. Transvestites are often happy with their gender and have no desire to change their sex, but simply enjoy being able to cross-dress from time to time.  Oh yeah, this is definitely compulsion, appearing as the gender he identifies as. And taking Testosterone for two years is hardly a far cry from occasionally cross-dressing. Thank you for straightening that out.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}what make him transvestite? tranvestite don t take hormones  & \cellcolor{green!27}Transvestite & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}so how will a male transition to female?  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27}I would imagine they take estrogen instead of testosterone, since that induces the growth of secondary female sex characteristics (boobs, extra layer of body fat around the stomach/thighs/glutes, yada yada...) M2F transgenders can also have breast implants, if they so choose, but I'm pretty sure estrogen would be the main thing.   To be honest, Google probably has more information than I do about the actual process of transitioning. Still, I hoped this helped at least a little.  & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Features & \cellcolor{green!27}1/77 & \cellcolor{green!27}1.299 \\  \hline
  \cellcolor{green!5}BOOOOY YOU CUTE AS SHIT HOLD MY GAY ASS BACK  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Smut Brush By that standard, being a teenager in an American High School is an illness.   Btw, that 45  statistic was for Transgender people who were not allowed to express the gender they identified as, or who were ostracized during their transition.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}PLS DONT USE STEROID ... ITS MAKES UR LIVER FAT...  & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Features & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}freak  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}A You forgot the 'onomics' at the end, and I really don't see what the demonization of gluten has to do with this boy's transition progress.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}Liz Erich freak and trannylover  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}A no one is a freak. he is a man who loves himself, let him be who he wants.  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}Yes. a freak, i agree. finally someone who agrees  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}you can not change your gender you femenist scum go fucking killyourself noone will miss you  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Liz Erich it s a girl she is suffering from gender dysphoria look it up  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}You simply cant change your gender, no way. The only reason this  Transgender  thing exists es because of the leftists and the SJW crap out there. Go to school kid. Disgusting  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}Igor Antonovich it s just common sense  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Sarrah Siano, Sexist? i was just telling the truth, you cant change your gender, And if im right this female  here does not have a penis, It's a mental illness. shut up women  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}Fucking feminist shit, go learn something before typing here.  Feminism and SJW shit is ruining our society , you americans are so ignorant and dont know shit, bet  you cant say that   to me IRL woman, go back to the kitchen.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}Sarrah Siano i am grown russia man. my parents dead you see you are america woman, so you are retarded.. ok?   & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Well then, you are women atleast... How old are you little girl? go to school before typing to russian man, for your own good :) so i dont come to your doorstep suka  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}Sarrah  girl , dont burn your brain cells on this dumb fuck. he's russian, he's drunk!  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Poses to be male, still has XX Chromosomes. Gay loser bitch.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}says the retard bitch boy.... HE is a male actually genetically because gender identity IS genetically predisposed PRIOR to full development of body. meaning that HE was a HE before the chromosomes made him a womans' body.  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/37 & \cellcolor{green!5}2.703 \\  \hline
  \cellcolor{green!27}You talk as if there's some  secret ingredient  to a gender  something that the body and mind cannot affect. Are you talking about the soul of a person? To me gender is pretty straight forward  it's how you look on the outside and how you act in regards to others. I'm interested in girls and therefor the person in the video is of no interest to me, as I perceive him very much as a boy. I'm sure most people would follow this sentiment.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}Ethan Strong you're the disgusting here, spreading hate. Why tho? Whatever people change their gender or not it doesn't effect you in any way! Btw being close minded is disgusting.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Mona Lisa it s nasty that your promoting a mental illness.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}This whole comment sections has been filtered. There is NO WAY nobody gave you a negative comment so here we go. You are mentally sick and instead of taking hormones, you need to get fixed. Mental illness shouldnt be  tolerated . You are still female and you will be for the rest of your life. Get help.  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}Read read the Bible you dumb fucking tranny  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}Story time!   If Mary was a virgin when Jesus was conceived, then a Y chromosome was never introduced. If the possesion of that Y chromosome is your definition of a male, then Jesus was... transgender  Also, I'm pretty sure they didn't know about Transgenders when the bible was written.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}Watermelon Seed Yeah, well not everybody believes that a ghost in the sky litterally created matter from nothing.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}Okay give me a second to process what I just read. First you called Jesus TRANSGENDER, then don't believe that being transgender is deforming God's image? It is arrogant to believe that these people can do whatever they want to their body and call themselves  Christian . They use  God made me this way  as an excuse to ruin their body. If you think that Jesus was  transgender (since transgender is a fake term), then you need to read the Bible. God placed baby Jesus into Mary.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/85 & \cellcolor{green!5}1.176 \\  \hline
  \cellcolor{green!27}GAY  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}Right you are, my friend! Female and male are both genders and this boy has been the same gender since he was born. He may change sexes (i.e. having a vagina or a penis) but he has always been and will always be a male.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}no he was born a man, but his chromosomes didn't sync up with his genetic markers that predetermined his identity/gender. which is why gender is the way us educated people view people not but chromosomes lol  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}no so he's male genetically, which derives from his genetic markers. His psychological identity is genetically based, and therefore, not an illness. The body is where biology fucked up. rather than syncing up with the gender, the chromosomes messed up and produced a female body. That's called a genetic anomaly  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}no chromosomes just determine the sex organs. other genetic markers create identity and gender.  that is basic biology. perhaps you need to review harvard's findings....http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}that's scientifically bullshit. Sex organs do not define Gender. that is basic modern science.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Raiden3 thanks for restoring my faith in the human race  & \cellcolor{green!27}Race & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}Raiden3  Are you mentally I'll? There are more proof that TransMale are mentally I'll! And have Bipolar, Autism and personality disorder with it. Did you know what happens for those who said that  They'll can't change their sex ? Yea, got fired because of Social justice! Those who are saying that  You have another brain or something are saving their asses   & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/60 & \cellcolor{green!5}1.667 \\  \hline
  \cellcolor{green!27}Dude you look kinda gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}Two words, mental illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}you look gay asf  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}what happens if you stop the testosterone do you go back to the woman build  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}It's amazing how just hormones can simply change your gender. the body Is truly amazing.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}Chloe Johnson Don't forget, you can change your sex!  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}lol when a femele has more facial/body hair than a real boy at age 19 lmao feels bad  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}mohsin hassan nothing to do for at least two years, wow.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}mohsin hassan i mean you had nothing to do, so you watched this video.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}kylie if anyone have a mental problem he must consult a phycytrist . You have been bless the body of a girl, you need to live like a girl, this is a mental issue. These stupid people just start messing with their body    & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}mohsin hassan it isn't a mental issue. and even though he was born in the body of a woman, he knew he was a man. the only person who has a mental problem here is you.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}mohsin hassan kid listen you clearly don't go to school some people get the wrong body for example: a girl who doesn't like her bottom or top and she wants the body of a man and she wants to live as a man not a woman You can't get over transgenderism it's just there and will forever be untill u make the choice to do the surgery some people have depression because of it So shut the fuck up don't make fun of them  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/84 & \cellcolor{green!5}1.19 \\  \hline
  \cellcolor{green!27}Mohsin Hassan, you really need to move into this Millennium. Clearly you live in the dark ages, just like your neanderthal supported, Murre Khaibulaev. It is a scientific fact that humans are born with different levels of testosterone, this is not my opinion, its a fact. (But it is also my opinion).  If you don't accept this to be true, it s because you are simply a moron. I only wish that you lived nearer to me, so I could arrange to meet you face to face and ,,,,,,,,,,, discuss this. I gather that you think you are some sort of hero in the eyes of the public with your Dickensian, prehistoric,  uneducated, exceptionally ignorant, and uninformed views, but you are NOT a hero. Nor will you ever be respected by any intelligent, emphatic, or forward thinking woman, for your pathetic out-dated views. Crawl back into the hole you somehow managed to escape from, and live your life, like people did 1,000 years ago, as this is where your social and I.Q. level is befitting. And before you make any uninformed comments by return, be aware that I am 100  Male heterosexual, an Ex Super Bike racer, ( I have no fear), I am married to a beautiful woman, the kind that you could only dream about, and I have a daughter who wants to transgender, and become a male. I am fully supporting my amazing child, and I will not accept the kind of comments made by imbeciles like you, who would last 1 minute in the company of the superior people whose presence I frequent. I hope this makes you rethink your narrow minded and out dated point of view. I'm looking forward to your reply, if you think you are informed and articulate enough challenge me, let the battle commence.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/302 & \cellcolor{green!27}0.331 \\  \hline
  \cellcolor{green!5}mohsin hassan This happens when you have nothing to do.  Ok let me comment something stupid, that will be fun  huh  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Up what about his Adams Apple?!how is that possible??  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}hdhgd gfgfb Testosterone effects on women are definitely reversible in women. However, sterility is high and the woman usually has left over physical effects from the test. There are many long term side effects that can occur from abuse of testosterone such as liver disease and a reduction in immunity. She is going for the man look and it is attainable with this. I'm just not sure about the long term aspects  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27}gay..  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/1 & \cellcolor{green!27}100.0 \\  \hline
  \cellcolor{green!5}I am 28. I have always had a problem where I never seemed to develop like other guys. I didn't get a proper jaw line. I could not grow any facial hair. I'm 28 now and it's only just started.  People say it's good to look young. But it makes you feel less of a man especially when lots of 19 year olds have beards and I'm nearly 30 and can't grow a moustache. I just assumed it was good Gene's but I'm at a stage where I just want to look my age.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/94 & \cellcolor{green!5}1.064 \\  \hline
  \cellcolor{green!27}Says the retard monkey with no knowledge of science. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/ here's harvard to prove you wrong. HE was a HE before HE got a sex organ. Gender identity is NOT sex organs it's NOT chromosomes, it's genetically predisposed. No matter what you retarded monkeys say, HE was always a HE. Just because you are too stupid and insecure in your sexuality, doesn't mean you are right lmaoooo  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}Raiden3 Psicological diferences and organic human proof aren't the same as the fucking gender itself, are you telling me that thousands of years from man to woman making empires and succesful civilizations under the banner of a patriarch and not into this degerancy?  That  investigation  rejects any scientific anthropologist investigation and lacks the evidence over the biological diferences between the two sexes.  Im not fucking suprised that only a non thinking imbecile would just see the title of a  harvard  investigation and just post it over there because of the name and not becaude of the content.  Good day.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}Buddy, put up a fucking argument that isn't filled with ad hominem and strawman attacks. No, that is NOT how biology works. You are classified a male because you have male reproductive organs and the body produces testosterone. If you were a fucking female, you'd produce estrogen and have a god damn vagina. These fucks want us to accept them  for who they are  when they can't even accept themselves for whom they were born as. You can't just be a fucking male at birth and 10 years later suddenly become a female, dipshit. I don't care how much estrogen or testosterone you fill yourself with, YOU STILL CARRY THE BIOLOGICAL COMPONENTS OF YOUR BIRTH GENDER. You wait until the fucking revolution comes, we will execute by public hanging each and every one of you transgender pieces of shit.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/139 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}that's what he wanted lol does'nt make any sence i don't care what blah blah saying for me that's good and there's nothing wrong and your brain is wrong so STFU! ya know do your own business lol  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}How is there nothing wrong? I'm not going to change BASIC BIOLOGY simply because of your subjective opinion of yourself. There is something wrong there. Your biological anatomy is that of a female and it will NOT change no matter how many drugs you infest your body with.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}He thinks he's a woman xd  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Why u cover your nip you are basicly a dude now without the P  & \cellcolor{green!27}Nip & \cellcolor{green!27}Japanese & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}Eww disgusting tranny  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}He's transgender, he needs the testosterone.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}This poor young girl has a clear mental disorder, and our fucked up society is too retarded to see or help it. She has two XX chromosomes. This goes down to the dna and mental level. No amount of surgery or injections can change that. Men have XY, Women have XX. This is how you determine sex or gender (same meaning).  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}nope. SEx is sex organs while gender is through identity which is GENETICALLY PREDISPOSED! Meaning HE WAS A HE before the chromosomes were created. Learn your science before you mouth off like an idiot. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/35 & \cellcolor{green!27}2.857 \\  \hline
  \cellcolor{green!5}Hormones aren't a good way to treat gender dysphoria...  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Absolutely not. Physiological counseling is in need. This recognized mental illness should not be normalized. For example... People with schizophrenia or psychosis are given medication to try and regulate their brain chemistry, counseling and other means of treatment are valid ways to mitigate the issues. I understand none of the treatments might not work but that does not make these people  normal ...  Hormones and puberty blockers mean the boy or girl will literally be infertile. If they ever get help down the road or they feel like turning their gender back to fit their sex then they will never be able to have children. There's lots of research out there about gender dysphoria now recognized as gender identity disorder. I would really suggest you read up.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/126 & \cellcolor{green!27}0.794 \\  \hline
  \cellcolor{green!5}counseling  normally doesn't help, especially when they're going through male/female puberty, the effects of their non desired gender are being shoved in their faces. Hormones are a very good way to treat dysphoria, but you are right about possible infertility. Children are normally put on blockers until they're old enough to make a choice about estrogen/testosterone so they have plenty of time to change their minds. Blockers only pause puberty, if they choose to go back to their biological sex they can simply stop the blockers and resume puberty. Most transgender people will freeze their eggs/sperm so if they do change their minds or just feel like having children, they can unfreeze them.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/113 & \cellcolor{green!5}0.885 \\  \hline
  \cellcolor{green!27}You really are uneducated aren't you? There is no mental illness. Identity is predetermined genetically while sex organs can easily mess up. therefore it's really a genetic anomaly when men are born without a penis and the wrong sex organs. Sex organs have no say in a person's gender. the only person that needs psychiatric help you is.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}I am uneducated? You know gender dysphoria IS a recognized mental illness right?   Okay, lets open this up here, NO there aren't any traceable genetics that determine gender. Gender identity is ones personal experience to a gender or genders. It is something that is more or less an understanding of ones self, ultimately a social construct. Genders do exist and you misinforming people on this subject is really what is adding to people not fully understanding what gender is.   People can be born without a penis and still identify as a male. There are syndromes such as klinefelter syndrome that are a good example of a male with female body parts. The chromosome make up is XXY. Fun fact. In ANY variation of chromosomes if there is a Y present the person identifies as a male. Genetic anomalies are a thing, they do happen, and ignorance doesn't make them go away.   The great thing about facts is that whether or not you believe them, they still are a fact.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/169 & \cellcolor{green!5}0.592 \\  \hline
  \cellcolor{green!27}lol, get the fuck outta here you stupid sjw. She was being polite and respectful. Please fucking hang yourself. Nobody needs apes like you in this word. I sincerely mean it. Kys  & \cellcolor{green!27}Nobody & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/32 & \cellcolor{green!27}3.125 \\  \hline
  \cellcolor{green!5}uvuvwevwevwe ossas an ape am I ? boy im more intelligent than you're entire family put together. noone needs a reject like you. sit down boy, You're out of your league.  & \cellcolor{green!5}Ape & \cellcolor{green!5}Black & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}Briggs Guy lmaooo no genetic markers?  go look up harvatds study as just ONE source. also dysphoria is the anxiety and depression that comes with being trans and also from the depression that is caused by idiots like you who think its a mental illness. and yes you ARE uneducated using rejected old theories against modern knowledge  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/57 & \cellcolor{green!27}1.754 \\  \hline
  \cellcolor{green!5}BOT Peter did you not see the scientific proof retard? its the HARVARD LINK. I have a greater education than all of you combined lmaooo  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}Gender dysphoria is a mental illness, but the prescribed treatment is transition. Hormones are actually the best way to treat dysphoria. (Speaking as a trans man).  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}That's why i freaking hate lgbt nazis, a polite person tried to talk and instantly a  :   I'm more informed than all of you apes combined  pops off... Why someone can't simply reply normally? You get triggered so hard that it just shows your enormous life insecurities  & \cellcolor{green!5}LGBT & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}Galactiq Bork i don't get it, you're saying that all the normal children should be put on hormones block until they decide the gender to become? That shit is terrifying  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}This is a serious mental illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}some random non-important person today we have the medical Technology to change genders, just be yourself, change your sex and noone will bother you until you bother someone. Just don't tryhard to get a classification and insult others for not calling you as you want to... i actually saw people saying for example  I'm demisexual but somedays pansexual and one day a month i feel like an agender  aromantic demiguy. Also i want to be referred as them and not his or her, also i prefer to be referred as army because blah, blah, blah... Oh and also i insult everyone that misgenders me  that is why you can't be accepted in society, if someone needs to study 30 pages of gender categories and 10 essays on gender psychology just to say  hello  to you  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/135 & \cellcolor{green!27}0.741 \\  \hline
  \cellcolor{green!5}So whats next then? Every gay person is mentally ill. Every one who is different from the norm is mentally ill?? Go back to your redneck shithouse  & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/27 & \cellcolor{green!5}3.704 \\  \hline
  \cellcolor{green!27}Raiden3 Gender dysphoria is a classified mental disease no matter how much you want to believe it isn't.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}most of the people who go trough a gender change end up killing themself or become unhappy of them self.. this is a mental illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}dilen noris The suicide rate of holocaust survivors were about 3x that much of the general population and those in camps were nearly 30x as much. so about .01  of all people in concentration camps committed suicide. That is enormous, but actually MUCH smaller than trans people.  Trans is comparable to nothing. Which is actually why its favorable to believe that its a severe mental illness that needs to be fixed. And transition (like others claim above) does little to affect the suicide rate.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/84 & \cellcolor{green!27}1.19 \\  \hline
  \cellcolor{green!5}Milo Hemingway Care to show me how that is the prescribed treatment? It wasn't as of 4  years ago. It recently took a huge political shift. I mean ffs the medical industry is extremely political, they don't care if they are killing you (that's why they have no problem prescribing you opiates). Transition has a negligible effect on suicide rates, the only long term study on gender dysphoria has proven this.  A 42  suicide rate? That puts Holocaust suffers to shame. It's obvious a mental illness and we need to find a way to help these people. Transitioning has no significant effect on suicide rates (probably no effect at all), so to assume a course of action that will steralize you for the rest of your life probably isn't smart.  I by no means am saying to not allow them to transition. I think it's fucking retarded, but if you are a grown adult and want to transition, that is your choice. However if you are under 18, you should NEVER be allowed to. I don't give a shit if your parents want it or not. We will not sterilize and disfigure a child when chances are they are going to grow out of it.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/205 & \cellcolor{green!5}0.488 \\  \hline
  \cellcolor{green!27}The UnderBrony Well being gay is not normal, but statistically the effect it has on their life is negligible at best. So there is no reason to  treat  a gay person. They can live their life and no harm will come. Although a trans person having a 42  suicide rate is astonishing and fucking terrifying. Going through gender reassignment surgery and feeling  accepted  within your family or community has no significant effect on the suicide rate according to the only long term study done on gender dysphoria.  All this shows us is something is actually wrong with people who experience this phenomenon. And honestly I think we need to find actual solutions to help these people. Transitioning is an adult's choice, I give zero shits what someone does with their body. HOWEVER, doctors prescribing this as the best course of action with no factual evidence to back this up is disgusting. And so is pushing this onto children (who a great majority of will grow out of this phase).  & \cellcolor{green!27}Zero & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/169 & \cellcolor{green!27}0.592 \\  \hline
  \cellcolor{green!5}You're right. It really is a genetic anomaly when men are born without a penis and the wrong sex organs. This is not the same as transgender. Men (person with XY chromosome) that are born without a penis are NOT the same as  men  (those with XX chromosomes). Oh, and it is a mental illness. The same chemical imbalances in their brains that cause them to want to change their sex are the same chemicals that make 50  of them attempt suicide.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}The UnderBrony everyone who has an actual mental illness is ill  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}Actually they can reduce the anxiety and depression associated with the condition, that being said, it doesn't change the suicide rate of transgender people at all. At least to some studies I've seen. BTW, I'm against all this sjw shit anyway. I just think that people taking hormones is a free choice and if it helps someone's state of mind then I'm ok with it.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/65 & \cellcolor{green!5}1.538 \\  \hline
  \cellcolor{green!27}Hey guys, how about the possibility that someone literally just thinks  fuck! Puberty! I gotta stop it! I don't want body hair, facial hair and male pattern baldness! I'd feel much more comfortable looking like a woman! I want the fat distribution and lack of muscle mass! I wish there was a way to stop this slope towards masculinity!    and then they don't expect anyone to call them a woman or whatever anyways because they realize that  gender  is only meaningful in situations that deal with reproduction.  I don't give a fuck if you call me a man or  a woman because it really doesn't matter. I'm concerned with how I want to look to myself.      This particular thing is heavily similar to people wanting to cut or dye their hair or wear clothes that they feel naturally represent themselves...ibcluding tattoos and piercings.  I would like to feel comfortable going in public in  women clothes  and be able to look in the mirror naked without this sense of  fuck, this sucks .  & \cellcolor{green!27}Fat & \cellcolor{green!27}Physical Features & \cellcolor{green!27}1/172 & \cellcolor{green!27}0.581 \\  \hline
  \cellcolor{green!5}Who the fuck let a child change their own gender? You know your brain isn't fully developed until your 25??!! Stay strong.  I don't blame you. I blame your parents for allowing this.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}Galactiq Bork you realize she's still a child and hasn't fully developed. Don't you think this gender disphoria is just a phase. I mean some kids this girls age are furry or emo!!!  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}Raiden3 You re trying to use  boy  as condescending, while assuming their gender  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}Raiden3 That entire article was just showing the psychological thought behind it and statistics based off of people who identify as those things, it had nothing to do with it not being an illness  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}The UnderBrony idk about gay because they admit they are their gender, they are just attracted to the other gender, but transgenders who think they are the gender they changed to are mentally ill  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}Raiden3 you are just brainwashed biological there is no such thing as gender identity that is made up you have your dna ehat regulates the body decide what gender you are if you have gender dismorphia you should be treated like all other body dismorphia illnesses someone who wants to be blind is also getting normal treatment you cant let self destructive behavior rule  & \cellcolor{green!27}Blind & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5}It s really gender identity DISORDER. Not dysphoria... it s a mental illness.  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}Max Vikings 2 It either used to be gender dyphoria and is now gender identity disorder or the other way around.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}Tyler Padgett yes, the downfall of society will be people expressing themselves the way they want, and not the growing hostilities between every nation everywhere, the rapid mutation rate of bacteria, the steady deterioration of the ozone layer, or the sun inevitably expanding and swallowing the earth.  & \cellcolor{green!5}Nation & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/47 & \cellcolor{green!5}2.128 \\  \hline
  \cellcolor{green!27}you are still a female, dumb fuck  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}no you are the abomination. too retarded to understand basic biology. He was always a man. gender identity is genetically predisposed.He was born in the wrong body is all. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Raiden3 wtf? youre denying basic biology in favor of some girls  feelings . dont call others retard when the retard is you  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}If you are a female accept your fate. This is the way God made you. There is nothing wrong with being a female there are billions of beautiful woman everywhere.  Don't follow in the footsteps of this poor lost soul. A man can never become a woman and a female can never ever become a biological man. So if you are thinking about becoming a man forget about it. This is who you are accept it and be proud of it!  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27}If we play along that there is an all-loving, all-powerful God with an exact plan for everyone he has  created .....then he created this man as a transgender person, destined to transition. I'm certain your God would not approve of you spreading hate instead of love. Benton is a man, and I'm sure he DOES accept it and is proud of it! :)  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/62 & \cellcolor{green!27}1.613 \\  \hline
  \cellcolor{green!5}Swami Vivekananda omg I hate when men say that, the whole  but your so pretty as a girl  makes me want to barf, because most of them are older and I feel concerned and I feel awkward because I don t look like a girl, so sucks for me I guess and also being a girl sucks ass, everyone thinks your easy and that you can easily be taken down and that is why I feel as though most men want women to stay as women, so they have more of a chance. But one god doesn t give a shit what you do, and also if someone wants to transition the can, because its not harming you at all, and it helps the person them self for right in there body. And for me I get mistaken all the time and thats not my fault, so if I were to transition no one would know and so let people do what they want.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/162 & \cellcolor{green!5}0.617 \\  \hline
  \cellcolor{green!27}That was all old testament. I believe in the new one, Jesus is the way the truth and life. And God did not hate man or made them do any of that, it was sin, and God HATES sin  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}So this is a chick?  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}You are a kind of  retard..  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Transgender people are a mistake on humanity  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Yeah, that's why they transition.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}Liz Erich I hope she gets mental help .  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}disgusting insect  & \cellcolor{green!27}Insect & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}bicth  u become a gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}No , gay means being  attracted to the same sex  not changing your fucking gender to the best of ones ability , not the same thing.  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/26 & \cellcolor{green!27}3.846 \\  \hline
  \cellcolor{green!5}ok gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}OK GAY  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}np gay  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Got a vagina?? Ya still a woman, even with it mutilated.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/11 & \cellcolor{green!27}9.091 \\  \hline
  \cellcolor{green!5}Every chromosome in that things body is female. There is nothing male about this creature.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}Hezeldo except he doesn t have the Y chromosome so he is technically still a girl physically. Having a dick or not doesn t decide if you are a man or not. If I cut of my dick and balls it doesn t turn me into a woman.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5}gender and sex are two different things, her sex is female but her gender is now male  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}R s thats true but you dont need to test T to be a man (gender)  if you lift and shave upper lip hair enough thatll make you m gender wise since its only physical charecateurs  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}when mental illnesses go to far  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Unless he undergoes major resection, I assume Benton will retain a clitoris and vagina. The sex he has will then largely depend on who he wants to fuck and who wants to fuck him. Whatever, I wish him the very great happiness in being who he wants to be.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}That s so weird but fucking crazy cool!  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Don t take this the wrong way....but that s fucking weird!!  All I see is a guy.  I can t even fathom that you began as female.  I just....I just see some dude, and I think you re joking, but I know you re not...it s just, fuck....testosterone!!  Hell of a drug!!  Why does it seem that men don t transition as well as you have?  Is it because the testosterone is inhibiting transition?  And this is an honest to goodness question from someone who wants to understand further: do you go shirtless at a beach, as males usually do, or....or for whatever reason you don t?  Anywho, good luck with everything!!  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/104 & \cellcolor{green!27}0.962 \\  \hline
  \cellcolor{green!5} Nice voice, you look like a very attractive guy.  I would never have thought you were a girl.  Many transgender guys have femininity, but you do not.  Bravo! Good luck  -)   & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}XD you look just older version of you XD XD and your body looks as limp as it was XD  & \cellcolor{green!27}Limp & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}Is it gay to say that his really good looking am a guy btw?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}OMG i am a gay guy... but... although I know you were a woman...  god I like you a lot.  You're so handsome!!  Congrats  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}Weird bitch  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}I love your body..... great transition.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}You fucked retard imbeen on t for 20 years  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}This is so fucking weird dude. wth  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}It blows my mind that one can actually change gender!  Gotta love science :)  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}It blows my mind that people  think  one can actually change gender! There is nothing scientific about chopping off ones dick and donating it to a woman to attach to herself!  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/31 & \cellcolor{green!27}3.226 \\  \hline
  \cellcolor{green!5}If you legitimately believe you can switch genders you are seriously delusional. No one on this earth can make a female turn male. Its not possible and never ever ever ever will be.. If you tell me it is than you are telling me that you are able to remove every chromosome from that females body and replace it with a males chromosome. Witch is never going to ever fucking happen you fools.  & \cellcolor{green!5}Witch & \cellcolor{green!5}Female age and physical appearance & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}miaskittens D you can t change a gender no matter what you do. You look a different gender that s all.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}Tennessee Redneck that isn t what even happens though :   & \cellcolor{green!5}Redneck & \cellcolor{green!5}Working class & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Tennessee Redneck You clearly lack understanding of this topic, you don't have a right to comment on it.  & \cellcolor{green!27}Redneck & \cellcolor{green!27}Working class & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}Smonster TIME Sex and gender are not separate. Gender identity is a made up term and the definition of gender was changed for political correctness.  Hell your license says  SEX  yet you can change it in some states with a note from a doctor saying you identify as the opposite gender. Its all become political now and no one gives a shit what the original definitions are. People change them as they wish to fit their political agenda. Its sick and dishonest.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}Nice transition congrats man you look good  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}disgusting woman  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Hey, just wanted to say you're a really cute guy! (Cute in that way guys are, not the way kittens are) Also, how did you tell your parents that you wanted to transition?  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/33 & \cellcolor{green!27}3.03 \\  \hline
  \cellcolor{green!5}Skinny chris evans  & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Features & \cellcolor{green!5}1/3 & \cellcolor{green!5}33.333 \\  \hline
  \cellcolor{green!27}I have to admit that this transition becomes you. Your build as a female was waifish at best, flat at worst and you were kinda lacking in the face department so I guess you've made the right choice.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}Vagina for sure. Periods? She's probably barren for life now. (That's the untold price of changing from one sex to another). But to her credit, she was really masculine as a woman. She had indeed a rather masculine face and a mannish frame so I'm afraid I have to confess she's better looking righ now.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/55 & \cellcolor{green!5}1.818 \\  \hline
  \cellcolor{green!27}maybe you thought she was ugly because the only reason she was trans was due to a confusion of hormones in her body making her look more masculine even before her transition to him. now he's a good looking guy that deserves happiness for all the shit he went through to get here.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/53 & \cellcolor{green!27}1.887 \\  \hline
  \cellcolor{green!5}Gamarleton this person is a freak  & \cellcolor{green!5}Freak & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Gravy Is Nice no she s a she. She will always be a woman because she has XX Chromosomes  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}I feel bad for transgender people  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}Woman fail to realize hgh turns into estrogen. Keep those emotions in check.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}You look great! Medical advancements are amazing! Very proud to be in this day and age!  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}But you still don't have a pecker my friend and your genetics are still that of a woman.  I cannot understand what goes on inside your heads to make you want to cut things off your body or become a fur-ball.  Oh, I get it, you think having hair all over your body makes you a man.  You are going to find out soon enough that having all that hair is not what it is cracked up to be.  Also what made you think at 16 that you wanted to fuque-up the rest of your life while trying to pretend that you are a man when you are not.  Do you have any idea as to the suicide rate among Transgendered people?  Then there are those who want to change back because  CHANGING  was not all it is cracked up to be.  Explain to us how you are going to have sex my friend.  Like a woman?  Also, if you have an implant it will not eve come close to what we men feel when we're having sex !!!  You've have basically ruined the rest of your life because finding a sex partner who is OK with your changes will be few and far between.  Your parents had to have been totally out to lunch to allow you to do this to yourself at that young an age !!!  Go ahead and deletes this comment, I don't care, but I know you will have read it and that is what I wanted to address.  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/254 & \cellcolor{green!27}0.394 \\  \hline
  \cellcolor{green!5}again, crickets, because nobody cares what you think :)  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}You're hairy as fuck dude why have you got so little facial hair when your torso hair is going crazy?!  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}You look super handsome. I'm hoping to transition ftm when I move out of my parents home.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}No but look at her picture as a woman, she had a man's face.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5}As a girl with PCOS, sometimes I've just thought maybe I should transition to a dude. Like, if I can't make children and I already look like a man, I may as well be one. I'd probably make a hotter one anyway. unfortunately I identify as a woman. lol  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27}I am gay and ur so pretty     & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}(This question is not meant to be rude) Why are transgender people so hot? Like, I've seen a lot of videos where transgender people show their story and blah, blah, but I seriously stop and think, how are they even hotter than they were before, like WHat IN THE WORLDDD?  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}NEVER WOULD HAVE EVER THOUGHT you were transgender male!  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}That's a chick..... 0 O  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}I am going to ask a question that most will find irritating. I am a straight vanilla person. My question is why can't a person who feels they have been born into the wrong body, just accept the reality of that without changing it?? It is a beautiful working body regardless of if you do not like it. I am a woman, but if I wanted to do everything as a man, couldn't that just be like a super coulorful expression rather than a need to physically alter my appearance and body parts? There are lots of things I am not happy about with my body and my life, and yes I would trade it for a totally different life and body right now if that were a realistic option. But I just kind of breath through the things I don't like, and find a spiritual center to help me cope with life. I just don't fully understand why that is not an option for those with gender dysmorphia.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/169 & \cellcolor{green!27}0.592 \\  \hline
  \cellcolor{green!5}Julia Skagfjord Because it's a mental disorder and going through a transition is generally the only thing that helps actual transgender people. If they just try to deal with a disorder without getting it fixed, they'll get even more on top of it, like depression.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}That determines sex not gender  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}This is fucking mental  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27}Why are you asking that? His sex does not define his gender  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}If you do have a girlfriend or boyfriend, and want to have sex... what will happen? I am thinking you could use a strap on though! Well not with a guy,,, but ya know  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27}I'm so proud of you! You are so handsome and brave, you are a definition of inspiration that will help so many transgender people! Stay happy! Greeting from Mexico!  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}You are a great example of what a transgender person would want to end up like   perfect  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}Oh shit GENDER WAAAAAAAAAAAAAAAAAAAARRRRRRRRRRRRRRRRRRRRRRRRRRRRRR  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}do u haft to be a certain age to have testosteron  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}I'm 12 and coming out as transgender FTM extremely soon. Any words of advice for comming out to parents?  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}Does he have a girlfriend? And quick question, if I date a transgender man, does that change my sexuality at all..?  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Well it does make you Pansexual. Some people don't like dating people who don't have a simple Gender Sexuality.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/19 & \cellcolor{green!27}5.263 \\  \hline
  \cellcolor{green!5}No it doesn't make you pansexual. Being pansexual means you're attracted to all genders, sexes, and identities. If you're a girl, and you dated a transgender man, you would be straight, because he is a man.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}I see this, and I feel extremely happy for you. But I'm nearly 15, and I am absolutely terrified to come out to my parents as transgender (ftm) and gay. I'm just not sure what I should do. But watching these videos gives me hope that maybe one day I can be who I truely am  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5} Hokibukisa  Hope you made the right choice  there's a heady process of gender therapy and scrutiny by people who are actually knowledgeable in this field before you can get T, I'm pretty sure he wouldn't have been able to even make the choice had he not been 100  sure.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/49 & \cellcolor{green!5}2.041 \\  \hline
  \cellcolor{green!27} Hokibukisa You're assuming that he's gay  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5} Hayden Of Hell I hope so for his sake! The number of women looking for a man with a vagina? Like, zero. If hes gay at least he can be a bottom bitch.  & \cellcolor{green!5}Zero & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27} Hayden Of Hell Love and belonging are a very important part of life fulfillment. That includes sex. Men with really small penises have a tough time in that department due to unsatisfied partners and low self confidence. And if he can't handle plain honest talk like this, oooh man tough times ahead, cause people don't care about your feefees when you're a man. Get ready buddy. But anyways back to love and belonging. Theres no demand for a man with a vagina. And again if he can't handle straight talk like this then hes in for a world of pain.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/100 & \cellcolor{green!27}1.0 \\  \hline
  \cellcolor{green!5} Hokibukisa trust me if he wasn't born with his Gender being incorrect the testosterone wouldn't of worked on him. Some people can form as a baby in many wrong ways. Gender Identity, Arms and legs and also more problems including Brain damage. If you've ever seen weird looking babies on the internet they're probably real except for the Blood and glory images. I'm just saying that the testosterone is made so that it can reform your body into how its meant to be IF you're born with the wrong Gender and sexuality. If he was born with there being nothing wrong with him the testosterone WOULDN'T have worked.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/108 & \cellcolor{green!5}0.926 \\  \hline
  \cellcolor{green!27}Therefor there isn't anyone who wants to turn back time once they've transitioned because not even ONCE do they think that it wasn't the right choice. If a boy just wanted to be a girl for the fact that he liked girls then his body would refuse the testosterone and reject it completely. If you were old enough or understood science more then your comment wouldn't have existed.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/68 & \cellcolor{green!27}1.471 \\  \hline
  \cellcolor{green!5} Dying lmao what u mean fam? Thought he used to be a chick  & \cellcolor{green!5}Chick & \cellcolor{green!5}Gender & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27} Red lol sex and gender are different  & \cellcolor{green!27}Red & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5} Alan Snackbar ahh, if you're transgender, you can still be a boy even if you have a vagina. Sex is what's in your pants, gender is what you identify as.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Let me guess. You're transgender?  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}me too ur dumb  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/4 & \cellcolor{green!5}25.0 \\  \hline
  \cellcolor{green!27} Darien Hurst bro no need to say  IMO  this thing will never be a male, fuck all you punks that expect me and anyone else to refer to this thing as a dude.  you bunch of pansy fucks  & \cellcolor{green!27}Pansy & \cellcolor{green!27}Male homosexuality & \cellcolor{green!27}1/38 & \cellcolor{green!27}2.632 \\  \hline
  \cellcolor{green!5}I want to have a gender doctor. but i have no idea where to find one so i can have testosterone. I really have no idea what it is called in Dutch.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}I used to wanna be a girl but yesterday I was like what do u like about being a girl.....nothing and yet my mom has bought barely any boy clothes and does it hurt doing surgery  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}You don't deserve an Adams apple  & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}..Every sex has an adams apple you nitwit it's our voicebox. It's just more prominent on males.  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}still have hand movement s and gestures like a woman when I look at you I see woman!  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/18 & \cellcolor{green!5}5.556 \\  \hline
  \cellcolor{green!27}is there any age restriction for testosterone shots if so what is it  just like a question  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5}So many uninformed brainless hater's comments here...they think the world is in natural order while nothing in this universe is natural. Everything in this whole world are here because of chemical reactions by coincidence. In 10-20yrs from now, genomic science will produce a pill that can change sexes just by taking it, it's so easy to change genes already, it's the matter of time. Sex is not determined only by XY genomes. Adults Men's testicles can turn to ovaries just by stopping a single gene and women's ovaries to male testicles in same fashion. This is because all animals used to be hermaphrodites--meaning both female/male in a single body. Read science books, ans you will see what you believe is not the real true world. Transgender is nothing unnatural. It's artificial, but so as Justice, Laws, Nations, Religion or Equality.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/140 & \cellcolor{green!5}0.714 \\  \hline
  \cellcolor{green!27}They are abominations, It is not normal it is a mental illness not a struggle.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5} Your friendly drug dealer :D it's actually been recently proven by scientists that transgender people do not have a mental illness  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}Being trans isnt a mental illness or an abomination, if it was they wouldnt allow surgurys like this  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5} Madi H it's still wildly inappropriate. You don't go up to Cis people and ask what's in their pants. I get that it doesn't seem like a big deal, and I respect that opinion. But as a trans guy, I find that question so idiotic, and rude. Like what do you get out of asking that question? Literally nothing. It's privacy thing. I'm sorry.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/64 & \cellcolor{green!5}1.562 \\  \hline
  \cellcolor{green!27} Day But you wouldn't go up to a cis person and ask anyway, because they enjoy the birth equipment they were given.. That was a really dumb statement to make.  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}I support you coming out as lesbian madam, power to you  & \cellcolor{green!5}Lesbian & \cellcolor{green!5}Female homosexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}im 16 and transgender and after knowing my whole life that I'm transgender ( i found out that i wanted to be a boy in kindergarten) i finally desited to come out as transgender like six months ago and are finaly  at the first of my many big steps of becoming a BOY and you're video helps me in my ruff times tank u so much i know u problem not going to read this but just wanted to say it anyways and that with every stages i go true i get happier and happier TANK YOU SOOOO MUTCH aerated sorry for my super bad english I'm from norway hehe  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/110 & \cellcolor{green!27}0.909 \\  \hline
  \cellcolor{green!5}Everyone always asks this question as if transgender people's parts aren't considered private. I'm not trying to speak on behalf of Benton, but perhaps you shouldn't ask about what's in other peoples pants.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27}He is female to male transgender. With that said it is probably uncomfortable for him to show his bare chest without having top surgery(when the breast tissue is removed). Please refrain from using female pronouns when you know very well her is not a woman.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/45 & \cellcolor{green!27}2.222 \\  \hline
  \cellcolor{green!5} Connor Curtis I am Nobody, kill yourself.  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27} Connor Curtis Tits censor   woman  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5} Connor Curtis Let me guess? Nobody cares.  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}No, tranny is offensive. Tran is nothing.  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}Stop getting mad at me saying tran. Transgender people don't like tranny but tran is just a shorter word for it.  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27} Stoner Jesus tranny is short for transgender it's just people say it in a gross way so they mean the same shit.  & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}Tran is not short for tranny...  & \cellcolor{green!5}Tranny & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}tranny     & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}How do you have sex?  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}my Mum and I have been talking about me being transgender for a while. But she's got more and more angry with me about it. She admitted herself in the worst tone possible that she will not support me until I  fully develop  and truly know what its like to be a girl. Then she said you need to find yourself, and that doesn't mean overnight, it takes YEARS! When I've already had years! Now she's saying I have to wait a minimum of 6 years (when I'm a legal adult) before we can start thinking of changing my name etc. Never mind getting surgery. I don't want to live that long as a girl and she just doesn't understand that. My Dad literally laughed in my face and left when I came out to him. I haven't told my brother, or anyone else. I have no idea what they might say. Maybe I just have to wait another 6 years  half my life. I also think I'm bisexual too. They think I got all this nonsense from the internet. This is because they keep on asking the same questions like  Why do you want to be a boy?  and I mean... Who can explain that? I don't want to be transgender, wanting to be the opposite sex is like someone saying they prefer red over green, YOU CAN'T EXPLAIN IT! And they said and keep on saying things like  that sounds like you got that from the internet. WHEN. I. HAVE. NOT. My Mum also said I would make a lovely, beautiful girl, or an ugly boy. I just can't anymore. They also know I'm depressed but act like they don't know and ask me   Why are you acting 2cool4school? . I literally just want to die on the spot. If I tell my friends they will most likely hate me, i even had a conversation about trans people to my friend (as it randomly went into subject) and she said that her Mum hates trans people, and Lulu asked whether I was transsexual or not (I replied with no)and she said,  good, I mean imagine if you were... Please don't be.  If I tell the teachers about it they'll think it as an awkward subject and won't help me. My parents won't do anything until I'm 'fully developed' which will take God knows how long. Although there is a trans FTM in my school who just changed who's in year 10. I really want to ask him about it but I'm afraid he might just think I am a creep because it's too much of a personal thing for him or something and it will be embarrassing and humiliating for both of us. I recently cut my hair to a stereotypical boys length for charity. But that was basically just an excuse to look more like a boy. My parents are now forcing me to grow it out because almost everyone hates my hair now because its not normal for a girl too have it that short, plus I won't be able to get any girl OR boy parts in a musical theatre group I am in. Mainly because I can't have a boy part because I'm not a  boy  and I can't have a girls part because no one will think I'm a girl in the audience while I'm on stage and they'll get confused. I don't know what to do. I hate my life. I don't want to wait because people are already saying things and teasing me in front of me saying things such as  Are you a boy or a girl?  Even though they have known me since the start of the year and know perfectly well that I am a girl (but I don't want to be, so this isn't really much of an issue, as I like being called a boy, I just get scared of how people can be so heartless...) Please help!     Sorry this was such a long message! I am glad and extremely happy that you managed to read this far down, I did not expect it to be so long.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/692 & \cellcolor{green!27}0.145 \\  \hline
  \cellcolor{green!5}omg this brought me to tears look there isnt much we can do to help with your parents but with your school dont be scared to ask your teachers they help 100  I really wish you all the best with your transition remember if your friends judge you then they aren't your true friends do what makes you happy good luck :)  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}Stay as a woman, everything is so easy. As a man, everything is fucking shit hard. They expect me to man up and do shit, but all I want to do is play video games, I rather be born as a female.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5}I don't know what to say Your mother is damn right. You don't onow what this is like. You may regret this decision rate. Tra sgender people have a high suicide rate... Because most of them didn't think this through. Don't do the same thing.  Things feel pretty weird dyring puberty, you should just hold on. Being a tomboy doesn't always mean that you have to be the opposite sex. I know so many girls that used to behave or hang out with boys, but they changed as they grew up.  In short: Don't do anything yet. Wait and decide this later. Focus on more important things like studies and stay close to your family.  & \cellcolor{green!5}Tomboy & \cellcolor{green!5}Female homosexuality & \cellcolor{green!5}1/115 & \cellcolor{green!5}0.87 \\  \hline
  \cellcolor{green!27}Children don't always know what they will want in the future with regards to random things but they know who they are. Gender identity is evident since childhood, and feelings of not being cis are almost always traced back to childhood. This is your issue of ignorance-and their parent's. I'm 23 and without going into it too much I am not cisgender, once I knew I could trace this feeling in memories and even in writing through my journals back to when I was a child.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/86 & \cellcolor{green!27}1.163 \\  \hline
  \cellcolor{green!5} RDB ///Gender identity is evident since childhood///  Actually, no it's not. It is extremely common for kids to go through identity crises of all kinds, including gender. That is unsurprising when you consider the tidal wave of growth and sex hormones that flood the body during childhood and puberty. It is a normal and natural part of growing up. It is a mistake not to give herself the opportunity to naturally resolve the crisis by simply growing out of it. That may not happen, but in most cases, that is exactly what does happen. Her dysphoria may simply evaporate as she grows into an adult and her hormones stabilise.  It is important to remember that reassignment is not a cure. The young man in the video is extremely convincing, he should be able to live his life exactly as he chooses for the most part. But while he may look like a man, his biology will never be male and that will always be there for him. Reassignment may help for many, but it is not a cure.  & \cellcolor{green!5}Common & \cellcolor{green!5}Working class & \cellcolor{green!5}1/178 & \cellcolor{green!5}0.562 \\  \hline
  \cellcolor{green!27}In my personal opinion I really do think you should let nature take its course and actually let your body develop the way it was suppose to be. What is wrong with being a tom boy or a masculine thing. I'm pretty sure that everyone on the face of this earth hates their body to some degree but, it is your job to appreciate what life has given you, realize that other peoples opinions do not matter. Its your reality not anyone else's. I feel like you might think that this change will just fix everything in your life and boom you're happy forever. What if you get this change and then realize that it doesn't actually change who you are. Like im just saying if you get the change and then realize that you were wrong. Life will be a lot harder. Im so glad I didnt grow up in this age.  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/153 & \cellcolor{green!27}0.654 \\  \hline
  \cellcolor{green!5} Not a cure  well firstly that's off to the person transitioning. Perhaps some of them will never be fully fully happy with their internal organs but for most transitioning alleviates dysphoria and feelings of suicide and self-harm tendencies. Not every single transgender individual is happy after or during and some realize it's not for them-but it NEEDS to be up to the person themselves whether they want to do this because no one can speak for them and transitioning has changed so many people's lives for the better. I suggest you not assume but look at the people who can self report on this. https://www.reddit.com/r/asktransgender/comments/32hvk7/are you happier after transition/ https://www.quora.com/Are-most-people-who-undergo-a-gender-transition-happier-after-transition-than-before-it I think happiness is pretty convincing I also think that in a perfectly accepting world there would be less pressure to transition as long as other knew who you were-but in this society transgendered individuals are forced to live a double life unless they can pass. I get how it's confusing for people because identity crisis is a part of being a teenager. But even with people who transition late their stories go back to feelings of dysphoria evident since very very young. Some children do grow out of it-so my beef with your argument is your implication it can't be a cure (and the possible implication that they can be converted back?). I think that while we need a balanced approach and I actually generally agree with what your saying (you do seem to have a bias in assuming that's what WILL happen though and I think that at this point it's safe to say he's clearly not growing out of it) when figuring this out-using these arguments to force children to undergo bodily changes they clearly loathe is very unethical. For many kids who-say-grow out of a tomboy phase they will just go through their normal puberty. If someone is going through puberty and viscerally wants it paused they need to be listened to, they need to be given time to think about it before irreversible changes happen. Because if they're forced to go through those changes and then are left with just trying to reverse what happened, that will still make them feel better but they will not as easily pass-which will open them up to harassment and stigma from and leave them with a body that's not as fully male/female as they wanted it to be.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/396 & \cellcolor{green!5}0.253 \\  \hline
  \cellcolor{green!27}RDB /// Not a cure  well firstly that's off to the person transitioning.///  People often dont want to hear the truth, nevertheless there it is. You can choose whether or not to be offended by it.   To expand on the 'cure' statement, it really rather depends on the nature of the problem. If the issue is one of simply being unhappy with your appearance, then transitioning can be a cure. But I suspect that is almost never the case and if it's only appearance that is the issue, then your issues are probably not deep enough to warrant irreversible surgery and hormones. If you truly believe you are the wrong sex, then transitioning will not 'cure' you, because you can only change your appearance, you cannot change your sex. The young man in the video very definitely looks male, he will pass as a man 100  of the time. But at the risk of stating the obvious, he is not actually male and never will be. It can never be more than a masquerade. That might be enough for some, but I wouldn't be shocked if it falls short of expectations for most.  I'm sure that many who transition state they are happier. But happiness is relative. Being happier that you were when you were suicidal, is progress but it may not be the great leap forward you might have been hoping for. You know when people make a big investment into something, it is human nature for them to evangelise about the wisdom of their investment. They are not necessarily the best people to ask for impartial advice. In long term studies, it's interesting to note that pre and post transition suicide rates, remain unchanged. Transitioning might help to some extent, but it isn't a cure and it's going to leave you with a whole bunch of new problems to deal with, such as sexuality to name an obvious one. Is the young man in the video going to date men or women? Is he going to confine his dating to the LGBT community, or will he date straight men or women? If he dates a woman, will that make him straight, or gay? Will he care? Maybe not, but will she? Will he be honest about his trans status at the start of the relationship? Will he date gay men? Would that make him straight or gay? Will his partner care that the guy he's having sex with, used to be (or still is?) female? This is a hell of a lot to expect anyone to rationalise, let alone a young child.  I take your point about an early transition producing better physical results, but there is way more at stake here than that. The parents, guardians and doctors have a duty of care to this young girl and if they get any of it wrong, they have abused their position and the child. The only thing to lose by waiting, is the physical results may not be quite so convincing. But given the vast array and complexities of the psychological issues, then without any doubt we/they/ everyone should err on the side of caution and wait until the individual is capable of making mature, competent, well balanced decisions ...and taking all the responsibility for the consequences of getting it wrong.  ///and I think that at this point it's safe to say he's clearly not growing out of it///  But he could come to regret it. It's not unheard of. That is the problem, if he does then couldn't he reasonably turn to the adults who had responsibility for him and say  how the hell could they let me do it, I was just a child? .  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/617 & \cellcolor{green!27}0.162 \\  \hline
  \cellcolor{green!5} I don't know what to say You might have born with a male brain and that's completely normal and okay. Don't you ever let anyone tell you who you are. It doesn't matter if you're not 18 to become a transgender because your brain already is! that's why you are depressed: because you're oppressing yourself into something you're not just to please other people.  Once you understand that it is YOUR life, you'll know what to do. Fuck the haters!  This obviously applies to everyone who's feeling the same way.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/90 & \cellcolor{green!5}1.111 \\  \hline
  \cellcolor{green!27}There probaly partly worried that it might not be the right choice. sure its glorified in the media at the moment but I've read stories of people who regetted it later on down in life. especially male to female. I was always under the impression that it was partly an obsessive disorder because of the way a person can obsess over wearing the opposite genders clothes and everything to do with the other gender.   I guess one day if they somehow prove that people can be born in the wrong body, then it will be accepted but I think its a hard one to fully accept just because someone feels a certain way. There are some people who think they are cats or babies etc there life revolves around that so whos to say wanting to change gender isn't the same sort of problem? I think its important to understand the psychology behind the feelings of why you want to change gender before actually going through with any changes in oppose to watching a bunch of people in the media and youtube celebrate their change.   Maybe one day they'll have hard evidence that a brain can be born in the wrong body but for now its not.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/207 & \cellcolor{green!27}0.483 \\  \hline
  \cellcolor{green!5} Ghost 572 that is exactly the point. In all the case records of pre-pubescent gender dysphoria, 75  of them come to accept their biological sex if allowed to progress through puberty naturally. Being unhappy with your physical body is really very common among teenagers. That doesn't mean there is a physical illness. It's also important to remember that taking puberty blockers and sex hormones, damages a perfectly healthy body. It's also important to consider that the pressure from trans-activists to have gender dysphoria declassified as a mental illness, is socio-political in origin. It isn't rooted in science, because there isn't any ...or precious little. It's not the same as bringing pressure on society to accept homosexuality, even though it is often compared to it. There are distinct differences and distinctly different claims with profoundly different consequences. Gender dysphoria has nothing to do with sexuality and accepting someone is gay, does not require that we give body-damaging puberty blockers, surgery and carcinogenic sex hormones to children. There needs to be a substantial body of evidence to be sure we are doing the right thing - and we dont have it yet. The trans activists and pressure groups have an intrinsic bias. Obviously they want their condition to be accepted as biological rather than psychological, but we need to be extremely cautious before accepting the  I'll kill myself if you dont let me transition  guilt trip that is often applied to parents, guardians and the medical community.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/245 & \cellcolor{green!5}0.408 \\  \hline
  \cellcolor{green!27}Ghost572 I know there's no hard evidence about that. You have an interesting theory, it's just that for me is even harder to believe that this is about an obsession like those cases where people fully know themselves or those very little children that identify with their opposite gender but not with theirs since they were born. I heard many times that we do have differences in our brains according to gender, it might have something to do with the genetics field. I hope some research is being made about this matter.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/92 & \cellcolor{green!27}1.087 \\  \hline
  \cellcolor{green!5}RDB suicide rates are the same before and after transition. the problem IS NOT the gender. its the brain.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27}I don't know what to say omg we have so much in common, like no joke I can totally relate to you. I told my dad and sister but I'm scared to tell my mum because she's that type that says oh what did you read or watch this time. I'm scared to socially transition because I'm scared about the way people would react to me, especially cutting my hair. I also have a ftm in my school but I'm scared to talk to him because it's weird to bring it up as he's like a year younger and also it's quite rude  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5} alexander202 Can I ask, have you thought about your future relationships? I mean as a ftm, are you going to go for gay men in the hope they will overlook your female genetics? Or would you go for straight women, in the hope they will also overlook your female genetics? Do you plan to trick them by not telling them? Or are you going to be honest upfront and risk being lonely?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/72 & \cellcolor{green!5}1.389 \\  \hline
  \cellcolor{green!27} alexander 202 OK, so how do you think a straight woman would feel, knowing that you used to be female and in fact still have 100  female genetics even after surgery/hormones? You see, even though you might feel male, biologically you are not and never will be. Do you not think someone who considers themselves to be straight female, might feel challenged by that? At what point is 'before going serious'? Is that before holding hands? Before the first kiss? Or before sex? Do you not think that any level of romance under such circumstances, might cause someone to feel revulsion and create a sense of self-loathing? You see, while you might have come to terms with being you, but nobody else is required to. I can tell you as a straight male, I would only consider genetic females for partners. I cant help that. We don't choose our sexuality and we are not in control of who we are attracted to. That is the same for straight or gay, male or female. Gay people want same-sex partners, straight people want opposite-sex partners and while gender is fluid, sex is not. For most of the population, transgender partners are not an option. That is the reality.  It is possible that you could 'pass' (deceive someone) long enough for someone to have feelings for you before dropping the bomb. But to hope that they wont be revolted or angered by the deception, is a lot to ask, don't you think? If you are not upfront from the very start, you will suffer an awful lot of painful and angry rejections. If you are upfront from the beginning, you will most likely be taking yourself 'off the menu' and wont get the dates.  Have you thought about this?  I appreciate that gender is not the same as sexuality, but a decision to transition will have significant and lifelong implications for it. As someone who is sexually immature, do you think you posses the sexual maturity to make those decisions?  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/337 & \cellcolor{green!27}0.297 \\  \hline
  \cellcolor{green!5}Martyntd5 yes I know where your coming from and it's tough, it really is knowing that your not the real deal and that's what troubles almost every transgender out their. But, we've come to this era where we can change our biological sex, it's possible. In 2011 they managed to change a female mice's ovaries into testes and produce the average amount of testosterone as a regular male mice by just turning on (or off I forgot) one gene. Imagine in 10 years time we can completely change and manipulate the sex where we can in the future be full male one day and the next female. We all take gender for granted, like we were given that gender for a reason and we can't do nothing about it. I know it will be hard to find someone who accepts you. But that's not the only big thing that goes on in your life, what about work, vacations, parties and all these different activities, it's not all just about sex and whether if I have the right genitalia. Life isn't all fixated on that, and people now a days need to understand that, that the whole we live in is more capable at making our dreams come true. But honestly I don't know how my life will be on 5 or 10 years time, I guess I'll just have to wait and find out.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/234 & \cellcolor{green!5}0.427 \\  \hline
  \cellcolor{green!27}ZG9 I know this is an old comment but give yourself some time and just do what your mom wants until you're old enough to earn your own money. I always have been a tomboy and even had such irregular periods that I thought that I didn't even know what it's like to be an  actual girl . However, as I got older, I realise that you don't have to exclusively act girly to be feminine. I'm still not stereotypically feminine but I'm sure now that I'm a woman regardless. If it were up to me to make a decision when I was younger, I probably would have wanted to be a boy. Don't rush into things and give yourself some time to think and mature.  & \cellcolor{green!27}Tomboy & \cellcolor{green!27}Female homosexuality & \cellcolor{green!27}1/125 & \cellcolor{green!27}0.8 \\  \hline
  \cellcolor{green!5}i think  on my modest opinion  that your parents are right,listen to them it's a REALLY HUGE BIG DEAL to change your part of your identity (gender   name) in a such young age as you as you say    i want to be  the oppsite sex but you didn't think about what you really  need to be  that is important.  some people have a serious mental illness that is called gender dysophira(search about it) and who have it will never be good untill they be transgender they  need  this to be good,to be normal,to have normal life and normal brain so after all of this do really have a SERIOUS mental illness that you can't live or act normal untill you change your gender? or it just a feel that you have inside you? feelings is a not a strong reason to do it as most of the youtubers do it because they just feel that they are not that person who they really are that's another issue that will not been recovered by transitioning after 6 years if you still have this issue then go ahead no one will judge you but now it's just puberty and hormones that missing around our brains in some periods be strong and hold on i wish i didn't upset you with my opinion and wish you luck  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/226 & \cellcolor{green!5}0.442 \\  \hline
  \cellcolor{green!27}https://youtu.be/jDIrnp2iNJU watch this it's about de-transition and people in your age that go back to their original gender after trans  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}I would wait till you're 18. Your mother is right, quite a lot of people have transitioned and want to turn back which is extremely problematic. I fully support people that are coming out and transitioning but doing so at such an early age is again, very, problematic.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}When I was 4 years old, I wanted to be a boy. But my mother would not let me cut it short. I used to have it cut to as short as a typical girl's haircut could go: at the chin. I was persistent at first, but my mother still did not let up. So I had no choice, I gave up and decided to grow it long. Eventually, I started to like my longer hair and came to appreciate my femininity more and more as I grew older. I lost the desire to become a boy and just accepted my physical gender as a girl. If my mother had let me cut my hair short, I wonder if I would identify as male now.  I know that this is the wrong youtube page to be posting this kind of story, but I just had the urge to share and maybe let someone who felt like becoming the opposite gender at some point in their life, but ended up deciding to remain their physical gender, know that they are not alone.   Not everyone who has the desire to be the opposite gender at some point will neccesarily follow through with their wish.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/202 & \cellcolor{green!27}0.495 \\  \hline
  \cellcolor{green!5}ZG9 you were born a girl, god created you that way. If you change your self, then u would be saying that god makes mistakes which he doesn t. You shouldn t chang your gender, but Change how people look at you, tall your parents taht u need there help and tell your friends that your a girl  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/56 & \cellcolor{green!5}1.786 \\  \hline
  \cellcolor{green!27}Get your mental health issue addressed.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5} Your friendly drug dealer :D  He was biologically a girl but identifies as a guy. It's that simple. You can go ahead and think he's still a girl if you'd like but not many trans people like to be reminded of their biological gender, so I suggest you consider that he chooses to identify as a guy and respect his views.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27}I hang out with a bunch of guys in gym and I'm from half a foot to a foot shorter than all of them, and it's common to talk about stuff like body hair so naturally, they were curious about my leg hair. It upset me so much because I have so little leg hair.  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5} Isiaih N Neela he changed from girl with no chest hair to a girl with chest hair adams apple and no penis lmao  & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}it is still a girl u fucking idiot dosent matter if they change how they look or change gender parts they still a women and fucked in the head  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5} Jared Moulden no its you faggot I would knock you out for being a absolute bitch  & \cellcolor{green!5}Faggot & \cellcolor{green!5}Male homosexuality & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Isiaih N Neela u cant change gender u will always be what you were born to be just accept it!!  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}daum yall guys got no respect for trans ppl  trans ppl  change because they dont feel comfortable being a boy or girl  also do some research, you can get surgery to get the opposite sex body parts.  in conclusion, yall thought bye bye now :3  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/45 & \cellcolor{green!5}2.222 \\  \hline
  \cellcolor{green!27}I wouldn't be gay, i mean he got a vagina....  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}YOU ARE STILL A WOMAN!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! you will never be male no matter what you do !!!!!!!!!!!!!!!!!  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Yes, female to male transition... as the title to the video states.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5} Ad S (. .) it's kinda weird lol, the laws of trans are still in development  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27} Kamina Lancer unless his gender marker on his birth cirtificate says male hes not alowed to show nipples  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}Descrimination of any kind is terrible, but nipple discrimination is just plain crazy!  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}Dumb feminist...  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/2 & \cellcolor{green!27}50.0 \\  \hline
  \cellcolor{green!5}That's feminism ya dumb fuck LOL  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27} Youreraisingmyphoenix females have more rights then men anyways  a man gets hit?  No one gives a shit   a woman gets hit?  Call the fucken cops     a man gets raped or molested?  who cares   a woman gets raped or molested?  its a big fucken deal    and when i say im for equal rights, i am not a feminist simply as i am against the name being just as  Fem    all genders deserve equal rights  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/73 & \cellcolor{green!27}1.37 \\  \hline
  \cellcolor{green!5} Ad S He's a transgender fucking dumbass  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27}Been following your videos, and I must say hats off and respect for your FTM journey, it must be quite tough juggling your mood swings when u r on T. Being a dude, I envy how deep your voice is (deeper than mine LOL) however curious to know what sort of Test are you on: C, E or mixed which brings back to wonder about the slow facial hair growth process which makes me realise perhaps it's gotta do with genetics, ie. does any male members of your family experienced the same thing? Being aware of the negative side effects of T ranging from severe mood swings (roid rage) to severe acne breakout from what i've seen. Thanks for making such great videos, you are an inspiration to the LGBT world. All the best for your continuing journey.. :)  & \cellcolor{green!27}LGBT & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/139 & \cellcolor{green!27}0.719 \\  \hline
  \cellcolor{green!5}    okay so I'm gay and I get upset because most if not all transgender men are straight. Lmao. YOU ALL ARE GORGEOUS        if I met a full transgender man that liked men as well, I would definitely go out with them and probably marry them lol.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}Your still a woman. Sticking feathers up your arse doesnt make you a chicken  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/14 & \cellcolor{green!27}7.143 \\  \hline
  \cellcolor{green!5} MavrikPastelBaby   Transgenders have psychiatric delusions. You are promoting a mental illness  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}Yes, but admit it, if you didn't know him and he was was sitting next to you in a bus, would you know that he's transgender?... Mission accomplished.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}It's not a comparison. You said he's a woman. Well okay. But if he didn't tell anyone but the people he's close with then nobody would know. As long as he's productive(job, school, pays taxes) contributes to society like anyone else,  then I don't see a problem :)  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27} TLeh  Most transgenders end up killing themselves anyway because of their mental illness. They are a scourge and a problem in society. We need to help these people  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}actually it's been proven that transgenders have ZERO psychiatric problems besides depression and anxiety from the bullying you retarded monkeys place on them for not getting basic biology. Gender identity is genetically predisposed. Go argue with harvard. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/  & \cellcolor{green!5}Zero & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27}no they end up killing themselves because retards like you bully them into suicide. They are actually smarter and in better mental health than you because unlike you, they are grounded in science and factual evidence.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}i want to do a strange question do dont take it in a bad way, and sorry for my english im acually not english,so... he currently has a cunt, so can he has a sexual intercourse( so do sex) with a male..but, he is transgender, then he is attracted to females .. so would he feel pleasure in having sex with a transgender woman, so with a penis? or not .. I know the question is strange, but I'd like to understand that he is attracted to women,then a lesbian transgender would she feel pleasure in having sex with him? taking pleasure in the sense of attraction, not physical pleasure .. strange question but I hope someone can answer me  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/120 & \cellcolor{green!5}0.833 \\  \hline
  \cellcolor{green!27}lesbian not transgender    & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/4 & \cellcolor{green!27}25.0 \\  \hline
  \cellcolor{green!5}This is my first time on your channel, the first very video I've watched of your channel. And I can already say I'm in love you. You are such a great person. I literally have no words, thank you..for changing a lot of people's perspectives on transgender people.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}Dude, I'm just wondering why you had to blur your nipples in the shirtless pictures? Is youtube really that dumb, you just feel comfortable doing that, or are you just being safe so your video doesn't get taken down (which would be incredibly stupid)?  & \cellcolor{green!27}Dumb & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/44 & \cellcolor{green!27}2.273 \\  \hline
  \cellcolor{green!5}Because SOMEBODY out there would get their knickers in a knot over him showing some nip.  & \cellcolor{green!5}Nip & \cellcolor{green!5}Japanese & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27} christine xo   You calling me ugly doesnt change my multiple high quality hot hot partners who would also view you as disgusting :D Two can play that game,faggot  & \cellcolor{green!27}Faggot & \cellcolor{green!27}Male homosexuality & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}aww, looooook, a chad trying to prove how alpha male he is! someone who thinks that dick size actually matters and uses faggot as an insult? didn't know we were in middle school again, how fun.  & \cellcolor{green!5}Faggot & \cellcolor{green!5}Male homosexuality & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}awwww look at him with with his fragile masculinity. i bet he doesn't even wipe his ass because it would be gay to touch your butt lmaoooooo  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}MRDESTRUCTION26 what s more disgusting is black guys on the DL fucking little twink boys and giving them HIV and lying about their sexuality  That s disgusting  So take your black ass outta here  & \cellcolor{green!5}Black & \cellcolor{green!5}Black & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}I'm a gay man and can I just say- he's totes bangable  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5} So  he's  a female or male?     you just answered your own question he's a transgender male meaning he has girl parts but he was transformed into a male from when he was once a female.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27}wow I would never thought that you was a women you just ma men for me thats crazy im so happy that transgender have that now for help them in there transition thats woderful  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}Whoever does this has some serious mental issues    & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27} cody C still a girl/ woman to me  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}the weird thing is that i don't use testosterone yet! But i have adam's aapple since i was a small little girl..., well, it got more clearer when i had puberty  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}No one get triggered alright but this is impressive when a person is born a different  gender it is damn near impossible to transform  completely without there being small tells in a persons looks or features. This guy is blowing my mind, I've never seen such a complete and flawless transition from one gender to another  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/56 & \cellcolor{green!27}1.786 \\  \hline
  \cellcolor{green!5}She either doesn't have a dick or there's some weird contraption down there  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}Hey Benton, I have a few questions. I am 11 and transgender FTM just like you are. All my life I have felt different and when I found out about what transgender is, I knew immediately I was. I'm scared to come out and tell everyone I am transgender. I told a few close friends, and they both ditched me and stopped being my friends because of it. I'm scared of what my parents and my class will say, or even if they will let me go to school anymore. And if they will accept me because all my life I acted or pretended like a stereotypical girl all day every day. It would be awesome if you reply, might even change my life, Thank You! : )  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/128 & \cellcolor{green!27}0.781 \\  \hline
  \cellcolor{green!5}he's now a male so this is what i've got to not confuse you guys lmao his sex   female his gender   male  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}what's the difference between sex and gender?  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}sex   what you really are, he's a female, and you can't change that. however, you can change ur gender. sry 4 bad english  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27} some dude No. But if you post your transgender story, from a girl to a boy, you can ask this.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5} Nanashi x3 uh, no. if a trans person talks about their hormone transition, which has literally nothing to do with genitals or genital surgery, then that doesn't give you a free pass to ask about their junk.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/36 & \cellcolor{green!5}2.778 \\  \hline
  \cellcolor{green!27} ilovefishful If you're transgender. MTF  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5} ilovefishful What's your problem with a transgender person? or to be  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27} ilovefishful OMG. Because he doesn't want to be a woman anymore. A transgender person doesn't feel like his biological body.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5} ilovefishful you obviously don't know the first thing about gender dysphoria dude. do some basic research about a subject before you make presumptuous and offensive comments about it.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/28 & \cellcolor{green!5}3.571 \\  \hline
  \cellcolor{green!27}YOU'RE HOT. I think I've fallen in love with a transgender male lol! I would honestly have never known! testosterone is fuckin awesome  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}so thats mean you are a girl in the past and now youre a man WTF that is so weird you are so handsome im a man doe well yea the end is near  -   & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/35 & \cellcolor{green!5}2.857 \\  \hline
  \cellcolor{green!27}I'm a 12 year old year GIRL I'm size 9 men shoe and I'm 5'3 but size and shape SIZE  NOT MATTER  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}Its a mega personal question, but does anything change in sexual pleasure?  & \cellcolor{green!5}Sexual & \cellcolor{green!5}Gender & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}THIS IS SO CRAZY, OMG  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}So this is the first video I've seen on this channel and I honestly would have never guessed he was transgender. I thought the video would be about someone else tbh  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27}The Computer/internet/technology is completely unnatural, and I can speak for my self, and I believe that many also come from the same place, but this unnatural technology is serious messing with our brains, it is all artificial stimulation, we are addicted to artificial technology, maybe you havent noticed it yet, but it is the truth, can you go one hour without logging on to the computer or checking your phone? to answer your question, I use the computer because i am addicted to it, and thats not a good thing. And if this was natural, than tell me, has anything like this happened at all is history? Nothing like this was even possible even less then 100 years ago. lets not be in denial, Lets be objective, its im not stating an opinion, but injecting testosterone into the blood stream is NOT natural, that is why in the body building community, someone that takes steroids (steroids is synthetic testosterone) is said about him that  he is not a natural body builder  that is a term that is commonly used. Its scary that the masses are accepting the unnatural as natural, just shows how easily things can be skewed. Very dangerous. Please dont think im stating an oppion, because I am not. this is common knowledge.  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/215 & \cellcolor{green!27}0.465 \\  \hline
  \cellcolor{green!5} G Moula Yes but having testosterone in your body IS natural, and he is replicating the normal levels in a male body. Also, transgender people have existed for centuries. I agree with you on the tech addiction though.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/38 & \cellcolor{green!5}2.632 \\  \hline
  \cellcolor{green!27} Drybowser8 The only natural testosterone is the testosterone that your own hormones produce. It is no longer natural when it comes from a lab, packaged, then injected into the bloodstream. Am I crazy for saying that's not natural? If a body builder were to do the same, he would be disqualified from any  natural  body building contests, and would not be classed as a  natural  body builder.  & \cellcolor{green!27}Crazy & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/67 & \cellcolor{green!27}1.493 \\  \hline
  \cellcolor{green!5}Id say its astonishing but not really scary Like He is not going to turn into a psycho and Murder everyone  & \cellcolor{green!5}Psycho & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}how about the adam apple?  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}I agree but YouTube would take down the video. On my other channel I uploaded a video of my changes and I didn't blur out my  boobs  and YouTube contacted me saying since I was  a woman  (not true) they took it down  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27} Anon Sings You are a woman, and you always will be. Can't change chromosomes. Sorry.  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5} stylinsondoge So conforming to male stereo types instead automatically makes her a guy? That's not how it works in society. Guy   penis, woman   vagina.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}GOD made you a woman, not a man. So here's my questions, you don't like the creation of God?  God created us all perfectly. Changing from a woman to a man, doesn't it meant that you hate God's creation? God is perfect  everything he created in this world is perfect. Yeah, whats done ,is done. But I want you to think about this. Do you Love GOD?, If you love him ,then why did you change what GOD created as your body?- maybe your answer would be, we have a choice, or we are not perfect.  yeah we have a choice, but the morality of that choice is too ugly in the eyes of GOD. Its not too late, I am not forcing you anything, what I have is only an Advice   read the Bible   be happy ,how,   what GOD created you to be. Not only for you, but share this to your friends, neighbors,   family. Thank you for your time,   GOD Bless     ..... 3    God's Messenger    & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/174 & \cellcolor{green!27}0.575 \\  \hline
  \cellcolor{green!5}This woman is cancer to society  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27} Brittany Kirkland only take T if you are beginning your transition. Not just to stop your menstrual.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5} Brysen Sheetz I already started testosterone three months ago, I'm feeling much happier. I been transgender since I was 7 but my parents didn't understand what it was or why I was calling myself a boy and asking for boy clothing and accessories and toys,  so they didn't let me go on puberty blockers, so I went through girl puberty when I was 14, I didn't like It one bit, I started feeling suicidal at 15, but I didn't know what transgender was or why I didn't feel comfortable in my body, time went by and my mother got even depressed crying all the time because she wanted a girl not another boy(im the only girl) she wasn't thinking about my feelings just her own she didn't believe in transgender people because our religion so she wouldn't let me talk to a counselor or get any help, at 16 I found out that I was transgender but I was to afraid to tell her due to she might throw me out of the house so I waited until I got a good paying job, I'm 24 now and I finally got my own place and started my transition, I didn't know life could feel so good until now, I feeling a little more like myself now.    & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/217 & \cellcolor{green!5}0.461 \\  \hline
  \cellcolor{green!27} Brysen Sheetz ikr same hear I hate my birth name is so girly so I changed my name on my birth certificate when I was 19 and told everyone that my name is Britt all these years I been trying to get Them to call me Britt but They still prefer Brittany and everyone in my family keeps calling me Brittany, it really makes me depressed and uncomfortable, so I'm going to try to stay away from my family for awhile until they get my name right. Plus they don't believe in transgender people, so they keep telling me to Stop transition. That's another reason I have to stay away from my family.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/113 & \cellcolor{green!27}0.885 \\  \hline
  \cellcolor{green!5}I personally started with hormone suppression and that cuts off your period and then I started testosterone, much smoother transition id say  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/22 & \cellcolor{green!5}4.545 \\  \hline
  \cellcolor{green!27}Perks of starting testosterone when you're still a teenager lol. You look awesome! Great voice change and great (and desirable) adam's apple. In Mexico you have to wait till you're 18 to start  HRT and I think I don't know anyone who had hormone blockers. Canada is fucking awesome and so are you! Thank you for sharing your changes and story.  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/61 & \cellcolor{green!27}1.639 \\  \hline
  \cellcolor{green!5}What the hell is your problem. He has a youtube channel that lets everyone know hes transgender, so everyone knows it.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27}You're hot...congrats on your transition though  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/6 & \cellcolor{green!27}16.667 \\  \hline
  \cellcolor{green!5}Can you back to woman? That's my big question.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Wait, so you are around 18 years old, and you have ALREADY TAKEN HORMONES TOWARD GENDER TRANSFORMATION??? Kinda young to make such big decisions.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}I've personally known more trans 16-19 year olds that have killed themselves over dysphoria than have started their transition.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/19 & \cellcolor{green!5}5.263 \\  \hline
  \cellcolor{green!27} larry I regret she is a ugly woman tell her to take off her pantie  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5}This makes me SO MUCH more confident in my future transition. Thank you for this video!!  33  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}(         ) how much expense on transition process  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5} Kristian Wasdin Well you are meant to be what sex God made you for a reason. This unholy form of  being who you are  is propagated by the Devil.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27} CCTB  weird if true,cause you're too much of the negative stereotype of a religion person.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/15 & \cellcolor{green!27}6.667 \\  \hline
  \cellcolor{green!5} Tommy Scott dannng you just roasted an entire gender  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/9 & \cellcolor{green!5}11.111 \\  \hline
  \cellcolor{green!27}Autumn Apple There are only 2 genders  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/7 & \cellcolor{green!27}14.286 \\  \hline
  \cellcolor{green!5}And this is how you make men gay.  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27} Mick D fuck you he's a guy not a girl go fuck urself  & \cellcolor{green!27}Mick & \cellcolor{green!27}Roman Catholic & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5} Mick D He don't need a penis to be a guy.  & \cellcolor{green!5}Mick & \cellcolor{green!5}Roman Catholic & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}Adam G   Nothing effective ( I'm a licensed surgeon) . She's a mentally ill lesbian who's surgically altering her body to make her appear more masculine as a coping mechanism.  & \cellcolor{green!27}Lesbian & \cellcolor{green!27}Female homosexuality & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}Depends man, some cases, very rare but still happens, 0.01   of the population face a mutation called gender dysphoria where a female brain forms in a male body or vice versa. I don't believe in the whole gender fluid transgender craze either, but some folks legit have this mutation.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/50 & \cellcolor{green!5}2.0 \\  \hline
  \cellcolor{green!27}Playing devil's advocate here bro, they say that the fact that gender is a social construct, and is different from sex which is a biological construct. They believe gender is separate and is not fixed to chromosomes and sex. Some even go as far and say that the traditional male female structure of genders are merely social constructs.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/58 & \cellcolor{green!27}1.724 \\  \hline
  \cellcolor{green!5}That's what they mean, the role in society is a social construct. The argument is that we should do away with the gender binary since it is a social construct and biology is something separate entirely from what someone wants to identify as. This, combined with the gender fluid idea is something I am sceptical about. The scientific and medical findings for this is dubious to say the least.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/69 & \cellcolor{green!5}1.449 \\  \hline
  \cellcolor{green!27}Well that's the thing, it's a mental illness that they are suffering from. Gender fluidity is very different from being transgender, it's just nonsense.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/24 & \cellcolor{green!27}4.167 \\  \hline
  \cellcolor{green!5}You mean Gender IS binary, NON BINARY would mean gender fluid as there is more than two.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/17 & \cellcolor{green!5}5.882 \\  \hline
  \cellcolor{green!27}wow! i know it's beside the point but i would have never thought you used to be a woman. love your voice!  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}That One Dude If  she  is transgender shouldn't you refer to her/him with he?  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Omg! I would have never guessed you were transgender! handsome at that!!  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}Gpod Joe girl by definition is someone with vag and ovaries and therefore ability to bear children. It aint defined by the brain. The reason its not defined by brain is cause anyone could feel like anything. Its like people that think theyre a king from a different century. Imagination is very powerful. Your brain changes all the time but your sex doesnt. One just needs to deal with it or seek psychiatric help.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}Covalite Hey you can say whatever you want but if you have a vagina you are a girl and the same with penis for boys and thats it. Transgender people have a  mental disorder , go and search you will see.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/40 & \cellcolor{green!27}2.5 \\  \hline
  \cellcolor{green!5}Lmao it s not a  genetic anomaly  that made him look like a female. It s basic biology. He has two X chromosome, and therefore is female. Because he doesn t  feel  like a female, that doesn t mean it s an  anomaly . That s just a transgender person s way of thinking, that they shouldn t be male/female. But they are. No science as of today can change that.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/62 & \cellcolor{green!5}1.613 \\  \hline
  \cellcolor{green!27}quido lol...you have the mental disorder it's called intollerance.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}sandy xx it actually is a mental disorder, go look it up before commenting something stupid  & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}What was my so called stupid comment...where did i say it wasnt a mental disorder?  How about you read the comments properly before you comment some crap!  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/27 & \cellcolor{green!27}3.704 \\  \hline
  \cellcolor{green!5}sandy xx  lol... you have the mental disorder it's called intollerance   & \cellcolor{green!5}Mental & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}I still dont see where I said it wsn't a mental disorder.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}Guido haha, she has xx chromosome so shes a girl  & \cellcolor{green!5}Guido & \cellcolor{green!5}Italian & \cellcolor{green!5}1/10 & \cellcolor{green!5}10.0 \\  \hline
  \cellcolor{green!27}Oh my you are so gorgeous. Oh my. No idea what your sexual orientation is but you are going to make a girl or guy very happy one day!  & \cellcolor{green!27}Sexual & \cellcolor{green!27}Gender & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}lol the last video I watched was over a year ago, its great to see the transition, so much hope  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/20 & \cellcolor{green!5}5.0 \\  \hline
  \cellcolor{green!27}You really should not ask questions like this. It's disrespectful to intrude someone's privacy that way. I understand your  curious but it's rude. Some guys do not ever get surgery for a penis and some do. Some never get boobs removed and some do. It depends on the person but never ask someone about it unless your in a relationship with them or plan on having sex lol. Any other time it's not your business. Hope this helps.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5}Omg.. Your transition looks really amazing so far! I literally thought  oh is this a boy taking T to change to a girl  then was like  wait the title says female to male  I'm so happy for you!   wishing for the best for you  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/44 & \cellcolor{green!5}2.273 \\  \hline
  \cellcolor{green!27}Can I ask u something? I don't mean to be offensive. How does the gender exchange surgery work for transmen?. I mean Can a transgender man have a penis?.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5} Brittany Hammington Where did you get your information? That's nothing like what they do to make the penis. There's multiple surgeries anyways, and I haven't seen an end result that would qualify as weird looking. They look like penises to me.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27} James Petersen They never asked if he had a penis or not. If you look at the question, they asked if it's possible for a transgender man to get/have a penis. They were asking about bottom surgery, nothing more, nothing less.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5}Just renoticed this thread from a notification, btw people, yes they do pull out the clitoris. It's not like there's a penis inside of women, I know that. They also use some skin from the person's thigh or arm to shape the new penis. And it's all a matter of opinion, but I've seen a ton of dicks thanks to the internet and I've seen some ftm bottom surgeries as well on the internet and they do look kinda weird. At least to me. Thanks for being so condescending.. I'm just some 'chick' so I'll shut up I guess.  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/99 & \cellcolor{green!5}1.01 \\  \hline
  \cellcolor{green!27}Because he was a girl,you see,a girl produces way less testosterone than a man,so,of course the hormonal receptors of the hair folicules will react way more erasier to more testosterone since they used toreact for way smaller doses of testosterone,that's why you have a man like me who can atract even animal with his pheromones,and have sex over 6 times a day and yet,I don't have a lot of hair,it's all thanks to genes in a way,and the heterosomes since those designate genders,kinda,they should usually,but....you know....transgender people are a thing.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/90 & \cellcolor{green!27}1.111 \\  \hline
  \cellcolor{green!5}I understand your confusion in this, they are not changing from a man to a woman or vise versa. Gender is how you identify as, he is a guy but was born with a female body, So by changing his body from female to male (ftm) he is helping himself with a lot of struggles such as gender dysphoria or body dysphoria.  The gender you identify as in your brain could be different from the sex of your body.  I hope this helped.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}Erm, actually, you can. You mean male to female, which are sexes. You can change gender  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5}True but these retards cant get that in their head cuz their too fucking dumb  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}actually HE was never a woman to begin with. he just had the BODY of one. Body isn't identity because gender is based on identity which is genetically predisposed like being straight or gay. Aaand that's how you destroy the uneducated in 5.4.3.2..  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}wise up? child stfu, noone is CHANGING their gender. their gender didn't match their sex organs to begin with. their sex organs ARE NOT their gender. gender is identity and genetically predisposed. You're a thousand years too early to debate me. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}they aren't CHANGING Gender. they are changing sex organs. their identity NEVER matched their sex organs. Jesus you are stupid. if you have a vagina that just means you have a vagina. gender is through identity and that's genetics. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/  You're a million years too early dude. stfd  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/48 & \cellcolor{green!27}2.083 \\  \hline
  \cellcolor{green!5}Raiden3 so I guess whenever I feel like it I can say  my gender is female  and enter a women's toilet? This whole PC bullshit is ridiculous and disGUISting  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}Raiden3 are you retarded or something you cant change gender deal with it idiot why am I even replying to you Autistic af  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5}Zevox made up science?  retard every scientist agrees with me. he was born with the wrong sex organs idiot. go back to basic biology  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/24 & \cellcolor{green!5}4.167 \\  \hline
  \cellcolor{green!27}Zevox he was always a man genetically.  the fact that his sex organs didn't match is WHY he's trans but in terms of genetic coding he was always a he  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/30 & \cellcolor{green!27}3.333 \\  \hline
  \cellcolor{green!5}Zevox ive already shown you one harvard article retard. you're too early to debate me  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27} WindBastard  he isn't changing gender retard. he was always a he genetically. gender does NOT equal sex organs.  basic biology  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/20 & \cellcolor{green!27}5.0 \\  \hline
  \cellcolor{green!5}Raiden1 lol she's not biologically or genetically a mind, there is nothing about her that makes her a man other then the fact that she felt like being a man, which is all in her brain,  that's why this is a mental illness.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}Zevox actually retard its been proven by EVERYONE that its not a mental illness its genetic.  he shares the same genes as every other male in terms of identity which btw is ALL genetic coding.  and you got owned idiot. take the loss  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}Raiden3 hahahaah what a retard omg you really don't know shit about biology  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}Raiden3 I got 'owned'? Lol if she shares the same genes as all men then why does she have a pussy, unable to produce sperm and has to take unnatural testosterone injections to appear more manly?  & \cellcolor{green!27}pussy & \cellcolor{green!27}Chinese & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}says the retard bitch boy with no actual science to back up his retarded claims lmaooo. http://sitn.hms.harvard.edu/flash/2016/gender-lines-science-transgender-identity/ go argue with science boy.  you're a thousand years too early to argue with me  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}Raiden3 i dont need a degree to see or understand that a transformation has ocurred. Sex is fixed, gender identity is not. Thats obvious, but that should not give rise to the transformation of ones body. Its the luck of the draw. Be happy youre healthy.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/46 & \cellcolor{green!27}2.174 \\  \hline
  \cellcolor{green!5}gender identity is fixed. Identity is genetically predisposed. that's the point. transgender men are born in a women's body but their identity never changed from male.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27}GamerCringeTV I'm not a big believer in medication - period. If it does more positive than negative and is a necessity I believe it should be used in conservative manner. However in this case I feel like this is a choice of the individual whether to transition or not and it is therefore a luxury not a necessity - similar to plastic surgery.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/63 & \cellcolor{green!27}1.587 \\  \hline
  \cellcolor{green!5}Ana Luna  your 100  correct we don't have the advance techonolgy to turn a biological woman into a biological man but he sure looks like one. I don't mind referring him and a  he .  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/34 & \cellcolor{green!5}2.941 \\  \hline
  \cellcolor{green!27} WindBastard  You clearly didn't go to biology class if you didn't learn the difference between gender and sex.  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5} WindBastard  you are a very pathetic excuse for a person. Of course anyone can change gender and it's people like you that taint the world with your crap. How would you feel if you felt constantly uncomfortable within your own body? Your mind is obviously so closed with no understanding at all.  You clearly have no understanding of autism either and your words are disgustingly offensive to those that are. Go and get an education and empathy, you don't seem to know anything!!!  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/83 & \cellcolor{green!5}1.205 \\  \hline
  \cellcolor{green!27}Terrance Harris Well , everyone loves a freak show , don't they? That's why we all watching this.Yeah.  & \cellcolor{green!27}Freak & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/18 & \cellcolor{green!27}5.556 \\  \hline
  \cellcolor{green!5}Ddrsdd D but nobody likes a child molester and heroin addict like you tho!  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/14 & \cellcolor{green!5}7.143 \\  \hline
  \cellcolor{green!27}Dr Gr nental If you're born female , you will die female.Simple as that - you can't change person's sex. If you are chromosome xx - you're female , if you're xy - you're male.This can't be changed. Chopping bits off and adding bits on doesn't change a thing. If they dig up your bones in 1000 years , they would be able to tell what sex you were.You can pump yourself with artificial hormones - they will just mask your true gender. Doctors are just using all these transsexuals to conduct their experiments on them - they're willing participants , so why not?  & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality & \cellcolor{green!27}1/103 & \cellcolor{green!27}0.971 \\  \hline
  \cellcolor{green!5}Zach Stachelski shut the fuck up. He's right. His sex is still female...  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27} Zevox well that's because you're retarded boy. A man can be born with a woman's body. it's because their sex organs are created independently of their Identity. Genetics prove this. you really are pathetic. you're a million years too early lmaoo  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/41 & \cellcolor{green!27}2.439 \\  \hline
  \cellcolor{green!5} ddrsdd d  A person's identity is predisposed before birth. While a sex organ is just another  limb  if you will call it that. Identity is correct, while the  limb or appendage  can very well be incorrect because of genetic anamolly. If you identify as femalem you're chromosomes have not say, but the genetic markers for identity have a say.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/58 & \cellcolor{green!5}1.724 \\  \hline
  \cellcolor{green!27}says the bitch boy who can't understand basic boy. you're the triggered retard here. I'm far superior, twerp. Sex isn't identity.....boy  & \cellcolor{green!27}Twerp & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}are you retarded? if your genetic markers make you identify as a woman, then that is your gender. you're sex organs have literally nothing to do with it. you uneducated pompous bitch.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}says the little boy with no educated. keep running your mouth retard. Everyone else whose educated knows how idiotic you sound. you're an ant boy. keep crawling away.  & \cellcolor{green!27}Retard & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/28 & \cellcolor{green!27}3.571 \\  \hline
  \cellcolor{green!5}No, we you start getting hair loss...you reduce the testoserone dosage....its not a male precaution...haha  Why because your diet also affects your hormones and level of activity etc.  As we age, a lot changes....including sensitivity or lack of to hormones....so I wouldn't blame it all on testosterone nor would I give it all the credit..look at the males in your family and see how their natural testosterone works for them.  And as you as and increase level of activity or not...your feet will grow again....so it's not all hormones.  So what can we do for feet....sleep once a week or twice in the recumbant position (only your legs...keep your back flat as normal)..that means with your knees elevated...and perhaps a bolster underneath your knees or a pillow...  Next stretch your feet out...everyday or several times per week or your clogging honey man..or man honey...that means your toes are not getting exercised nor relaxed because you dont stretch them out....  Where comfortable sneaker with arch support if you need it...walking around flat footed all day is not good for posture..etc...  Do rub down your feet with a little Suave Advance Therapy....something that is water soluble and will hydrate your skin...and perhaps so some very low impact aerobic....why....you don't want to ruin your joints...everything in your body takes a joint and articulation...so if you're not working out you are not engaging your circulation and if you over do it you can ruin your joint....and well winter is on the way....hormones are very temperamental and come with a threshold...I think during the summer you reduce the load and during winter you get off the hormones temporarily...something like that...  You also dont want to assume men dont have any hips....men have hips...they just wear larger fitting clothes...there are all kinds of mens in the world...and hormones work intermittently so why are you on them full time...all that you may need to address your local congress and our national congress...hormones are considered enzyme catalysts...that means they are short lived and live for seconds at a time and the body only requires a minute quantity rarely if its going to be and continue to be sensitive to hormones...same idea with insulin but with insulin we get the food factor and what you ate...blah, blah..so we can't compare them...  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/382 & \cellcolor{green!5}0.262 \\  \hline
  \cellcolor{green!27}I was doing some research because I recently have made friends with a transgender guy and I have never met anyone like that so i was doing some research about it and I'm so happy I found this video  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/39 & \cellcolor{green!27}2.564 \\  \hline
  \cellcolor{green!5}Nigga wat  & \cellcolor{green!5}Nigga & \cellcolor{green!5}Black & \cellcolor{green!5}1/2 & \cellcolor{green!5}50.0 \\  \hline
  \cellcolor{green!27}Ive seen so many transgender ppl that dont really look like they were a certain gender! But oh boy oh boy not like u! Ur the ONLY trans that i say 100  u dont look like u were a girl and u were true with true voice and not tryina fake it! Love it! x  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/55 & \cellcolor{green!27}1.818 \\  \hline
  \cellcolor{green!5}I understand great transition is there long term side effects to the heart from taking testosterone alot body builders I grew up passed away taking testosterone wondering if you factored the possibility atherosclerosis  at age 50 but I admire that in your gut you knew this was right went with your decision...  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}If your taking under a doctors supervision then there is very little to worry about unless you could get something That runs in your family. As far as your bodybuilder buds they passed away because a cis man(born with man body) taking testosterone is stupid and dangerous. The body turns Testosterone back into estrogen once the T levels have gotten to high. Idk much about HOW it would kill them but I hope this helped.  & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality & \cellcolor{green!27}1/75 & \cellcolor{green!27}1.333 \\  \hline
  \cellcolor{green!5}how to not be gay trans 1) if u trans female-male just be girlfriends with male-female 2) if u trans male-female just be boyfriends with female-male  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/26 & \cellcolor{green!5}3.846 \\  \hline
  \cellcolor{green!27} Cassidy and the Alters No, she is just a confused girl on hormone drugs. Nothing else.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/16 & \cellcolor{green!27}6.25 \\  \hline
  \cellcolor{green!5} Kevin Andersson If God assigned it to him, why did he also give him body dysmorphia, ie, the desire to change genders and look like a man. Why would God make some people attracted to the same sex if it's wrong? Why would God even care what we do with our bodies, as long as we are being good people? Why would God care that this person decided to take testosterone to become stronger and look like a man, seeing as it doesn't really change his moral character. I don't know, it sounds like you're speaking for God. Maybe this is just what you think, and perhaps God would prefer you to let people overcome the hurdles he has put into their lives without making it all the more difficult. After all, it is THEIR life, and being rude to transgender people doesn't make YOU a better person, Mr. Andersson.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/150 & \cellcolor{green!5}0.667 \\  \hline
  \cellcolor{green!27} Michelle Kawaii  Not Yet, i am studying to be a Doctor.  Science is ever changing , we didn't know the effects of silicone injections would have, or that cigarettes cause a number of health issues. We are still learning we are still discovering, WE as a humans can never stop solving or discovering , all is flex on this planet and nothing stays still. that's the same with studies, there is a reason we do many studies frequently.  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/78 & \cellcolor{green!27}1.282 \\  \hline
  \cellcolor{green!5} brandnewstance12  you're studying to be a doctor and you don't know about or have compassion for transgender people? i find that a bit disturbing actually.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}You look amazing ! It's ridiculous. I can see a huge difference from your pictures. Did your Adam's apple just appear?  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}Omg your Adam's Apple    & \cellcolor{green!5}Apple & \cellcolor{green!5}Native-American & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27}i think it's much easier for ftm then mtf. i would have never guessed you're trans if I saw you on the street. an the Adams apple is amazing...didn't know that happens from hormones.. and of course -the voice. anyway,happy for you :-)  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}I was LEGITIMATELY 100  shocked when I realized you're an FTM. Like, I straight up yelled  HOLD UP. NO WAY.  I mean, I've seen tons and tons of transitions but never this good. You do not look or sound like a woman even the slightest bit. If I passed you on the street without knowing, I wouldn't even have guessed. Like, at all. Congratulations, though, I'm happy things are going well for you. :)  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27}Great, now your a woman that looks like a dude  & \cellcolor{green!27}Woman & \cellcolor{green!27}Gender & \cellcolor{green!27}1/10 & \cellcolor{green!27}10.0 \\  \hline
  \cellcolor{green!5}Why would that matter? He doesn't want to show his nipples, why would that be something weird? Top surgery or not  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/21 & \cellcolor{green!5}4.762 \\  \hline
  \cellcolor{green!27} nnelliess I never said it was weird, it isn't weird, I was just genuinely curious. I didn't mean to offend anyone. I just thought an aspect of having top surgery was so that you an go shirtless and not have to worry.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/42 & \cellcolor{green!27}2.381 \\  \hline
  \cellcolor{green!5} nnelliess I completely 100  agree! I being a woman personally wish that I could go shirtless in public/online without judgement like men are able to. Again I 1000  agree with you, I hope you can see where I was coming from though.  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}In Michigan, my son has to go through specific criteria in order for him to take hormone blockers and T.  He's almost 15 and must see a therapist to determine whether or not he can emotionally handle the changes etc.  Did you take hormone blockers before T or didn't you need that?    Without uploads here, I would probably a little unprepared for F2M transition.  My knowledge is from M2F trans women, except for the effects of medication on emotions.   I can't wait to see my son bloom into the body he was supposed to have. I'm legally changing his name. As a mom, I can't thank you enough for progress pics etc. so I can prepare him for all the changes with T.    HUGS       & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/125 & \cellcolor{green!27}0.8 \\  \hline
  \cellcolor{green!5} Nicole G. I'm glad people like you and your son exist. My parents seem to have a hard time accepting my gender as more than just a phase, I wish it were easier.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/33 & \cellcolor{green!5}3.03 \\  \hline
  \cellcolor{green!27} Adrian D. I'm so sorry. Remember, your parents have to grieve the loss of the  old gender  you. To be honest my son's dad still hopes this isn't a phase he wakes up from and regrets it. That concern is from a place of love. He doesn't want his child to suffer through the changes and have it be a massive mistake that can't be undone. He wants to protect his child from pain out of love. He has to learn his SON didn't make this decision on a whim.  He remembers the Daddy-Daughter dances, the little girl who twirled around in dresses I made,  his first-born baby girl he held minutes after birth--giving her her first bottle feeding.   And yes, there are the closed-minded parents that say,  God doesn't make mistakes.   My reply always is,  Then why are there handicapped/disabled children in the world?  If He can create those children for a reason, who is to say what God has in store for transgender children?   & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/166 & \cellcolor{green!27}0.602 \\  \hline
  \cellcolor{green!5} Nicole G.  Thank you for your words. I understand it's difficult for my parents since they can't imagine what having gender dysphoria feels like and I can't blame them for that, but I do blame them for seeming to not acknowledge my tries to explain myself and simply my feelings. I hope it'll all get better eventually.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27} Adrian D. I hope so too. My son cries every time he has a menstrual cycle because it reminds him his body isn't right. In Michigan, most doctors won't prescribe T for anyone under 18 and must have a  letter written in a specific way from a therapist stating they're emotionally ready. It helps fight against malpractice. Unfortunately, none of this helps my son. I can feel his emotional anguish. It breaks my heart every time and I fight that much harder for him.   One day, perhaps if you have children, you'll realize you're just as strong for them as you are right now. And they will be better for it.    & \cellcolor{green!27}doctors & \cellcolor{green!27}Nationality & \cellcolor{green!27}1/112 & \cellcolor{green!27}0.893 \\  \hline
  \cellcolor{green!5} Nicole G. this is late but i just read this comment, and im about to turn 16. I'm on blockers right now. and if the therapist thinks the person is ready you can get T at 16. 16 is the youngest age you can get T in Michigan not 18 lol  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/51 & \cellcolor{green!5}1.961 \\  \hline
  \cellcolor{green!27} MACHETEtv Duran Where?  We're having trouble finding a doctor in our area (Kalamazoo) that will prescribe to my 15 yr old son.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5} MACHETEtv Duran That's way far from us. I've contacted the Lurie Children's Hospital in Chicago. I know they've had children as young as 11 yrs old on hormones. (Not sure which gender specific hormones they were on, estrogen or T.)  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/40 & \cellcolor{green!5}2.5 \\  \hline
  \cellcolor{green!27} Adrian D. Therapy is a great start!  It has helped everyone, including me, in our house. If your parents think you're the problem, they're wrong. They have to realize they're also the problem.  Take advantage of therapy   stay open-minded and honest with your therapist.  Don't be discouraged if they aren't a good fit. You may want a therapist that understands gender issues--or at least is LGBTQ friendly.  Hang in there.    & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/72 & \cellcolor{green!27}1.389 \\  \hline
  \cellcolor{green!5}It's people like you that restore my faith in the human race. So sorry to hear all that your son goes through. People should prescribe with parents consent, not a therapists.  & \cellcolor{green!5}Race & \cellcolor{green!5}Ethnicity & \cellcolor{green!5}1/31 & \cellcolor{green!5}3.226 \\  \hline
  \cellcolor{green!27} ExterminateKilljoys I think it's a regulation in Michigan to see a therapist. His therapist has recommended testosterone, but finding a doc willing to take that risk with a teen in a sue-happy world is difficult. He's going to Lurie Children's hospital to their gender services clinic at the end of January.  Thanks for the compliment!  I only wish other parents would be as supportive.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/64 & \cellcolor{green!27}1.562 \\  \hline
  \cellcolor{green!5} Nicole G. Hi, Im 28 years old, been mostly in the closet about F2M my entire life, as in I can remember being confused about my gender as young as the age of 6, but it wasn't something anyone ever talked about when I was a kid, and it's certainly not something I can expose the majority of my family to.Just wanted to say keep fighting! Youre amazing! If I had Parents like you, things would have been different! I have a son now, 12 years old, and from the day he was born, the only thing I wanted him to feel was love, and to teach him to love others regardless of what some people may label as  abnormal.  I always tell him, If someone is truly happy, so long as they're not hurting anyone, then let them be! Also shout out from Michigan!  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/145 & \cellcolor{green!5}0.69 \\  \hline
  \cellcolor{green!27} Aly M Hi!  Yes, I started telling/explaining to them around age 7 or 8 what gay meant, the difference between cross-dressing and transgender, how calling someone  tranny, fag, dyke  was just as bad as calling someone  retard  or the n word. The dialogue continued from there. I think I always knew my eldest was different from the 3rd grade which is why I stressed at an early age, everyone should be treated with the same respect no matter how different and I'd love them no matter what.  Next week my son's dad and I are taking him to Lurie children's hospital in their gender issues dept to try and get hormones for him.   I'm from the Kalamazoo area!  As some advice for you--my favorite quote:   It's never too late to be who you might have been.     & \cellcolor{green!27}Tranny & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/137 & \cellcolor{green!27}0.73 \\  \hline
  \cellcolor{green!5} Nicole G. I can tell :) you would get a long so well with my mother. right now she's looking for other people with transgender kids to talk to actually.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/30 & \cellcolor{green!5}3.333 \\  \hline
  \cellcolor{green!27}Bangy Habby   If she say  son  means that her son have vagina,not a penis. A transgender son, is an AFAB. And, trans females arent  castrated . They domt loose any part of their genitals, genius.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/34 & \cellcolor{green!27}2.941 \\  \hline
  \cellcolor{green!5}Jonasz Koran-Mekka  But you click on this video. Retard right agenda  & \cellcolor{green!5}Retard & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/11 & \cellcolor{green!5}9.091 \\  \hline
  \cellcolor{green!27}It showed up in my recommended, i have nothing to this video, only to the mother supporting her childe through body mutilation  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}Jonasz Koran-Mekka  I am a religious person, i pray every night and do fasting for many weeks. And i do have a relationship with my Gods. How i am disgusting? I didnt rape, kill or harm anyone. I do not harm myself for being transgender. I do not change me for vanity.  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}Meness  Yes, tjey die young for being deny their own gender identity.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/12 & \cellcolor{green!27}8.333 \\  \hline
  \cellcolor{green!5}luke tyson13  I though the one who is destroying humanity is corruption, and nuclear wars, and radiation. Not a person who identifies with other gender  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/25 & \cellcolor{green!5}4.0 \\  \hline
  \cellcolor{green!27}14 years old and you are considering to allow your CHILD to tak e hormone blockers?! You are a disgustingly dangerous parent.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}as a child of an unsupportive and abusive parent, to read a comment about a mother (especially a mother) who wants to learn about a transition from the pov of an actual transgender man, so that she can be educated on the subject for her child, it makes me so happy to see this. it's a great reminder that there are always open-minded people hiding in plain sight and that there is hope.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/73 & \cellcolor{green!5}1.37 \\  \hline
  \cellcolor{green!27}the mother is not making the choice for him. the teenager has come out to her, and she's allowing him to avoid many mental sufferings that come with keeping your child from going through with this decision when they're 100  they know what they are and what they want. transgender people seem different after transitioning because they dont feel the need anymore to act like they are the gender everyone says they are. theyre more confident if their personality traits or physical behaviors dont stem from issues with the way others have perceived their identity. you dont suddenly know what you want only when youre an adult, you know what you want based on what you experience. like, for example, you know you dont want to touch a burning stove, because if you burned yourself before, you know it hurts. you had an experience that taught you somewhat what you want. but of course, gender identity may change in some people, because some people turn out to have a more complex identity than just trans female or trans male. but this boy? doesnt sound like he's confused, as he's already gotten quite far. trust me, you'll regret it much more if you waste your childhood feeling wrong just so that you can make someone else certain the choice is right.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/220 & \cellcolor{green!27}0.455 \\  \hline
  \cellcolor{green!5}I truly believe that one shouldn't make any decisions before the end of puberty as this is when hormones act a lot and the gender dysphoria might disappear. Otherwise it's a matter of the specifics of the case and  personal choice  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/41 & \cellcolor{green!5}2.439 \\  \hline
  \cellcolor{green!27}This is disgusting, making your child go through genital mutilation and your children's mental issue will only WORSEN as they get older eventually leading to depression or even suicide. There is no such thing as a happy transgender, they may put on a smile but they are dying on the inside. What you should do is make your kid go to therapy to get over their crazy mindset and in a year or two when they do eventually get over it (hopefully) they will be a MUCH happier human being and thank God that they didn't go through a irreversible surgery that would ruin their social life. Any parent who makes their child go through this and they think they are helping, just know your doing the OPPOSITE, society might tell you your doing the right thing, but when is society ever right? like 10  of the time maybe? Yeah..  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/150 & \cellcolor{green!27}0.667 \\  \hline
  \cellcolor{green!5}Kitterz  that's stupid two genders only, you cannot change gender or sex.  & \cellcolor{green!5}Sex & \cellcolor{green!5}Gender & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}No disrespect, but you really need to think this through. Your child is probably going through a phase of puberty, which is very common at the age. Why are you just giving him what he wants?  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/36 & \cellcolor{green!27}2.778 \\  \hline
  \cellcolor{green!5}Kitterz  hi, you are one of the most positive example of supportive parents  i ever saw.  3 i m very happy that u support your  son, i wish my parents would do the same. I'm 16, and a ftm transgender. Whenever i try ti express my feeling out to my parents they reject it and say it s phase. I hate it so much and it makes me very angry , depressed and sad. I often have suicide thoughts because i realise, in my country there is no hope for transgender people. They are being  considered alot of negative things and they see our problem as a  mental disability so they treat us like we are sick . :/ . Idk how i m gonna keep this up. I have no family to support me , and that matter s the most to me. Idk...  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/145 & \cellcolor{green!5}0.69 \\  \hline
  \cellcolor{green!27}what a horrible mother promoting and supporting mental illness  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/9 & \cellcolor{green!27}11.111 \\  \hline
  \cellcolor{green!5}Had never really thought about female to male transition - I guess because it's less talked-about. Kind of amazing to think that you can take something and become stronger, taller, more powerful.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/32 & \cellcolor{green!5}3.125 \\  \hline
  \cellcolor{green!27}Gods Knowledge is infinite and so is his abilities, DONT compare him to a human, because he CAN and he DOES, determine the gender of every baby including yourself, what he is able to do is outside of what the human can imagine. If he knows every star by name, what makes you think he doesn't determine the gender of all of mankind. ALL WORK IS EASY WORK FOR GOD.  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/70 & \cellcolor{green!27}1.429 \\  \hline
  \cellcolor{green!5} Heidi Kim I have nothing to worry about, I have everlasting life, which you so easily could also have through Jesus(considering its free), and how do you know your heart won't fail you tonight, do you think people dying right now, expected it?.... NO  you better get ready before its too late.  & \cellcolor{green!5}Nothing & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/52 & \cellcolor{green!5}1.923 \\  \hline
  \cellcolor{green!27}Your face is very manful, voice is exellent! Youre Adam's apple... it's shining like a Sun, man, it's really good results!  & \cellcolor{green!27}Apple & \cellcolor{green!27}Native-American & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}The human body is amazing...and weird....but amazing.  & \cellcolor{green!5}Weird & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/7 & \cellcolor{green!5}14.286 \\  \hline
  \cellcolor{green!27} Galeno Delmar But  still, isn't it kind of fascinating how a change in hormones can evoke completely different secondary sex characteristics?  & \cellcolor{green!27}Sex & \cellcolor{green!27}Gender & \cellcolor{green!27}1/21 & \cellcolor{green!27}4.762 \\  \hline
  \cellcolor{green!5}Correct! However in order to transition it requires a hormone replacement, a modern invention. Hm.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/15 & \cellcolor{green!5}6.667 \\  \hline
  \cellcolor{green!27}Piece Of Garbish Why the fuck would you care if some complete stranger wants to change their gender. It's their thing and they'll be happy for the rest of their life, rather than question their identities. Humanity will never learn how disgusting hatred is. Individuals will, but humanity won't  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5}Don'tWatchTheWorldBURN the hormone is natural but high  amount woman is not safe and should be banned  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/16 & \cellcolor{green!5}6.25 \\  \hline
  \cellcolor{green!27}Nothing fucking human about this  & \cellcolor{green!27}Nothing & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}Basically wipe out 98  of humanity and then have nobody to reproduce?  & \cellcolor{green!5}Nobody & \cellcolor{green!5}Youngsters & \cellcolor{green!5}1/12 & \cellcolor{green!5}8.333 \\  \hline
  \cellcolor{green!27}You're so handsome... I hope my transition goes well... but I'm short o.o  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/13 & \cellcolor{green!27}7.692 \\  \hline
  \cellcolor{green!5}Wow you're stunning... I'm gay, btw  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}y r u not gay this pains me  & \cellcolor{green!27}Gay & \cellcolor{green!27}Sexual Identity & \cellcolor{green!27}1/8 & \cellcolor{green!27}12.5 \\  \hline
  \cellcolor{green!5}So awesome to see how much you've changed! And these videos must be really important for people who are just beginning their transition!  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/23 & \cellcolor{green!5}4.348 \\  \hline
  \cellcolor{green!27}I only found you a few days ago on instagram and would've never thought about you being transgender so applause to your physical changing! :))  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/25 & \cellcolor{green!27}4.0 \\  \hline
  \cellcolor{green!5}I can't find the song at the end and its driving me crazy  & \cellcolor{green!5}Crazy & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}Your voice will get a little higher again, most is mental and emotional not many physical, it depends how long you were on it though also. If it was for a long time there would be a lot to think about because most guys who have been on it for years have had their woman organs removed so they will have no hormones at all causing a lot of emotional issues. But if it was for a few months not much. The hair stays once it's there though. Hope this helps.  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/91 & \cellcolor{green!27}1.099 \\  \hline
  \cellcolor{green!5}Hey my name is Lane c: I'm transgender ftm, and I'm starting up my channel it would mean a lot if anyone reading this could go check it out  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/29 & \cellcolor{green!5}3.448 \\  \hline
  \cellcolor{green!27}and yet you are still a girl... I'm not trying to be rude but common sense your a girl... instead of turning to testosterone you should have turned for help... what was it that happened to you that made you think you are a boy/could become a boy... sometimes reality isn't sweet but we all got to hear it  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}You look great, and I'm very happy for you. I've been watching your videos for a long time now and it's cool to see how far you've come. Knowing your story gives me hope that things really can get better. Hopefully one day I can fully transition too.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/48 & \cellcolor{green!5}2.083 \\  \hline
  \cellcolor{green!27}why did yo blurr your nips on the thumbnail? You're a guy (which shouldn't have any impact but I'm pretty sure YouTube has gender specific policies regarding women's nips).  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/29 & \cellcolor{green!27}3.448 \\  \hline
  \cellcolor{green!5}wait  i am confused he was  a woman?  & \cellcolor{green!5}Woman & \cellcolor{green!5}Gender & \cellcolor{green!5}1/8 & \cellcolor{green!5}12.5 \\  \hline
  \cellcolor{green!27} DoctorWho 101 Bro, that's kinda rude dude. That's like saying you're happy about someone of one ethnicity bc a different ethnicity is gross.  & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}Ethnicity & \cellcolor{green!27}1/23 & \cellcolor{green!27}4.348 \\  \hline
  \cellcolor{green!5} Am lia L.  see-no-evil monkey emoji  whaaaat (and really, you play too? that's cool!)  & \cellcolor{green!5}Monkey & \cellcolor{green!5}Black & \cellcolor{green!5}1/13 & \cellcolor{green!5}7.692 \\  \hline
  \cellcolor{green!27}Congrats Benton ! Amazing transition  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5}In regards to facial hair. It'll come. When I was your age, it grew slowly. Once you hit your 20s, the facial hair will start growing more and at a faster rate. Before you know it, shaving once a month becomes once a week and once a week becomes everyday. Enjoy the clean face while it lasts.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/57 & \cellcolor{green!5}1.754 \\  \hline
  \cellcolor{green!27} Bits of Laurie it's irrelevant whether Benton is cis or not. other than being reliant on a whole range of genetic and dietary factors, facial hair and DHT binding does actually have positive correlation to your age, thus you get more facial hair as you get older, and your hairline recedes as you age, whether you are a cisgender man or a transman on HRT.  & \cellcolor{green!27}Age & \cellcolor{green!27}Age & \cellcolor{green!27}1/65 & \cellcolor{green!27}1.538 \\  \hline
  \cellcolor{green!5}Okay, I stand corrected: it's irrelevant in Benton's case because he started HRT around 17? I'm not actually sure. In any case his 'second puberty' follows a similar pattern to a cis man's and as I said the effects of DHT on his hair follicles will become stronger with age (hence more facial hair once he'll be in his 20s).  Obviously the effects of T are way different if you start HRT in your 40s. Most start in their 20s or even as soon as they hit 18, though.  & \cellcolor{green!5}Age & \cellcolor{green!5}Age & \cellcolor{green!5}1/89 & \cellcolor{green!5}1.124 \\  \hline
  \cellcolor{green!27} louman-eightyfour It might not come - without being braggy and insensitive, I have glorious 5 o'clock shadow. But one of my best friends struggles to grow more than about 3 facial hairs and we're both in our late 20's - biology is weird.  & \cellcolor{green!27}Weird & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/43 & \cellcolor{green!27}2.326 \\  \hline
  \cellcolor{green!5}I have a question, if you don't mind me asking, but have you had top surgery? I have to thank you, I got the courage to come out as transgender and hopefully will start T in the next couple of months. Thanks man!  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/43 & \cellcolor{green!5}2.326 \\  \hline
  \cellcolor{green!27}AND HERE I AM AT A YEAR ON T WITH ZERO FAT REDISTRIBUTION AHAHAHAHAHAAHA I'M SO SAD  & \cellcolor{green!27}Zero & \cellcolor{green!27}Youngsters & \cellcolor{green!27}1/17 & \cellcolor{green!27}5.882 \\  \hline
  \cellcolor{green!5} Benton did u loose but/thigh fat????  & \cellcolor{green!5}Fat & \cellcolor{green!5}Physical Features & \cellcolor{green!5}1/6 & \cellcolor{green!5}16.667 \\  \hline
  \cellcolor{green!27}If anyone is interested, this problem did get solved for me.  The thing about fat redistribution is that it's not actually the body fat you already have moving location, it's that testosterone signals your body to place new fat in your body differently, be more okay with losing fat in the ass/hips/thigh area, and overall makes it easier to have a lower body fat percentage (along with this, the broadening of your upper body can do a ton of help and offsetting the disproportionate largeness of hips). So after you start T, over time, because you burn and place down very small amounts of fat from day to day, you will eventually have a noticeable amount of fat redistribution, but it will be very gradual. If you work on losing body fat in general, this will go much quicker, and will be much more attainable than pre-t.  My problem was that I was gaining body fat the whole time (I put on about 15 pounds from staring to 1 year on T), so my body never had a chance to burn that old fat, because I was never at a caloric deficit, not even the typical, very small one that would allow redistribution very gradually. And even if my body was placing down more fat in my stomach area, T doesn't mean you will completely stop putting fat in your ass/hips all together. So the stuff I was gaining that was added to what I already had.  Since I made this comment, I have lost weight and finally have hips smaller than pre-T, and I'm so fucking happy about it. What it took was tracking what I ate, eating at a caloric deficit to lose body fat, and doing it consistently. It'd be awesome if T just took care of all the work for you, but it doesn't. If your dysphoria is bad enough though, the work is totally worth it.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/321 & \cellcolor{green!27}0.312 \\  \hline
  \cellcolor{green!5}Such an amazing transformation! You are honestly so strong and have inspired me so much even though I'm not transgender myself I am extremely interested in it. You are honestly my favorite YouTuber and I've been supporting you for a long time but I  haven't commented very often, so why not comment today? haha. We've been through very similar experiences with the self harm :( Anyways I'm so proud of how far you've come and I love you and support you :)  & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/82 & \cellcolor{green!5}1.22 \\  \hline
  \cellcolor{green!27}You look incredible and totaly awesome! You don't just be a guy, you also absolutly like one (I hope you understand how I mean it)! If your video wouldn't be about being transgender, I would have thought this is just a random video of a great looking guy!  )  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5} Gabryela Tomio Please PLEASE don't resort to suicide.  There are people who care. The internet has change the game for trans and LGBTQ youth as far as support and information goes because there are people out there that want to help and share information. I always read some of the comments Benton gets and so many trans kids out there and so many of you are feeling isolated and alone but once you start to leave comments you can make connections with people. IT GETS BETTER....it really does.  The teenage years are the worst for any kid and add being trans or gay and it is amped up because other kids are cruel but won't always be around those people and you will be in a position to advocate for yourself.  Call the The Trevor Project or other suicide hotline if you feel like you getting too close to actually going through with it. Do you have someone you can talk to? A friend? teacherR? parent? sibling? relative? anybody?  & \cellcolor{green!5}Gay & \cellcolor{green!5}Sexual Identity & \cellcolor{green!5}1/169 & \cellcolor{green!5}0.592 \\  \hline
  \cellcolor{green!27} Matthew G Your comment has touched me deeply and I have been trying to come up with something profound to respond but the reality is that your situation is horrific. Nobody should be rejected, but I know that far too many kids are. The saddest part is that trans kids need the most love and support because a transition has to be one of the most difficult things to go through at an age that is pretty crappy for most kids without confounding factors like being rejected by family, having no support system and the issues and bullying that come with transition.  Don't give up. Hope is crucial in so many facets of life, including where you are.  I promise that if you want to chat over email I will be here for you. If you are interested you can email me at daneekaps gmail.com. I'm a mom with two kids-16 and 9 and a pediatric nurse practitioner so I know about kids and teens. I am no expert on transition but I can be someone you can talk to.  & \cellcolor{green!27}Transition & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/179 & \cellcolor{green!27}0.559 \\  \hline
  \cellcolor{green!5}I'm so glad to see this, I don't comment a lot on youtube. You know what, do what makes you happy, and give 0 fucks about everybody else. Takes tons of testosterone :) !!!!!! A few years later, when u think back that you even considered suicide, you will feel so so dumb about yourself just to think that. Life gets better, I promise. Unless u do drugs.... Lmao :)  & \cellcolor{green!5}Dumb & \cellcolor{green!5}Physical (and Mental) Impairments & \cellcolor{green!5}1/70 & \cellcolor{green!5}1.429 \\  \hline
  \cellcolor{green!27} Quasar Well you're the one who came to their world and watched the video and felt the need to announce you were here. I would much rather  they  infect the world with faggot culture than whatever lies you tell yourself in order to look at yourself in the mirror. Grow up and get some professional help....clearly you need it.  & \cellcolor{green!27}Faggot & \cellcolor{green!27}Male homosexuality & \cellcolor{green!27}1/59 & \cellcolor{green!27}1.695 \\  \hline
  \cellcolor{green!5}Depending on the doctor, younger FtMs can be put on blockers as a stepping stone or a permanent thing. MtFs, since testosterone is such an active hormone, need to be on anti-androgens along with estrogen until the testes are removed (if ever). I, as a 19 yr old FtM, have had one doctor recommend me to take hormone blockers with T, and have two other doctors try to regulate with just my T dose.  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/74 & \cellcolor{green!5}1.351 \\  \hline
  \cellcolor{green!27} Connor Garst Thanks so much for answering me. I tried to look it up but couldn't find a definitive answer.  I guess in your case, you could see if T alone does enough and if not you could take an estrogen blocker. Ideally younger kids could get on blockers and avoid the severe dysphoria associated with puberty. But it's  tough enough to talk about trans issues when you are older, I can't imagine an 8 year old trying to advocate for themselves.  I'm sure there are situations with parents who are accepting from a young age but for so many of you it just isn't possible and it breaks my heart. I hope someday we can be more accepting as a society. People like you and Benton, who are advocating and speaking out on YouTube and blogs are making a difference.  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/141 & \cellcolor{green!27}0.709 \\  \hline
  \cellcolor{green!5} Danee Kaplan Thank you very much :) There are youth out there that start to medically transition before puberty through hormone blockers, though it's very uncommon, especially in the US. I have seen it happen, however, it's more common with MtFs for some reason. But yes, you have the jist of it. People in the community are trying to lobby for trans youth to give their own consent at a younger age, but I don't see it happening any time soon.  & \cellcolor{green!5}Transition & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/81 & \cellcolor{green!5}1.235 \\  \hline
  \cellcolor{green!27} Connor Garst Yes, we have a long way to go before everyone understands that transGENDER has nothing to do with SEX...that trans individuals are not sexual perverts or deviants, they aren't pedophiles and they aren't motivated by the desire to spend time in the women's bathroom.  I am not sure what one would see in the women's bathroom, but Michelle Duggar seems to think that is the reason someone would desire to change their gender.  That said, there is precedence for minors having authority to make medical decisions without parental conscent and that is regarding reproductive health care.  In the US-all 50 States- youths are emancipated for decisions regarding birth control, STD diagnosis and treatment and all prenatal care. I don't know about other countries but I will say that contrary to popular belief the US does not have the most progressive medical care so I suspect other countries have this as well.  & \cellcolor{green!27}Transgender & \cellcolor{green!27}Transexuality & \cellcolor{green!27}1/153 & \cellcolor{green!27}0.654 \\  \hline
  \cellcolor{green!5}I hope to get on testosterone when I'm older, you're so lucky , I'm jealous :D I'm not even on hormone blockers yet but I'm going to hopefully soon. I'm 14 next month so I'm still a kid really but ayy Is it normal for us transguys to hate their appearance so much that you can't even look in the mirror at yourself. I hate my skinny arms, my feminine face, my feminine looking everything etc... But I'll look at other transguys or cisguys just any guy and would do anything just to look like them  & \cellcolor{green!5}Skinny & \cellcolor{green!5}Physical Features & \cellcolor{green!5}1/96 & \cellcolor{green!5}1.042 \\  \hline
  \cellcolor{green!27} OleoBlog I'm almost 14 and have a 14-year-old friend and he desperately dreams of testosterone.   Dysphoria like that is very common. Very.  & \cellcolor{green!27}Common & \cellcolor{green!27}Working class & \cellcolor{green!27}1/22 & \cellcolor{green!27}4.545 \\  \hline
  \cellcolor{green!5}Good to hear it's common then :)  Hilda Sales Thanks so much :D You have to admit my voice is pretty high pitched compared to your average 14 year old cisguy though, I try to make it sound deeper sort of :P  & \cellcolor{green!5}Old & \cellcolor{green!5}Over 65s & \cellcolor{green!5}1/42 & \cellcolor{green!5}2.381 \\  \hline
  \cellcolor{green!27}You have serious mental issues  & \cellcolor{green!27}Mental & \cellcolor{green!27}Physical (and Mental) Impairments & \cellcolor{green!27}1/5 & \cellcolor{green!27}20.0 \\  \hline
  \cellcolor{green!5} Fallout3ProHunter It's called gender dysphoria.  & \cellcolor{green!5}Gender & \cellcolor{green!5}Gender & \cellcolor{green!5}1/5 & \cellcolor{green!5}20.0 \\  \hline
  \cellcolor{green!27} TheFifthDimension I'm reaching puberty and don't have a completely flat chest, it's barely anything but when you are trying to not have breasts (ew I hate the thought of having them) even the tiniest bit makes you self conscious. So obviously I'm not wearing a girls swimming costume, that's like wearing a dress, I wear trunks but I wear a rash vest so it's all good :P I wish I didn't have to wear it and even though I have passed well in front of other people, there were these two 16 or 18 year old boys at the pool the other day jumping in and the water reached me and I'm pretty sure they said  it reached that girl over there ... I couldn't hear to well but meh :/ My face isn't that masculine really and my top half was covered up :/  & \cellcolor{green!27}Old & \cellcolor{green!27}Over 65s & \cellcolor{green!27}1/144 & \cellcolor{green!27}0.694 \\  \hline
  \cellcolor{green!5} TheFifthDimension Just had Scoliosis surgery 3 months ago so I can do swimming but hopefully soon the doctors will let me get back to being my usual sporty self :D My mum hit puberty at 15 and I'm 14 so hopefully have a while, plus people in my family are late starters, my cousin hit puberty at 19. Haha thank you!  & \cellcolor{green!5}doctors & \cellcolor{green!5}Nationality & \cellcolor{green!5}1/61 & \cellcolor{green!5}1.639 \\  \hline
  \cellcolor{green!27} 0scR Scoliosis is where you have a curved spine haha, not anything to do with gender :P I've had Scoliosis that developed when I was 5 and was getting worse so they decided to straighten my spine. They do it with two titanium rods and lots of screws  )  & \cellcolor{green!27}Gender & \cellcolor{green!27}Gender & \cellcolor{green!27}1/49 & \cellcolor{green!27}2.041 \\  \hline
  \cellcolor{green!5} OleoBlog My son loathes his breasts. I knew he was either trans or had some sort of body image issues at age 12.  It wasn't until age 13-1/2 when I gave him the name, transgender, that he started to understand why he hated his body.   He has the equivalent breast size of a large C-cup bra. (He also has scoliosis).  When he went through puberty, I bought him chest binders from Underworks. I hope you can get hormone blockers before you need to bind. In our family, the females have lower-pitched voices. I can't wait to see what T will do for him. Good luck in your journey!     & \cellcolor{green!5}Transgender & \cellcolor{green!5}Transexuality & \cellcolor{green!5}1/109 & \cellcolor{green!5}0.917 \\  \hline
  
\end{longtable}
\end{center}


\centering\textbf{\large \hypertarget{Table 2}{Table 2}: Summary of the results per sociolinguistic variable 
}
\newcolumntype{C}[2]{>{\centering\arraybackslash}p{#1}}
\begin{center}
\setlength\mylength{\dimexpr\textwidth - 1\arrayrulewidth - 40\tabcolsep}
\begin{longtable}{|C{.25\mylength}|C{.40\mylength}|C{.15\mylength}|C{.15\mylength}|C{.15\mylength}|}
\hline
\textbf{Variavel Sociolinguistica} & \textbf{KeyWords} & \textbf{N de ocorrencias} & \textbf{Frequencia}  & \textbf{Frequencia(\%)} \\
\hline\multirow{1}{*}{\cellcolor{red!27}Transexuality}  & \cellcolor{red!27}Transgender, Transition, LGBT, Tranny, Transsexual, Transvestite & \cellcolor{red!27}306 & \cellcolor{red!27}306/105204& \cellcolor{red!27}0.29 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Chinese}  & \cellcolor{red!5}pussy, Slope & \cellcolor{red!5}18 & \cellcolor{red!5}18/105204& \cellcolor{red!5}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Gender}  & \cellcolor{red!27}Sex, Gender, Woman, Chick, Sexual, Sexism & \cellcolor{red!27}679 & \cellcolor{red!27}679/105204& \cellcolor{red!27}0.65 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Male homosexuality}  & \cellcolor{red!5}Gay, LGBT, Faggot, Queer, Pansy, Twink, Fag & \cellcolor{red!5}172 & \cellcolor{red!5}172/105204& \cellcolor{red!5}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Sexual Identity}  & \cellcolor{red!27}Gay, LGBT, homophobic, homosexual, Queer, Homophobia & \cellcolor{red!27}170 & \cellcolor{red!27}170/105204& \cellcolor{red!27}0.16 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Physical (and Mental) Impairments}  & \cellcolor{red!5}Mental, Crazy, Weird, Freak, Dumb, Weirdo, Retard, Handicapped, Blind, Limp, Psycho & \cellcolor{red!5}328 & \cellcolor{red!5}328/105204& \cellcolor{red!5}0.31 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Native-American}  & \cellcolor{red!27}Apple, Indian, Red & \cellcolor{red!27}32 & \cellcolor{red!27}32/105204& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Over 65s}  & \cellcolor{red!5}Old & \cellcolor{red!5}44 & \cellcolor{red!5}44/105204& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Black}  & \cellcolor{red!27}Nigga, African, Ape, Black, Monkey, Crow, coloured, Colored & \cellcolor{red!27}27 & \cellcolor{red!27}27/105204& \cellcolor{red!27}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Age}  & \cellcolor{red!5}Age & \cellcolor{red!5}39 & \cellcolor{red!5}39/105204& \cellcolor{red!5}0.04 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Ethnicity}  & \cellcolor{red!27}Race, Racist, Racism, Ethnicity & \cellcolor{red!27}14 & \cellcolor{red!27}14/105204& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Youngsters}  & \cellcolor{red!5}Nothing, Nobody, Zero, Insect, Twerp & \cellcolor{red!5}94 & \cellcolor{red!5}94/105204& \cellcolor{red!5}0.09 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Nationality}  & \cellcolor{red!27}doctors, Alien, Refugee, Nation & \cellcolor{red!27}20 & \cellcolor{red!27}20/105204& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}French}  & \cellcolor{red!5}Frog & \cellcolor{red!5}2 & \cellcolor{red!5}2/105204& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27} Ideological and Political Identity}  & \cellcolor{red!27}Libtard, Cuck, Snowflake, Red & \cellcolor{red!27}7 & \cellcolor{red!27}7/105204& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Female age and physical appearance}  & \cellcolor{red!5}Witch & \cellcolor{red!5}2 & \cellcolor{red!5}2/105204& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Female sexuality}  & \cellcolor{red!27}THOT, Promiscuous & \cellcolor{red!27}2 & \cellcolor{red!27}2/105204& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Working class}  & \cellcolor{red!5}Common, Redneck & \cellcolor{red!5}34 & \cellcolor{red!5}34/105204& \cellcolor{red!5}0.03 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Physical Features}  & \cellcolor{red!27}Obese, Fat, Scrawny, Skinny & \cellcolor{red!27}18 & \cellcolor{red!27}18/105204& \cellcolor{red!27}0.02 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}German}  & \cellcolor{red!5}Hun & \cellcolor{red!5}8 & \cellcolor{red!5}8/105204& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Muslim}  & \cellcolor{red!27}Terrorist & \cellcolor{red!27}2 & \cellcolor{red!27}2/105204& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Female homosexuality}  & \cellcolor{red!5}Lesbian, Tomboy & \cellcolor{red!5}13 & \cellcolor{red!5}13/105204& \cellcolor{red!5}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}White}  & \cellcolor{red!27}Redneck & \cellcolor{red!27}15 & \cellcolor{red!27}15/105204& \cellcolor{red!27}0.01 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Japanese}  & \cellcolor{red!5}Nip & \cellcolor{red!5}2 & \cellcolor{red!5}2/105204& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Irish}  & \cellcolor{red!27}Mick & \cellcolor{red!27}2 & \cellcolor{red!27}2/105204& \cellcolor{red!27}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!5}Roman Catholic}  & \cellcolor{red!5}Mick & \cellcolor{red!5}2 & \cellcolor{red!5}2/105204& \cellcolor{red!5}0.0 \\  \hline
  \multirow{1}{*}{\cellcolor{red!27}Italian}  & \cellcolor{red!27}Guido & \cellcolor{red!27}1 & \cellcolor{red!27}1/105204& \cellcolor{red!27}0.0 \\  \hline
  
\end{longtable}
\end{center}


\textbf{\Large Result analysis:}

\begin{itemize}\item Taking into account the words that were detected, we can reach the conclusion these comments are associated with : : Transexuality;
 Chinese;
 Gender;
 Male homosexuality;
 Sexual Identity;
 Physical (and Mental) Impairments;
 Native-American;
 Over 65s;
 Black;
 Age;
 Ethnicity;
 Youngsters;
 Nationality;
 French;
  Ideological and Political Identity;
 Female age and physical appearance;
 Female sexuality;
 Working class;
 Physical Features;
 German;
 Muslim;
 Female homosexuality;
 White;
 Japanese;
 Irish;
 Roman Catholic;
 Italian;%.

\item The percentage of hate speech related words is 1.9514.

\item Considering that the variable \textbf{Gender} has the most occurences in the post, we can interpret that this is the predominant hate speech.

\item Overall there were 2053/5115 occurences of hate speech related comments.\end{itemize}\end{document}